### 2016-01-05 docs/proposal/proposal.tex
Add papers to read

\documentclass{article}

% GRAPHICS
\usepackage{graphicx}

% HYPERLINKS
\usepackage{hyperref}

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.5in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{2ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

\begin{document}

% TITLE
\title{Autonomous Quadrotor Landing on a Moving Platform}
\author{Stan Brown \& Chris Choi}
\maketitle

\section*{Introduction}
Landing a quadrotor on a moving platform.

\section*{Previoius and Related Work}

\section*{Methods}

\section*{Milestones}
\begin{enumerate}
	\item{Identify hardware (camera, extra sensors...)}
	\item{Identify potential algorithmic solutions}
	\item{Implement solutions in softwaree}
	\item{Implement solutions in hardware}
	\item{Calibration of sensors}
	\item{Computer vision ID landing zone}
	\item{Motion Planning to land}
	\item{Perform the above successfully in simulation}
	\item{Perform the above successfully in real life}
\end{enumerate}

\section*{Potential Problems}
\begin{itemize}
	\item{Gazebo may have poor wind simulations}
	\item{Quadrotor ground effects (GP calcuting the error term?)}
\end{itemize}

\bibliography{proposal}{}
\bibliographystyle{plain}

\end{document}

### 2016-01-14 docs/proposal/proposal.tex
Add proposal

@@
 \section*{Introduction}
-Landing a quadrotor on a moving platform.
+Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, there exists a wide range of approaches to the problem, however to the best of our knowledge we are not aware of any solution that demonstrates a quadrotor capable of landing on a moving platform outdoors.
+It is our goal to replicate one of the successful solutions with the aim of extending the solution to land outdoors.
 
-\section*{Previoius and Related Work}
+\section*{Related Work} 
+The problem of autonous landing on a moving platform can be divded into three parts, perception, control and planning.
+
+From the literature we reviewed planning is the least concern, perception and control seems to be the main factor to sucess.
+For perception existing solutions could be as simple as using basic color detection techniques to identify the landing target\cite{Kim2014}, to sophisticated techniques such as \cite{Herisse2012} where they used the optical flow in images captured onboard the quadrotor to obtain necessary relative information for control.
 
@@
 
+\begin{itemize}
+	\vspace{-0.2cm}
+	\setlength{\itemsep}{5pt}
+	\setlength{\parskip}{0pt}
+	\setlength{\parsep}{0pt}
+
+	\item{\textbf{Perception}: To simplify the problem we plan to use common image processing techniques and AprilTag to identify the landing target.
+This is similar to \cite{Ling2014} where the solution used AprilTag and AprilTag Detection Algorithm to return the 6 dof pose of the landing target.}]
+
+	\item{\textbf{Control}: For our first approach we plan implementing using a set of PID Controller to minimize distance, altitude, heading difference, with the state controller overseeing the transition between tracking, approach and landing phase of the quadrotor.}
+
+	\item{\textbf{Planing}: At this stage we will omit planning because we are assuming that the quadrotor is within visual proximity to landing target, and we assume that the landing control implemented on the PX4 firmware \cite{px4} running on the Pixhawk flight controller \cite{pixhawk} will be adequate for our project.}
+
+	\vspace{-0.2cm}
+\end{itemize}
+
 \section*{Milestones}
 \begin{enumerate}
-	\item{Identify hardware (camera, extra sensors...)}
-	\item{Identify potential algorithmic solutions}
-	\item{Implement solutions in softwaree}
-	\item{Implement solutions in hardware}
-	\item{Calibration of sensors}
-	\item{Computer vision ID landing zone}
-	\item{Motion Planning to land}
-	\item{Perform the above successfully in simulation}
+	\item{Perform tracking and follow in simulation}
+	\item{Perform automated landing in simulation}
 	\item{Perform the above successfully in real life}
@@
 
-\section*{Potential Problems}
-\begin{itemize}
-	\item{Gazebo may have poor wind simulations}
-	\item{Quadrotor ground effects (GP calcuting the error term?)}
-\end{itemize}
+\section*{Possible Expansion}
+
+Trajectory Planning for high wind or fast moving platform.
 

### 2016-01-15 docs/proposal/proposal.tex
some edits

@@
 \section*{Introduction}
-Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, there exists a wide range of approaches to the problem, however to the best of our knowledge we are not aware of any solution that demonstrates a quadrotor capable of landing on a moving platform outdoors.
+Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem.
+However, to the best of our knowledge, we are not aware of any solution that demonstrates an algorithm that is capable of landing a quadrotor on a moving platform outdoors.
 It is our goal to replicate one of the successful solutions with the aim of extending the solution to land outdoors.
 
+\subsection*{Applications}
+Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform, landing in high wind conditions.
+
 \section*{Related Work} 
-The problem of autonous landing on a moving platform can be divded into three parts, perception, control and planning.
+The problem of autonomous landing on a moving platform seems to be divided into three separate parts in literature.
+First the quadrotor must plan to rendezvous with its target, next it must detect or sense its target and finally apply a set of controllers to approach the platform, match speed and heading and finally land when safe to do so.
+
+In the majority of the literature reviewed, rendezvous planning was neglected and it was assumed that quadrotor has a clear view of its landing location.
 
@@
 
-\section*{Methods}
+\section*{Proposed Methodology}
 

### 2016-01-15 include/munit.h
Add intial code structure

@@ -1,0 +1,113 @@
+#ifndef __MUNIT_H__
+#define __MUNIT_H__
+
+#include <stdio.h>
+#include <stdlib.h>
+
+
+/* GLOBAL VARIABLES */
+static int tests = 0;
+static int passed = 0;
+static int failed = 0;
+
+
+/* MACROS */
+#define KNRM  "\x1B[0m"
+#define KRED  "\x1B[31m"
+#define KGRN  "\x1B[32m"
+#define KYEL  "\x1B[33m"
+#define KBLU  "\x1B[34m"
+#define KMAG  "\x1B[35m"
+#define KCYN  "\x1B[36m"
+#define KWHT  "\x1B[37m"
+
+/* MUNIT */
+#define mu_assert(test, message) \
+    do { \
+        if (!(test)) { \
+            printf( \
+                "%sERROR!%s [%s:%d] %s\n", \
+                KRED, \
+                KNRM, \
+                __func__, \
+                __LINE__, \
+                message \
+            ); \
+            return -1; \
+        }\
+    } while (0)
+
+#define mu_check(test) \
+    do { \
+        if (!(test)) { \
+            printf( \
+                "%sERROR!%s [%s:%d] %s %sFAILED!%s\n", \
+                KRED, \
+                KNRM, \
+                __func__, \
+                __LINE__, \
+                #test, \
+                KRED, \
+                KNRM \
+            ); \
+            return -1; \
+        }\
+    } while (0)
+
+#define mu_add_test(test) \
+    do { \
+        tests++; \
+        printf( \
+            "%s-> %s %s\n", \
+            KBLU, \
+            #test, \
+            KNRM \
+        ); \
+        fflush(stdout); \
+        if (test() == -1) { \
+            printf("%sTEST FAILED!%s\n\n", \
+                KRED, \
+                KNRM \
+            ); \
+            failed++; \
+        } else { \
+            printf("%sTEST PASSED!%s\n\n", \
+                KGRN, \
+                KNRM \
+            ); \
+            passed++; \
+        } \
+    } while (0)
+
+#if defined(MU_PRINT)
+  #if MU_PRINT == 1
+    #define mu_print(message, ...) \
+        printf(message, ##__VA_ARGS__)
+  #elif MU_PRINT == 0
+    #define mu_print(message, ...)
+  #endif
+#else
+    #define mu_print(message, ...)
+#endif
+
+#define mu_report() \
+    do { \
+        printf(KBLU); \
[…]

### 2016-01-15 include/utils.h

@@ -1,0 +1,123 @@
+#ifndef __UTILS_H__
+#define __UTILS_H__
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <stdint.h>
+#include <string.h>
+#include <errno.h>
+#include <math.h>
+
+
+
+/* DEBUG / LOG */
+#ifdef NDEBUG
+  #define debug(M, ...)
+#else
+  #define debug(M, ...) \
+      fprintf(stderr, \
+          "[DEBUG] %s:%d: " M "\n", \
+          __func__, \
+          __LINE__, \
+          ##__VA_ARGS__ \
+      )
+#endif
+#define log_err(M, ...) \
+    fprintf(stderr,\
+        "[ERROR] (%s:%d) " M "\n",\
+        __FILE__,\
+        __LINE__,\
+        ##__VA_ARGS__\
+    )
+#define log_warn(M, ...) \
+    fprintf(stderr, "[WARN] " M "\n", ##__VA_ARGS__)
+#define log_info(M, ...) \
+    fprintf(stderr, "[INFO] " M "\n", ##__VA_ARGS__)
+
+
+
+/* CONTROL FLOW */
+#define check(A, M, ...) \
+    if (!(A)) { \
+        log_err(M, ##__VA_ARGS__); \
+        goto error; \
+    }
+#define check_mem(A) check((A), "out of memory.")
+#define check_debug(A, M, ...) \
+    if (!(A)) { \
+        debug(M, ##__VA_ARGS__); \
+        goto error; \
+    }
+#define silent_check(A) \
+    if (!(A)) { \
+        goto error; \
+    }
+
+
+
+/* MEMORY */
+#define INTEGER 0
+#define FLOAT 1
+#define DOUBLE 2
+#define STRING 3
+
+void *copy_value(int value_type, void *value);
+int *malloc_int(int i);
+float *malloc_float(float f);
+double *malloc_double(double d);
+char *malloc_string(const char *s);
+#define free_mem(TARGET, FREE_FUNC) \
+    if (TARGET) { \
+        FREE_FUNC((void *) TARGET); \
+    }
+
+/* if ((((uintptr_t) FREE_FUNC != (uintptr_t) NULL) ? 1 : 0)) { \ */
+
+#define free_mem_arr(TARGET, NELEM, FREE_FUNC) \
+    int _i; \
+    if (TARGET) { \
+        for (_i = 0; _i < NELEM; _i++) { \
[…]

### 2016-01-15 include/webcam.hpp

@@ -1,0 +1,14 @@
+#ifndef __WEBCAM_H__
+#define __WEBCAM_H__
+
+#include <iostream>
+
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+
+
+/* FUNCTIONS */
+void webcam_run(void);
+
+
+#endif

### 2016-01-15 scripts/dependencies.sh

@@ -1,0 +1,65 @@
+#!/bin/sh
+export CLASSPATH=$CLASSPATH:/usr/share/java/gluegen-rt.jar:/usr/local/share/java/lcm.jar:$HOME/april/java/april.jar:./
+export LD_LIBRARY_PATH=$LD_LIBRARY_PATH:$HOME/april/lib
+alias java='java -ea -server'
+
+
+install_dependencies()
+{
+    # install dependencies
+    apt-get install -y \
+        git-core \
+        ant subversion \
+        gtk-doc-tools \
+        libglib2.0-dev \
+        libusb-1.0-0-dev \
+        gv \
+        libncurses-dev \
+        openjdk-7-jdk \
+        autopoint \
+        libgl1-mesa-dev \
+        libpng12-dev \
+        libdc1394-22-dev
+}
+
+# install LCM
+install_lcm()
+{
+    cd $HOME
+    git clone https://code.google.com/p/lcm lcm
+    cd lcm
+    ./bootstrap.sh
+    ./configure
+    make
+    sudo make install
+    rm -rf $HOME/lcm
+}
+
+# install april toolkit
+install_april()
+{
+    cd $HOME
+    git clone git://april.eecs.umich.edu/home/git/april.git
+    cd april/src
+    make all
+    cd $HOME
+    cd april/java
+    ant
+    rm -rf $HOME/april
+}
+
+# RUN
+# install_dependencies
+# install_lcm
+# install_april
+
+# cd $HOME
+# # git clone https://github.com/liuliu/ccv.git
+# cd ccv/lib
+# ./configure && make
+# clang \
+#     -L"$HOME/ccv/lib" \
+#     -I"$HOME/ccv/lib" sift.c \
+#     -lccv `cat $HOME/ccv/lib/.deps`
+cd $HOME
+# rm -rf ccv

### 2016-01-15 src/webcam.cpp

@@ -1,0 +1,23 @@
+#include "webcam.hpp"
+
+
+void webcam_run(void)
+{
+    cv::VideoCapture capture(1);
+    cv::Mat frame;
+
+    /* open capture device */
+    if (capture.isOpened() != 0) {
+        std::cout << "Failed to open webcam!";
+    }
+
+    /* read capture device */
+    while (true) {
+        capture.read(frame);
+        cv::imshow("camera", frame);
+
+        if (cv::waitKey(30) >= 0) {
+            return;
+        }
+    }
+}

### 2016-01-15 tests/webcam_test.cpp

@@ -1,0 +1,14 @@
+#ifndef MU_PRINT
+  #define MU_PRINT 1
+#endif
+
+#include "munit.h"
+#include "webcam.hpp"
+
+
+void test_suite()
+{
+    webcam_run();
+}
+
+mu_run_tests(test_suite)

### 2016-02-11 homework/homework_1/report.tex
Add homework 1

\documentclass{article}

% MATHS
\usepackage{amsmath}
\usepackage{gensymb}

\usepackage{mathtools}
\newcommand\coolover[2]{\mathrlap{\smash{\overbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}^{\mbox{$#1$}}}}#2} 
\newcommand\coolunder[2]{\mathrlap{\smash{\underbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}_{\mbox{$#1$}}}}#2}

\newcommand\coolleftbrace[2]{%
#1\left\{\vphantom{\begin{matrix} #2 \end{matrix}}\right.}

\newcommand\coolrightbrace[2]{%
\left.\vphantom{\begin{matrix} #1 \end{matrix}}\right\}#2}

% GRAPHICS
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{tikzscale}
\usetikzlibrary{calc}
\usepackage{graphicx}

% HYPERLINKS
\usepackage{hyperref}

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.2in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{5ex}{2ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

%COMMENTING
\usepackage{comment}

\begin{document}

% TITLE
\title{ME780 Assignment 1}
\author{Stan Brown \& Chris Choi}
\date{}
\maketitle

\section{Derivation of the Omni-directional Robot}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/omni_robot_1.tikz}
		\caption{Omni-Directional Robot in Body Frame}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/omni_robot_2.tikz}
		\caption{Body Frame w.r.t Each Wheel}
	\end{subfigure}
	\caption{Omni-Directional Robot}
	\label{fig:omni_robot}
\end{figure}

Here we derive the kinematics of the Omni-directional robot. We followed the
generalized approach in \cite{Siegwart04} in resolving how each wheel
contributes to the robot chassis. The generalized equation is:

\begin{equation}
	\label{eq:general_robot_kinematics_equation}
    \xi_{I} = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
\end{equation}

Where:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

    \item{$\xi_{I}$: State in the body frame}
    \item{$R(\theta)$: Rotation matrix}
    \item{$J_{1}$: Wheel constraints}
    \item{$J_{2}$: Diagonal matrix denoting the radii $r$ of each wheel}
    \item{$\omega$: Angular velocity $\omega$ of each wheel}
\end{itemize}

\newpage
Deriving the robot kinematics for each wheel we get in the form of 
\ref{eq:general_robot_kinematics_equation} we obtain:

\begin{align}
	\vphantom{% phantom stuff for correct box dimensions
    \begin{matrix}
    	\overbrace{XYZ}^{\mbox{$R$}} \\ \\
    	\underbrace{pqr}_{\mbox{$S$}}
    \end{matrix}}%
	J_{1} &= 
	\begin{bmatrix}
			0 & 1 & l \\
  	    	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
   	    	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
    \end{bmatrix}
    \begin{matrix}% matrix for right braces 
        \coolrightbrace{x}{Wheel 1}\\
	    \coolrightbrace{x}{Wheel 2}\\
	    \coolrightbrace{x}{Wheel 3}
    \end{matrix} \\
    J_{2} &=
    \begin{bmatrix}
        r & 0 & 0 \\
        0 & r & 0 \\
        0 & 0 & r
    \end{bmatrix} \\
    \omega &= 
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix}
\end{align}

Putting it all together we have:

\begin{align}
	\vspace{-0.4cm}
    \xi_{I}
        &= R(\theta)^{-1} J_{1}^{-1} J_{2} \omega \\
    \begin{bmatrix}
        \dot{x} \\
        \dot{y} \\
        \dot{\theta}
    \end{bmatrix}      
        &= 
        \begin{bmatrix}
	        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
	        \sin{(\theta)} & \cos{(\theta)} & 0 \\
	        0 & 0 & 1
        \end{bmatrix}^{-1}
        \begin{bmatrix}
            0 & 1 & l \\
          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
        \end{bmatrix}^{-1}
        \begin{bmatrix}
            r & 0 & 0 \\
            0 & r & 0 \\
            0 & 0 & r
        \end{bmatrix}
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix} \\
	 \begin{bmatrix}
	     \dot{x} \\
	     \dot{y} \\
	     \dot{\theta}
	 \end{bmatrix} 
	 	&=
		\begin{bmatrix}
			\cos{(\theta)} & \sin{(\theta)} & 0 \\
			-\sin{(\theta)} & \cos{(\theta)} & 0 \\
			0 & 0 & 1
		\end{bmatrix}
		\begin{bmatrix}
			0 & -\frac{1}{\sqrt{3}} & \frac{1}{\sqrt{3}} \\
			\frac{2}{3} & -\frac{1}{3} & -\frac{1}{3} \\
			\frac{1}{3l} & \frac{1}{3l} & \frac{1}{3l}
		\end{bmatrix}
		\begin{bmatrix}
			r & 0 & 0 \\
			0 & r & 0 \\
			0 & 0 & r
		\end{bmatrix}
	    \begin{bmatrix}
	       \omega_{1} \\
	       \omega_{2} \\
	       \omega_{3} \\
	    \end{bmatrix} \\
	\begin{bmatrix}
		\dot{x} \\
		\dot{y} \\
		\dot{\theta}
	\end{bmatrix} 
		&=
		\begin{bmatrix}
			\frac{2}{3} \sin(\theta) 
				& -\frac{1}{\sqrt{3}} \cos(\theta) 
					-\frac{1}{3} \sin(\theta)
				& \frac{1}{\sqrt{3}} \cos(\theta) 
					-\frac{1}{3} \sin(\theta) \\
			\frac{2}{3} \cos(\theta)
				& \frac{1}{\sqrt{3}} \sin(\theta) 
					-\frac{1}{3} \cos(\theta)
				& -\frac{1}{\sqrt{3}} \sin(\theta) 
					-\frac{1}{3} \cos(\theta) \\
			\frac{1}{3l} 
				& \frac{1}{3l}
				& \frac{1}{3l}
		\end{bmatrix}
		\begin{bmatrix}
			r \omega_{1} \\
			r \omega_{2} \\
			r \omega_{3} \\
		\end{bmatrix} \\
	\begin{bmatrix}
		\dot{x} \\
		\dot{y} \\
		\dot{\theta}
	\end{bmatrix} 
		&=
		\begin{bmatrix}
			\frac{2}{3} \sin(\theta) r \omega_{1}
				- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
					- \frac{1}{3} \sin(\theta) r \omega_{2}
				+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
					- \frac{1}{3} \sin(\theta) r \omega_{3} \\
			\frac{2}{3} \cos(\theta) r \omega_{1}
				+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
					-\frac{1}{3} \cos(\theta)r \omega_{2}
				- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
					-\frac{1}{3} \cos(\theta) r \omega_{3} \\
			\frac{1}{3l} r \omega_{1}
				+ \frac{1}{3l} r \omega_{2}
				+ \frac{1}{3l} r \omega_{3}
		\end{bmatrix} \\
	\vspace{-0.4cm}
\end{align}

\begin{equation}
	\vspace{-0.4cm}
	\dot{g}(\theta, \omega) 
		= 
		\begin{bmatrix}
			\dot{x} \\
			\dot{y} \\
			\dot{\theta}
		\end{bmatrix} 
\end{equation}

Where:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{$\dot{g}$ is our velocity motion model of the omni-directional robot}
	\item{$\theta$ is the angle (or bearing) of the robot in the inertia frame.}
	\item{$\omega$ is the wheel inputs of the robot 
		$\begin{bmatrix}
			\omega_{1} \\ 
			\omega_{2} \\ 
			\omega_{3}
		\end{bmatrix}$
	}
\end{itemize}

\newpage
\section{Applying the Derived Robot Model}
\subsection{Predefined Rotation Inputs}
Applying the following rotation inputs to the wheel for 15 seconds:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{$\omega_{1} = -15.5 \text{ rad} s^{-1}$}
	\item{$\omega_{2} = 10.5 \text{ rad} s^{-1}$}
	\item{$\omega_{3} = 1.5 \text{ rad} s^{-1}$}

	\vspace{-0.4cm}
\end{itemize}

We obtain the following motion.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{images/traverse_predefined.jpg}
	\caption{Traverse with inputs:
		$\omega_{1} = -15.5 \text{ rad} s^{-1}$
		$\omega_{2} = 10.5 \text{ rad} s^{-1}$
		$\omega_{3} = 1.5 \text{ rad} s^{-1}$
	}
	\label{fig:omni_robot_predefined}
\end{figure}

\subsection{Traversing East, West, North East, South East and Inplace}

\begin{figure}[H]
	\centering

	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_east.jpg}
		\caption{Traverse East}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_west.jpg}
		\caption{Traverse West}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_north_east.jpg}
		\caption{Traverse North East}
	\end{subfigure}

	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_south_east.jpg}
		\caption{Traverse South East}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_inplace.jpg}
		\caption{Traverse Inplace}
	\end{subfigure}

	\caption{Traversing East, West, North East, South East and Inplace}
	\label{fig:omni_robot_traverse}
\end{figure}

The inputs that drove the robot to traverse in the directions shown in 
Fig~\ref{fig:omni_robot_traverse} for 15 seconds  are as follows:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{
		\text{East}: 
		$\omega_{1} = 0$, $\omega_{2} = -1$, $\omega_{3} = 1$
	}
	\item{
		\text{West}: 
		$\omega_{1} = 0$, $\omega_{2} = 1$, $\omega_{3} = -1$
	}
	\item{
		\text{North East}: 
		$\omega_{1} = 1$, $\omega_{2} = -1$, $\omega_{3} = 0$
	}
	\item{
		\text{South East}: 
		$\omega_{1} = -1$, $\omega_{2} = 0$, $\omega_{3} = 1$
	}
	\item{
		\text{Inplace}: 
		$\omega_{1} = 1$, $\omega_{2} = 1$, $\omega_{3} = 1$
	}
\end{itemize}

\newpage
\subsection{Moving in a Circle}

To traverse in a circle of diameter of $2$m, we had to be a little creative
with the rotation inputs of the wheels. To do this we applied the following 
intuition:

\begin{enumerate}
	\vspace{-0.4cm}

    \item{Constrained the robot's $y$-axis movement to $0$, 
    and so $\dot{y}$ is $\dot{y} = 0$. Use wheels 2 and 3 as fixed wheels 
    pushing the robot forward, and use wheel 1 as a steering wheel. (See 
    fig~\ref{fig:omni_robot})}

    \item{For the robot to traverse a circle, the robot must traverse the
    circumference of a circle, i.e. $2 \pi R$, where $R$ is the radius of the 
    circle we want the robot to make $d = 2 \pi R$. Converting that to 
    velocity, the equation becomes $\dot{x} = \frac{2 \pi R}{t}$}

    \item{For the robot to make a full circle, it must change angle $\theta = 2 
    \pi$. Converting this to the angular rate the equation becomes 
    $\theta = \frac{2 \pi}{t}$}

   	\vspace{-0.4cm}
\end{enumerate}

Putting the above all together we have the following, originally we had:

\begin{equation}
    \xi_{I} = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
\end{equation}

Where we are trying to figure out what the $\omega$ inputs are to drive the 
robot to make a full circle in the inertial frame, we already know what 
$R(\theta)$, $J_{1}$, $J_{2}$ are, the only unknown left is $\xi_{I}$, but 
using the above intuition we can relate what it should be to make a circle.

\begin{equation}
    \omega = \xi_{I} R(\theta) J_{1} J_{2}^{-1}
\end{equation}

\begin{equation}
    \xi_{I} =
  		\begin{bmatrix}
            \dot{x} \\
            \dot{y} \\
            \dot{\theta}
        \end{bmatrix} 
        =
  		\begin{bmatrix}
            \frac{2 \pi R}{t} \\
            0 \\
            \frac{2 \pi}{t}
        \end{bmatrix}
\end{equation}

Using the above equation we found the $\omega$ inputs required to traverse a 
2m diameter circle in 15 seconds is $\omega_{1} = 0.50265$, $\omega_{2} = 
-0.94838$ $\omega_{3} = 1.95369$ starting from the origin $(0, 0)$.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{images/traverse_circle.jpg}
	\caption{Omni-Robot Traversing a Circle}
	\label{fig:omni_robot_circle}
\end{figure}

\newpage
\subsection{Traversing in a Spiral}

For traversing in a spiral we used a similar approach as traversing in a 
circle. We constrained the robot so that it was only traversing in the $x$ 
direction in the robot's body frame, and set the speed of wheel 1 to have 
intial angular velocity $\omega_{1} = 10$, with its angular velocity set to 
decay at a rate of $0.999$ per $dt = 0.1$. Below is a figure of the robot 
traversing in a spiral pattern for 50 seconds.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{images/traverse_spiral.jpg}
	\caption{Omni-Robot Traversing a Spiral}
	\label{fig:omni_robot_spiral}
\end{figure}

\newpage
\section{Measurement Model}

Lets suppose the robot has a GPS and magnometer sensor. It is given that ``The
GPS output is in true North, East (and Down, not used here) and the
magnetometer points to magnetic north (your declination is 9.7 degrees West in
Waterloo, ON). Define additive noise distributions, with standard deviations in
North and East of 0.50m, and in magnetic north of 10 degrees.''

Given the above information, our measurement noise covariance matrix $Q$ is:

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.5 & 0 & 0 \\
		0 & 0.5 & 0 \\
		0 & 0 & 10		
	\end{bmatrix}
\end{equation}

With a mean $\mu$ of:

\begin{equation}
	\mu = 
	\begin{bmatrix}
		0 \\
		0 \\
		-0.1692 
	\end{bmatrix}
\end{equation}

Note that 9.7 degrees is 0.1692 radians. Now that we have $\mu$ and $Q$, the 
Gaussian Additive Noise then becomes:

\begin{equation}
	\delta_{t} \sim \mathcal{N} (\mu, Q)
\end{equation}

To complete the measurement model it becomes:

\begin{align}
	y(t) &= C(t) x(t) + \delta_{t} \\
	&=
	\begin{bmatrix}
		1 & 0 & 0 \\
		0 & 1 & 0 \\
		0 & 0 & 1
	\end{bmatrix}
	\begin{bmatrix}
		x \\
		y \\
		\theta 
	\end{bmatrix}
	+
	\delta_{t}
\end{align}

\newpage
\section{Defining the Extended Kalman Filter for the Omni-directional Robot}

Normally if our motion model and/or measurement model is linear we can simply 
use the Kalman Filter, however in the non-linear case we have to use the 
Extended Kalman Filter (EKF). In our case we have to linearize the non-linear 
motion model $g(x_{t-1}, u_{t})$, where:

\begin{equation}
	\dot{g}(\theta, \omega) =
	\begin{bmatrix}
		\frac{2}{3} \sin(\theta) r \omega_{1}
			- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
				- \frac{1}{3} \sin(\theta) r \omega_{2}
			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
				- \frac{1}{3} \sin(\theta) r \omega_{3} \\
		\frac{2}{3} \cos(\theta) r \omega_{1}
			+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
				-\frac{1}{3} \cos(\theta)r \omega_{2}
			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
				-\frac{1}{3} \cos(\theta) r \omega_{3} \\
		\frac{1}{3l} r \omega_{1}
			+ \frac{1}{3l} r \omega_{2}
			+ \frac{1}{3l} r \omega_{3}
	\end{bmatrix}
\end{equation}

Rewriting the above in terms of state $x_{1}, x_{2}, x_{3}$, and inputs $u_{1}, u_{2}, u_{3}$, where $S$ and $C$ short hand for $sin$ and $cos$ functions.

\begin{align*}
	& g(x_{t-1}, u_{t}) = \\
	& \begin{bmatrix}
		x_{1, t - 1} + \left(
			\dfrac{2 r u_{1, t} S(x_{3, t-1})}{3}
			- \dfrac{r u_{2, t} C(x_{3, t-1})}{\sqrt{3}}
				- \dfrac{r u_{2, t} S(x_{3, t-1})}{3}
			+ \dfrac{r u_{3, t} C(x_{3, t-1})}{\sqrt{3}} 
				- \dfrac{r u_{3, t} S(x_{3, t-1})}{3}
			\right) dt \\\
		x_{2, t - 1} + \left( 
			\dfrac{2 r u_{1, t} C(x_{3, t-1})}{3}
			+ \dfrac{r u_{2, t} S(x_{3, t-1})}{\sqrt{3}}
				-\dfrac{r u_{2, t} C(x_{3, t-1})}{3}
			- \dfrac{r u_{3, t} S(x_{3, t-1})}{\sqrt{3}}
				-\dfrac{r u_{3, t} C(x_{3, t-1})}{3} 
			\right) dt \\
		x_{3, t - 1} + (\dfrac{u_{1, t} + u_{2, t} + u_{3, t}}{3l}) r dt
	\end{bmatrix}
\end{align*}

If we linearize the above w.r.t $x_{1}, x_{2}, x_{3}$ we get:

\begin{align}
	% w.r.t x_1
	\frac{\delta{g}}{\delta{x_{1}}} &=
	\begin{bmatrix}
			1 \\ 
			0 \\ 
			0
	\end{bmatrix} \\
	% w.r.t x_2
	\frac{\delta{g}}{\delta{x_{2}}} &=
		\begin{bmatrix} 
			0 \\ 
			1 \\ 
			0
		\end{bmatrix} \\
	% w.r.t x_3
	\frac{\delta{g}}{\delta{x_{3}}} &=
	\begin{bmatrix}
			0 \\ 
			0 \\ 
			1
	\end{bmatrix} \\
	% putting it back together
%	\frac{\delta{g}}{\delta{x}} &=
%		\begin{bmatrix}
%			
%		\end{bmatrix} \\
\end{align}

As for the measurement model, because it is linear we do not need to linearize 
it.

\newpage
\section{Implementing the Extended Kalman Filter}

\end{document}

### 2016-02-11 homework/homework_1/src/ekf.m

@@ -1,0 +1,104 @@
+% Extended Kalman filter example
+clear;clc;
+
+% Create AVI object
+makemovie = 1;
+if(makemovie)
+    vidObj = VideoWriter('ekf.avi');
+    vidObj.Quality = 100;
+    vidObj.FrameRate = 8;
+    open(vidObj);
+end
+
+% Discrete time step
+dt = 0.1;
+
+% Initial State
+x0 = [20 -2 3]';
+
+% Prior
+mu = [22 -1.8 6.5]'; % mean (mu)
+S = 1*eye(3);% covariance (Sigma)
+
+% Discrete motion model
+Ad = [ 1 dt 0 ; 0 1 0; 0 0 1];
+
+R = [.0001 0 0; 0 .0001 0 ; 0 0 .0001];
+[RE, Re] = eig (R);
+
+% Measurement model defined below
+Q = [.0001];
+
+% Simulation Initializations
+Tf = 10;
+T = 0:dt:Tf;
+n = length(Ad(1,:));
+x = zeros(n,length(T));
+x(:,1) = x0;
+m = length(Q(:,1));
+y = zeros(m,length(T));
+mup_S = zeros(n,length(T));
+mu_S = zeros(n,length(T));
+
+
+
+%% Plot results
+figure(1);
+clf; 
+hold on;
+
+%% Main loop
+for t=2:length(T)
+    %% Simulation
+    % Select a motion disturbance
+    e = RE * sqrt(Re) * randn(n,1);
+    % Update state
+    x(:,t) = Ad * x(:,t-1) + e;
+
+    % Take measurement
+    % Select a motion disturbance
+    d = sqrt(Q)*randn(m,1);
+    % Determine measurement
+    y(:,t) = sqrt(x(1,t)^2 + x(3,t)^2) + d;
+
+
+    %% Extended Kalman Filter Estimation
+    % Prediction update
+    mup = Ad*mu;
+    Sp = Ad*S*Ad' + R;
+
+    % Linearization
+    Ht = [(mup(1))/(sqrt(mup(1)^2 + mup(3)^2)) 0 (mup(3))/(sqrt(mup(1)^2 + mup(3)^2))];
+
+    % Measurement update
+    K = Sp*Ht'*inv(Ht*Sp*Ht'+Q);
+    mu = mup + K*(y(:,t)-sqrt(mup(1)^2 + mup(3)^2));
+    S = (eye(n)-K*Ht)*Sp;
+
[…]

### 2016-02-11 homework/homework_1/src/omni_robot_1.m

@@ -1,0 +1,67 @@
+% clear environment
+clear;
+clc;
+close all;
+
+% simulation parameters
+t_end = 15;
+dt = 0.01;  % 10 Hz
+t = 0:dt:t_end;
+
+% model parameters
+r = 0.25;
+l = 0.30;
+omega_1 = -15.5;
+omega_2 = 10.5;
+omega_3 = 1.5;
+stddev_x = 0.05;
+stddev_y = 0.05;
+stddev_theta = 0.05;
+
+% wheel input commands
+n = length(t);
+
+% J_1, J_2 and x_t (state)
+J_1 = [
+    0, 1, l;
+    -cos(pi / 6), -sin(pi / 6), l;
+    cos(pi / 6), -sin(pi / 6), l;
+];
+J_2 = [
+    r, 0.0, 0.0;
+    0.0, r, 0.0;
+    0.0, 0.0, r;
+];
+x_t = [
+    0;
+    0;
+    0
+];
+
+% simulation
+for i = 1:length(t)
+    theta = x_t(3, i);
+    R = [cos(theta), -sin(theta), 0; sin(theta), cos(theta), 0; 0, 0, 1;];
+    omega = [omega_1; omega_2; omega_3];
+    additive_noise = [
+        normrnd(0, stddev_x);
+        normrnd(0, stddev_y);
+        normrnd(0, stddev_theta);
+    ];
+
+    x_dt = inv(R) * inv(J_1) * J_2 * omega;
+    x_t(:,i + 1) = x_t(:,i) + x_dt * dt;
+end
+
+
+% plot animation
+figure(1);
+clf;
+axis_limits = [ -5 5 -5 5 ];  % x and y-axis limits
+
+for i = 1:2:length(t)
+    plot(x_t(1, 1:i), x_t(2, 1:i), 'bx');
+    axis equal;
+    % axis(axis_limits);
+    drawnow;
+end

### 2016-02-11 homework/homework_1/src/omni_robot_2.m

@@ -1,0 +1,209 @@
+% clear environment
+clear;
+clc;
+close all;
+
+% simulation parameters
+t_end = 50;
+dt = 0.01;  % 10 Hz
+t = 0:dt:t_end;
+
+% model parameters
+r = 0.25;
+l = 0.30;
+
+% J_1, J_2 and x_t (state)
+J_1 = [
+    0, 1, l;
+    -cos(pi / 6), -sin(pi / 6), l;
+    cos(pi / 6), -sin(pi / 6), l;
+];
+J_2 = [
+    r, 0.0, 0.0;
+    0.0, r, 0.0;
+    0.0, 0.0, r;
+];
+
+
+
+
+% simulate robot
+function x_t = simulate(J_1, J_2, omega_inputs, t, dt)
+    x_t = [ 0; 0; 0 ];
+
+    for i = 1:length(t)
+        theta = x_t(3, i);
+        R = [cos(theta), -sin(theta), 0; sin(theta), cos(theta), 0; 0, 0, 1;];
+        omega = [omega_inputs(1); omega_inputs(2); omega_inputs(3);];
+        x_dt = inv(R) * inv(J_1) * J_2 * omega;
+        x_t(:,i + 1) = x_t(:,i) + x_dt * dt;
+    end
+endfunction
+
+% plot animation
+function plot_animation(t, x_t)
+    figure(1);
+    clf;
+    axis_limits = [ -5 5 -5 5 ];  % x and y-axis limits
+
+    for i = 1:2:length(t)
+        plot(x_t(1, 1:i), x_t(2, 1:i), 'bx');
+        axis equal;
+        % axis(axis_limits);
+        drawnow;
+    end
+endfunction
+
+
+
+% apply pre-defined rotation inputs
+% n = length(t);
+% omega_1 = -15.5;
+% omega_2 = 10.5;
+% omega_3 = 1.5;
+% omega_inputs = [
+%     omega_1 * ones(1, n);
+%     omega_2 * ones(1, n);
+%     omega_3 * ones(1, n);
+% ];
+% x_t = simulate(J_1, J_2, omega_inputs, t, dt);
+% plot_animation(t, x_t)
+% print -djpg -color traverse_predefined.jpg
+
+
+
+
+% % traverse east
+% n = length(t);
+% omega_1 = 0;
+% omega_2 = -1;
+% omega_3 = 1;
+% omega_inputs = [
+%     omega_1 * ones(1, n);
[…]

### 2016-02-11 homework/homework_1/src/omni_robot_3.m

@@ -1,0 +1,28 @@
+% clear environment
+clear;
+clc;
+close all;
+
+% creating the motion model
+syms theta r w_1 w_2 w_3 x_1 x_2 x_3 l
+
+R = [
+    cos(theta), -sin(theta), 0;
+    sin(theta), cos(theta), 0;
+    0, 0, 1;
+];
+
+J_1 = [
+    0, 1, l;
+    -cos(pi / 6), -sin(pi / 6), l;
+    cos(pi / 6), -sin(pi / 6), l;
+];
+
+v = [
+    x_1;
+    x_2;
+    x_3
+];
+
+g = inv(R) * inv(J_1) * v;
+simplify(g)

### 2016-02-11 homework/homework_1/src/omni_robot_ekf.m

@@ -1,0 +1,141 @@
+% clear environment
+clear;
+clc;
+
+% model parameters
+r = 0.25;
+l = 0.30;
+omega_1 = -15.5;
+omega_2 = 10.5;
+omega_3 = 1.5;
+
+% syms theta r w_1 w_2 w_3 x_1 x_2 x_3;
+% R = [
+%     cos(theta), -sin(theta), 0;
+%     sin(theta), cos(theta), 0;
+%     0, 0, 1;
+% ];
+% J_1 = [
+%     0, 1, l;
+%     -cos(pi / 6), -sin(pi / 6), l;
+%     cos(pi / 6), -sin(pi / 6), l;
+% ];
+% v = [
+%     x_1;
+%     x_2;
+%     x_3
+% ];
+% g = inv(R) * inv(J_1) * v;
+
+
+% video object
+% makemovie = 1;
+% if(makemovie)
+%     vidObj = VideoWriter('ekf.avi');
+%     vidObj.Quality = 100;
+%     vidObj.FrameRate = 8;
+%     open(vidObj);
+% end
+
+% discrete time step
+dt = 0.1;
+
+% initial State
+x0 = [0 0 0]';
+
+% prior
+mu = [0 0 0]'; % mean (mu)
+S = 1 * eye(3);% covariance (Sigma)
+
+% motion model
+R = [
+    0.1 0 0; 
+    0 0.1 0; 
+    0 0 0.1
+];
+[RE, Re] = eig(R);
+
+% measurement model
+Q = [
+    0.5, 0, 0;
+    0, 0.5, 0;
+    0, 0, deg2rad(10);
+];
+
+% Simulation Initializations
+Tf = 10;
+T = 0:dt:Tf;
+n = length(Ad(1,:));
+x = zeros(n,length(T));
+x(:,1) = x0;
+m = length(Q(:,1));
+y = zeros(m,length(T));
+mup_S = zeros(n,length(T));
+mu_S = zeros(n,length(T));
+
+
+
+%% plot results
+figure(1);
+clf; 
+hold on;
+
+%% main loop
+for t = 2:length(T)
+    % update state
+    e = RE * sqrt(Re) * randn(n,1);
+    x_1 = mu(1);
+    x_2 = mu(2);
+    x_3 = mu(3);
+    g = [
[…]

### 2016-02-12 homework/homework_1/src/Gt.m
starting ekf

@@ -1,0 +1,31 @@
+function [ X_dot ] = Gt(theta,omega_1, omega_2, omega_3)
+%UNTITLED2 Summary of this function goes here
+%   Detailed explanation goes here
+l = 0.3;
+r = 0.25;
+stddev_x = 0.05;
+stddev_y = 0.05;
+stddev_theta = 0.05;
+
+J_1 = [
+    0, 1, l;
+    -cos(pi / 6), -sin(pi / 6), l;
+    cos(pi / 6), -sin(pi / 6), l;
+];
+J_2 = [
+    r, 0.0, 0.0;
+    0.0, r, 0.0;
+    0.0, 0.0, r;
+];
+    
+    R = [cos(theta), -sin(theta), 0; sin(theta), cos(theta), 0; 0, 0, 1;];
+    omega = [omega_1; omega_2; omega_3];
+    additive_noise = [
+        normrnd(0, stddev_x);
+        normrnd(0, stddev_y);
+        normrnd(0, stddev_theta);
+    ];
+    X_dot = inv(R) * inv(J_1) * J_2 * omega;    
+
+end
+

### 2016-02-12 homework/homework_1/src/omni_robot_ekf.m

@@ -9,33 +9,9 @@ omega_1 = -15.5;
 omega_2 = 10.5;
 omega_3 = 1.5;
 
-% syms theta r w_1 w_2 w_3 x_1 x_2 x_3;
-% R = [
-%     cos(theta), -sin(theta), 0;
-%     sin(theta), cos(theta), 0;
-%     0, 0, 1;
-% ];
-% J_1 = [
-%     0, 1, l;
-%     -cos(pi / 6), -sin(pi / 6), l;
-%     cos(pi / 6), -sin(pi / 6), l;
-% ];
-% v = [
-%     x_1;
-%     x_2;
-%     x_3
-% ];
-% g = inv(R) * inv(J_1) * v;
 
 
-% video object
-% makemovie = 1;
-% if(makemovie)
-%     vidObj = VideoWriter('ekf.avi');
-%     vidObj.Quality = 100;
-%     vidObj.FrameRate = 8;
-%     open(vidObj);
-% end
+
 
 % discrete time step
 dt = 0.1;
@@ -87,16 +63,9 @@ for t = 2:length(T)
     x_1 = mu(1);
     x_2 = mu(2);
     x_3 = mu(3);
-    g = [
-        (2*x_1*sin(theta))/3 - (x_2*sin(theta))/3 - (x_3*sin(theta))/3 - (3^(1/2)*x_2*cos(theta))/3 + (3^(1/2)*x_3*cos(theta))/3;
-        (2*x_1*cos(theta))/3 - (x_2*cos(theta))/3 - (x_3*cos(theta))/3 + (3^(1/2)*x_2*sin(theta))/3 - (3^(1/2)*x_3*sin(theta))/3;
-        (x_1 + x_2 + x_3)/(3*l)
-    ];
-    G = [
-        2/3 * sin(theta), 2/3 * cos(theta), 1/(3 * l);
-        -cos(theta)/sqrt(3) - cos(theta)/3, -sin(theta)/sqrt(3) - cos(theta)/3, 1/(3 * l);
-        cos(theta)/sqrt(3) - sin(theta)/3, -sin(theta)/sqrt(3) - cos(theta)/3, 1/(3 * l);
-    ];
+    
+    g = x(:,t - 1) + Gt(mu(3), omega_1, omega_2, omgega_3) * (x(:, t - 1) - mu(:));
+    
     x(:,t) = g + G + e;
 
     % update measurement
@@ -118,6 +87,27 @@ for t = 2:length(T)
     mup_S(:,t) = mup;
[…]

### 2016-02-12 homework/homework_1/report.tex
Update report

@@
 \section{Derivation of the Omni-directional Robot}
+\label{sec:motion_model_derivation}
 
@@
 \section{Applying the Derived Robot Model}
+\label{sec:applying_motion_model}
+
 \subsection{Predefined Rotation Inputs}
+\label{subsec:traverse_inputs}
 Applying the following rotation inputs to the wheel for 15 seconds:
@@
 \subsection{Traversing East, West, North East, South East and Inplace}
+\label{subsec:traverse_directions}
 
@@
 \subsection{Moving in a Circle}
+\label{subsec:traverse_circle}
 
@@
 \subsection{Traversing in a Spiral}
+\label{subsec:traverse_spiral}
 
@@
 \section{Measurement Model}
+\label{sec:measurement_model}
 
@@
 \section{Defining the Extended Kalman Filter for the Omni-directional Robot}
+\label{sec:ekf_defintion}
 
+The Extended Kalman filter (EKF) has two stages, the prediction and measurement 
+updates. To complete the EKF we need to linearize the motion and measurement 
+model, we detail that in the following sections.
+
+\subsection{Linearizing the Motion Model}
+\label{subsec:ekf_motion_model_linearization}
 Normally if our motion model and/or measurement model is linear we can simply 
@@
 Extended Kalman Filter (EKF). In our case we have to linearize the non-linear 
-motion model $g(x_{t-1}, u_{t})$, where:
+motion model $g(x_{t-1}, u_{t})$ using 1st order Taylor Series Expansion:
+
+\begin{align}
+	g(x_{t-1}, u_{t}) 
+	& \approx 	
+		g(\mu_{t - 1}, u_{t}) 
+			+ \dfrac{\partial g(x_{t-1}, u_{t})}{x_{t - 1}} 
+				\bigg|_{x_{t - 1} = \mu_{t - 1}}
+			(x_{t - 1} - \mu_{t - 1}) \\
+	& = g(\mu_{t - 1}, u_{t}) + G_{t} \cdot (x_{t - 1} - \mu_{t - 1})
+\end{align}
+
+Where $G_{t}$ is the first order differential of the non-linear motion model. 
+We have, however, omitted the differentiation because we already know what 
+$G_{t}$ is, since we have already derived the differential of $g(x_{t-1}, 
+u_{t})$ in Section~\ref{sec:motion_model_derivation}.
 
 \begin{equation}
-	\dot{g}(\theta, \omega) =
+	G_{t} = \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
+\end{equation}
+
+Where $R(\theta)$, $J_{1}$, $J_{2}$ and $\omega$ are (derived in 
+Section~\ref{sec:motion_model_derivation}):
+
+\begin{align}
+	R(\theta) &= 
+ 	\begin{bmatrix}
+	    \cos{(\theta)} & -\sin{(\theta)} & 0 \\
+	    \sin{(\theta)} & \cos{(\theta)} & 0 \\
+	    0 & 0 & 1
+    \end{bmatrix} \\
+	J_{1} &= 
+	\begin{bmatrix}
+			0 & 1 & l \\
+  	    	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
+   	    	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
+    \end{bmatrix} \\
+    J_{2} &=
+    \begin{bmatrix}
+        r & 0 & 0 \\
+        0 & r & 0 \\
+        0 & 0 & r
+    \end{bmatrix} \\
+    \omega &= 
+	    \begin{bmatrix}
+	       \omega_{1} \\
+	       \omega_{2} \\
+	       \omega_{3} \\
+	    \end{bmatrix}
+\end{align}
+
+\begin{equation}
+	G_{t} = \dot{g}(\theta, \omega) =
 	\begin{bmatrix}
@@
 			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
-				- \frac{1}{3} \sin(\theta) r \omega_{3} \\
+				- \frac{1}{3} \sin(\theta) r \omega_{3} \\ \\
 		\frac{2}{3} \cos(\theta) r \omega_{1}
@@
 			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
-				-\frac{1}{3} \cos(\theta) r \omega_{3} \\
+				-\frac{1}{3} \cos(\theta) r \omega_{3} \\ \\
 		\frac{1}{3l} r \omega_{1}
@@
 
-Rewriting the above in terms of state $x_{1}, x_{2}, x_{3}$, and inputs $u_{1}, u_{2}, u_{3}$, where $S$ and $C$ short hand for $sin$ and $cos$ functions.
+\newpage
+\subsection{Linearizing the Measurement Model}
+\label{subsec:ekf_measurement_model_linearization}
 
-\begin{align*}
-	& g(x_{t-1}, u_{t}) = \\
-	& \begin{bmatrix}
-		x_{1, t - 1} + \left(
-			\dfrac{2 r u_{1, t} S(x_{3, t-1})}{3}
-			- \dfrac{r u_{2, t} C(x_{3, t-1})}{\sqrt{3}}
-				- \dfrac{r u_{2, t} S(x_{3, t-1})}{3}
-			+ \dfrac{r u_{3, t} C(x_{3, t-1})}{\sqrt{3}} 
-				- \dfrac{r u_{3, t} S(x_{3, t-1})}{3}
-			\right) dt \\\
-		x_{2, t - 1} + \left( 
-			\dfrac{2 r u_{1, t} C(x_{3, t-1})}{3}
-			+ \dfrac{r u_{2, t} S(x_{3, t-1})}{\sqrt{3}}
-				-\dfrac{r u_{2, t} C(x_{3, t-1})}{3}
-			- \dfrac{r u_{3, t} S(x_{3, t-1})}{\sqrt{3}}
-				-\dfrac{r u_{3, t} C(x_{3, t-1})}{3} 
-			\right) dt \\
-		x_{3, t - 1} + (\dfrac{u_{1, t} + u_{2, t} + u_{3, t}}{3l}) r dt
+As for the measurement model, it does not require linearization since in 
+Section~\ref{sec:measurement_model} we derived a linear measurement model. 
+Therefore $H_{t} = C_{t}$.
+
+\begin{equation}
+	H_{t} = C_{t} = 
+	\begin{bmatrix}
+		1 & 0 & 0 \\
+		0 & 1 & 0 \\
+		0 & 0 & 1
 	\end{bmatrix}
-\end{align*}
+\end{equation}
 
-If we linearize the above w.r.t $x_{1}, x_{2}, x_{3}$ we get:
+\subsection{Summary}
+\label{subsec:ekf_def_summary}
 
-\begin{align}
-	% w.r.t x_1
-	\frac{\delta{g}}{\delta{x_{1}}} &=
-	\begin{bmatrix}
-			1 \\ 
-			0 \\ 
-			0
-	\end{bmatrix} \\
-	% w.r.t x_2
-	\frac{\delta{g}}{\delta{x_{2}}} &=
-		\begin{bmatrix} 
-			0 \\ 
-			1 \\ 
-			0
-		\end{bmatrix} \\
-	% w.r.t x_3
-	\frac{\delta{g}}{\delta{x_{3}}} &=
-	\begin{bmatrix}
-			0 \\ 
-			0 \\ 
-			1
-	\end{bmatrix} \\
-	% putting it back together
-%	\frac{\delta{g}}{\delta{x}} &=
-%		\begin{bmatrix}
-%			
-%		\end{bmatrix} \\
-\end{align}
-
-As for the measurement model, because it is linear we do not need to linearize 
-it.
+Now that we have defined what $g(x_{t - 1})$, $G_{t}$ and $H_{t}$ (along with
+ intial values for the states) we have enough information to incorporate them
+  into the EKF model.
 
@@
 
+In the EKF we have used the following values:
+
+\begin{align*}
+	\mu_{0} &= 
+		\begin{bmatrix}
+			0 \\
+			0 \\
+			0
+		\end{bmatrix} \\
+	u_{0} &= 
+	\begin{bmatrix}
+		-15.5 \\
+		-10.5 \\
+		1.5
+	\end{bmatrix} \\
+	H_{t} &=
+	\begin{bmatrix}
+		1 & 0 & 0 \\
+		0 & 1 & 0 \\
+		0 & 0 & 1
+	\end{bmatrix} \\
+	G_{t} &= \dot{g}(\theta, \omega) \\
+		&= R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
+	    \begin{bmatrix}
+	        \dot{x} \\
+	        \dot{y} \\
+	        \dot{\theta}
+	    \end{bmatrix} \\
+	    &= 
+	        \begin{bmatrix}
+		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
+		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
+		        0 & 0 & 1
+	        \end{bmatrix}^{-1}
+	        \begin{bmatrix}
+	            0 & 1 & l \\
+	          	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
+	        	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
+	        \end{bmatrix}^{-1}
+	        \begin{bmatrix}
+	            r & 0 & 0 \\
+	            0 & r & 0 \\
+	            0 & 0 & r
+	        \end{bmatrix}
+		    \begin{bmatrix}
+		       \omega_{1} \\
+		       \omega_{2} \\
+		       \omega_{3} \\
+		    \end{bmatrix} \\
+\end{align*}
+
 \end{document}

### 2016-02-12 homework/homework_1/src/OmniRobot.m
added plotting functionality

@@ -34,6 +34,8 @@ classdef OmniRobot
             0, 0.5, 0;
             0, 0, deg2rad(10);
         ];
+        
+       
     
     end
     
@@ -59,7 +61,7 @@ classdef OmniRobot
             0;
         ];  % mean (mu)  
     end
-
+   
     methods
         function [G] = G(this, theta, omega)
             % constant terms
@@ -148,7 +150,7 @@ classdef OmniRobot
 
                 % store results
                 mup_S(:,t) = mup;
-                mu_S(:,t) = mu;                
+                mu_S(:,t) = mu;
                 
                 % plot results
 %                 figure(1);
@@ -173,7 +175,15 @@ classdef OmniRobot
                     writeVideo(vidthis, getframe(gca)); 
                 end
             end
+            plot_results = true;
+            if plot_results == true
+                this.plot_results(mu_S, x, T, S)
+            end
             
+        end
+        
+        function plot_results(~,mu_S, x, T, S)
+            % plot the true state and belief for x, y, heading
             figure(1);
             clf; 
             
@@ -195,13 +205,42 @@ classdef OmniRobot
             plot(T, x(2,:), 'ro--', T, mu_S(2,:), 'bx--');
             title('True state and belief (y-axis)');
             xlabel('Time (s)')
-            ylabel('Displacement (m)')            
+            ylabel('Displacement (m)')
+            
+            
+            %plot error elipse over time
+            for t = 2:length(T)
+                figure(2);
+                %clf;
+                hold on;
+                pause(0.1);
+                %mup = mup_S(:,t);
+                mu = mu_S(:,t);
+                
+
+                plot(x(1, 2:t), x(2, 2:t), 'ro--')
+                plot(mu_S(1, 2:t), mu_S(2, 2:t), 'bx--')
+
+                mu_pos = [mu(1) mu(2)];
+                S_pos = [S(1,1) S(1,3); S(3,1) S(3,3)];
+                error_ellipse(S_pos, mu_pos, 0.75);
+                error_ellipse(S_pos, mu_pos, 0.95);
+
+                title('True state and belief')
+                axis equal
+                axis([-1 8 -6 3])
+            end
+
             
             % close movie thisect
-            if (makemovie) 
-                close(vidthis); 
-            end
+%            if (makemovie) 
+%                close(vidthis); 
+ %           end
+            
         end
-    end
+            
+            
+   end
+   
 end
 

### 2016-02-12 homework/homework_1/report.tex
Update report

@@
 		0 & 0.5 & 0 \\
-		0 & 0 & 10		
+		0 & 0 & 0.1745		
 	\end{bmatrix}
@@
 
-With a mean $\mu$ of:
+Note that 10 degrees is 0.1745 radians. With a mean $\mu$ of:
 
@@
 
-Where $G_{t}$ is the first order differential of the non-linear motion model. 
-We have, however, omitted the differentiation because we already know what 
-$G_{t}$ is, since we have already derived the differential of $g(x_{t-1}, 
-u_{t})$ in Section~\ref{sec:motion_model_derivation}.
+Where $G_{t}$ is the first order differential of the non-linear motion model, 
+a.k.a the Jacobian of $g(x_{t-1}, u_{t})$.
 
 \begin{equation}
-	G_{t} = \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
+	G_{t} = \begin{bmatrix}
+		\dfrac{\partial g_{1}}{\partial x_{1}}
+		& \dfrac{\partial g_{1}}{\partial x_{2}} 
+		& \dfrac{\partial g_{1}}{\partial x_{3}} \\ \\
+		\dfrac{\partial g_{2}}{\partial x_{1}}
+		& \dfrac{\partial g_{2}}{\partial x_{2}} 
+		& \dfrac{\partial g_{2}}{\partial x_{3}} \\ \\
+		\dfrac{\partial g_{3}}{\partial x_{1}}
+		& \dfrac{\partial g_{3}}{\partial x_{2}} 
+		& \dfrac{\partial g_{3}}{\partial x_{3}}
+	\end{bmatrix}
+\end{equation}
+
+Since we only know $\dot{g}(\theta, \omega)$ we need to convert it to 
+$g(x_{t-1}, u_{t})$, it is simply:
+
+\begin{align}
+	g(x_{t-1}, u_{t}) 
+		&= x_{t - 1} + \dot{g}(\theta, \omega) dt \\
+		&= \begin{bmatrix}
+			x_{1, t - 1} + \dot{g_{1}}(\theta, \omega) dt \\ \\
+			x_{2, t - 1} + \dot{g_{2}}(\theta, \omega) dt \\ \\
+			x_{3, t - 1} + \dot{g_{3}}(\theta, \omega) dt \\
+		\end{bmatrix}
+\end{align}
+
+Now that we have $g(x_{t-1}, u_{t})$ we can work out the Jacobian. One 
+important note, the partial derivate of $x_{3}$ in our case is the bearing  
+$\theta$ of the robot, the only term affected in $\dot{g}(\theta, \omega)$ is 
+the rotation matrix $R(\theta)$, since $\dot{g}(\theta, \omega)$ is:
+
+\begin{equation}
+    \dot{g}(\theta, \omega) = R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
 \end{equation}
@@
 \begin{align}
-	R(\theta) &= 
+	R(\theta)^{-1} &= 
  	\begin{bmatrix}
-	    \cos{(\theta)} & -\sin{(\theta)} & 0 \\
-	    \sin{(\theta)} & \cos{(\theta)} & 0 \\
+	    \cos{(\theta)} & \sin{(\theta)} & 0 \\
+	    -\sin{(\theta)} & \cos{(\theta)} & 0 \\
 	    0 & 0 & 1
     \end{bmatrix} \\
-	J_{1} &= 
+	J_{1}^{-1} &= 
 	\begin{bmatrix}
-			0 & 1 & l \\
-  	    	-\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l \\
-   	    	\cos(\frac{\pi}{6}) & -\sin(\frac{\pi}{6}) & l
+		0 & -\frac{1}{\sqrt{3}} & \frac{1}{\sqrt{3}} \\ \\
+		\frac{2}{3} & -\frac{1}{3} & -\frac{1}{3} \\ \\
+		\frac{1}{3l} & \frac{1}{3l} & \frac{1}{3l}
 	\end{bmatrix} \\
@@
 
+Therefore to differentiate rotation matrix $R(\theta)$ with respect to $x_{3}$ 
+(or $\theta$), we can treat $J_{1}$ $J_{2}$ and $\omega$ as constant vector 
+$A$. The partial derivative of $R(\theta)$ then becomes:
+
 \begin{equation}
-	G_{t} = \dot{g}(\theta, \omega) =
+	\dfrac{\partial R(\theta)^{-1}}{\partial x_{3}} = 
 	\begin{bmatrix}
-		\frac{2}{3} \sin(\theta) r \omega_{1}
-			- \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{2}
-				- \frac{1}{3} \sin(\theta) r \omega_{2}
-			+ \frac{1}{\sqrt{3}} \cos(\theta) r \omega_{3}
-				- \frac{1}{3} \sin(\theta) r \omega_{3} \\ \\
-		\frac{2}{3} \cos(\theta) r \omega_{1}
-			+ \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{2}
-				-\frac{1}{3} \cos(\theta)r \omega_{2}
-			- \frac{1}{\sqrt{3}} \sin(\theta) r \omega_{3}
-				-\frac{1}{3} \cos(\theta) r \omega_{3} \\ \\
-		\frac{1}{3l} r \omega_{1}
-			+ \frac{1}{3l} r \omega_{2}
-			+ \frac{1}{3l} r \omega_{3}
+		-\sin(x_{3}) & \cos(x_{3}) & 0 \\ \\
+		-\cos(x_{3}) & -\sin(x_{3}) & 0 \\ \\
+		0 & 0 & 0
+	\end{bmatrix}
+\end{equation}
+
+\begin{equation}
+	A = J_{1}^{-1} J_{2} \omega
+\end{equation}
+
+Or in terms of $g$ and $x$.
+
+\begin{align}
+	\dfrac{\partial g}{\partial x_{3}} 
+	&= \dfrac{\partial R(\theta)^{-1}}{\partial x_{3}} A \\
+	&= \begin{bmatrix}
+		-\sin(x_{3}) & \cos(x_{3}) & 0 \\
+		-\cos(x_{3}) & -\sin(x_{3}) & 0 \\
+		0 & 0 & 0
+	\end{bmatrix}
+	\begin{bmatrix}
+		A_{1} \\
+		A_{2} \\
+		A_{3}
+	\end{bmatrix} \\
+	&= \begin{bmatrix}
+		-A_{1} sin(x_{3}) + A_{2} cos(x_{3}) \\
+		-A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
+		0
+	\end{bmatrix}
+\end{align}
+
+Completing our Jacobian $G_{t}$ we get:
+
+\begin{equation}
+	G_{t} = \begin{bmatrix}
+		1 & 0 & -A_{1} sin(x_{3}) + A_{2} cos(x_{3})  \\
+		0 & 1 & -A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
+		0 & 0 & 1
 	\end{bmatrix}
@@
 	\end{bmatrix} \\
-	G_{t} &= \dot{g}(\theta, \omega) \\
-		&= R(\theta)^{-1} J_{1}^{-1} J_{2} \omega
-	    \begin{bmatrix}
-	        \dot{x} \\
-	        \dot{y} \\
-	        \dot{\theta}
+	G_{t} 
+		&= \begin{bmatrix}
+			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
+			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
+			0 & 0 & 1
 		\end{bmatrix} \\

### 2016-02-12 homework/homework_1/src/OmniRobot.m
fixed the covariance mtrx

@@ -23,16 +23,16 @@ classdef OmniRobot
     
         % motion disturbance
         R = [
-            0 0 0; 
-            0 0 0; 
-            0 0 0;
+            0.05^2 0 0; 
+            0 0.05^2 0; 
+            0 0 deg2rad(0.5)^2;
         ];
     
         % measurement disturbance
         Q = [
-            0.5, 0, 0;
-            0, 0.5, 0;
-            0, 0, deg2rad(10);
+            0.5^2, 0, 0;
+            0, 0.5^2, 0;
+            0, 0, deg2rad(10^2);
         ];
         
        
@@ -115,6 +115,7 @@ classdef OmniRobot
             % save states
             mup_S = zeros(n, length(T));
             mu_S = zeros(n, length(T));
+            St = zeros(n,n,length(T));
           
             % create AVI thisect
             makemovie = 0;
@@ -131,14 +132,14 @@ classdef OmniRobot
                 e = RE * sqrt(Re) * randn(n,1);
                 G = this.G(mu(3), omega);
                 x(:,t) = x(:,t-1) + this.g(x(3, t - 1), omega) * this.dt + e;
-
+                
                 % update measurement
                 d = DE * sqrt(De) * randn(m, 1);
-                y(:,t) = x(:,t) + d;
+                y(:,t) = x(:,t) + d + [0; 0; deg2rad(-9.7)];
 
                 % EKF
                 % prediction update
-                mup = x(:,t);
+                mup = mu + this.g(mu(3), omega) * this.dt;
                 Sp = G * S * G' + this.R;
 
                 % measurement update
@@ -147,10 +148,12 @@ classdef OmniRobot
                 mu = mup + K * (y(:,t) - Ht * mup);
 
                 S = (eye(n) - K * Ht) * Sp;
+                
 
                 % store results
                 mup_S(:,t) = mup;
                 mu_S(:,t) = mu;
+                St(:,:,t) = S; 
                 
                 % plot results
 %                 figure(1);
@@ -177,17 +180,17 @@ classdef OmniRobot
             end
             plot_results = true;
             if plot_results == true
-                this.plot_results(mu_S, x, T, S)
+                this.plot_results(mu_S, x, T, St)
             end
             
         end
         
-        function plot_results(~,mu_S, x, T, S)
+        function plot_results(~,mu_S, x, T, St)
             % plot the true state and belief for x, y, heading
[…]

### 2016-02-12 homework/homework_1/src/omni_robot_ekf.m

@@ -1,6 +1,7 @@
 % clear environment
 clear;
 clc;
+close all;
 
 robot = OmniRobot();
 robot.simulateEKF();

### 2016-02-12 homework/homework_1/report.tex
Update report

@@
 	        \begin{bmatrix}
-		        \cos{(\theta)} & -\sin{(\theta)} & 0 \\
-		        \sin{(\theta)} & \cos{(\theta)} & 0 \\
+       			1 & 0 & -A_{1} sin(x_{3}) - A_{2} cos(x_{3})  \\
+       			0 & 1 & A_{1} cos(x_{3}) - A_{2} sin(x_{3}) \\
        			0 & 0 & 1
 	        \end{bmatrix}^{-1}
+	        A \\
+	A_{t}
+		&= J_{1}^{-1} J_{2} \omega \\		
+		&=
 			\begin{bmatrix}
@@
 
+\newpage
+\section{Adding GPS corrections to the EKF}
+
+Previously it was assumed that the GPS and Magnetometer both work at a rate of 
+10hz, however it is given that "corrections are sent for the x, y positions of 
+the vechicle at an update rate of 1Hz. These corections improve the GPS 
+measurements at that instance only, with an improved standard deviation of 
+0.01m". This means that the measurement disturbance $Q$ changes over time (i.e. 
+every 1Hz) from:
+
+\begin{equation}
+	Q = 
+	\begin{bmatrix}
+		0.5 & 0 & 0 \\
+		0 & 0.5 & 0 \\
+		0 & 0 & 0.1745		
+	\end{bmatrix}
+\end{equation}
+
+to (at every 1Hz):
+
+\begin{equation}
+	Q = 
+	\begin{bmatrix}
+		0.1 & 0 & 0 \\
+		0 & 0.1 & 0 \\
+		0 & 0 & 0.1745		
+	\end{bmatrix}
+\end{equation}
+
 \end{document}

### 2016-02-12 homework/homework_1/src/OmniRobot.m

@@ -23,20 +23,17 @@ classdef OmniRobot
     
         % motion disturbance
         R = [
-            0 0 0; 
-            0 0 0; 
-            0 0 0;
+            0.00000001^2 0 0; 
+            0 0.00000001^2 0; 
+            0 0 0.00000001^2;
         ];
     
         % measurement disturbance
         Q = [
-            0.5, 0, 0;
-            0, 0.5, 0;
-            0, 0, deg2rad(10);
+            1.1^2, 0, 0;
+            0, 10, 0;
+            0, 0, 0.00000001^2;
         ];
-        
-       
-    
     end
     
     % SIMULATION PROPERTIES
@@ -80,7 +77,7 @@ classdef OmniRobot
             G(1:2, 3) = dRot_A(1:2);
         end
         
-        function x = g(this, theta, omega)
+        function x = g_dot(this, theta, omega)
             Rot = [
                 cos(theta), -sin(theta), 0;
                 sin(theta), cos(theta), 0; 
@@ -130,22 +127,22 @@ classdef OmniRobot
                 omega = [omega_1; omega_2; omega_3];
                 e = RE * sqrt(Re) * randn(n,1);
                 G = this.G(mu(3), omega);
-                x(:,t) = x(:,t-1) + this.g(x(3, t - 1), omega) * this.dt + e;
+                x(:,t) = x(:,t-1) + this.g_dot(x(3, t - 1), omega) * this.dt + e;
 
                 % update measurement
                 d = DE * sqrt(De) * randn(m, 1);
+                d
                 y(:,t) = x(:,t) + d;
 
                 % EKF
                 % prediction update
-                mup = x(:,t);
-                Sp = G * S * G' + this.R;
+                mup = mu + this.g_dot(mu(3), omega) * this.dt;
+                Sp = G * S * transpose(G) + this.R;
 
                 % measurement update
                 Ht = eye(3);
                 K = Sp * Ht' * inv(Ht * Sp * transpose(Ht) + this.Q);
                 mu = mup + K * (y(:,t) - Ht * mup);
-
                 S = (eye(n) - K * Ht) * Sp;
 
                 % store results
@@ -193,7 +190,7 @@ classdef OmniRobot
             xlabel('Displacement in x-direction (m)')
             ylabel('Displacement in y-direction (m)')
             axis equal
-            axis([-1 8 -6 3])
[…]

### 2016-02-12 homework/homework_1/report.tex
Update report
Add traverse with noise images

@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.65\textwidth]{images/traverse_predefined_with_noise.jpg}
+	\caption{Same as Fig~\ref{fig:omni_robot_predefined} but with Additive 
+	Gaussian Noise}
+	\label{fig:omni_robot_predefined_with_noise}
+\end{figure}
+
 \subsection{Traversing East, West, North East, South East and Inplace}
@@
 
+\begin{figure}[H]
+	\centering
+
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_east_with_noise.jpg}
+		\caption{Traverse East}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_west_with_noise.jpg}
+		\caption{Traverse West}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_north_east_with_noise.jpg}
+		\caption{Traverse North East}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_south_east_with_noise.jpg}
+		\caption{Traverse South East}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.32\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_inplace_with_noise.jpg}
+		\caption{Traverse Inplace}
+	\end{subfigure}
+
+	\caption{Same as Fig~\ref{fig:omni_robot_traverse} but with Additive 
+	Gaussian Noise}
+	\label{fig:omni_robot_traverse_with_noise}
+\end{figure}
+
 The inputs that drove the robot to traverse in the directions shown in 
-Fig~\ref{fig:omni_robot_traverse} for 15 seconds  are as follows:
+Fig~\ref{fig:omni_robot_traverse} and 
+Fig~\ref{fig:omni_robot_traverse_with_noise}  for 15 
+seconds  are as follows:
 
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{images/traverse_circle.jpg}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/traverse_circle.jpg}
+		\caption{Without Noise}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/traverse_circle_with_noise.jpg}
+		\caption{With Noise}
+	\end{subfigure}
 	\caption{Omni-Robot Traversing a Circle}
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{images/traverse_spiral.jpg}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_spiral.jpg}
+		\caption{Without Noise}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/traverse_spiral_with_noise.jpg}
+		\caption{With Noise}
+	\end{subfigure}
 	\caption{Omni-Robot Traversing a Spiral}
@@
 	\begin{bmatrix}
-		0.5 & 0 & 0 \\
-		0 & 0.5 & 0 \\
-		0 & 0 & 0.1745		
+		0.5^{2} & 0 & 0 \\
+		0 & 0.5^{2} & 0 \\
+		0 & 0 & 0.1745^{2}		
 	\end{bmatrix}
@@
 	\begin{bmatrix}
-		0.1 & 0 & 0 \\
-		0 & 0.1 & 0 \\
-		0 & 0 & 0.1745		
+		0.1^{2} & 0 & 0 \\
+		0 & 0.1^{2} & 0 \\
+		0 & 0 & 0.1745^{2}		
 	\end{bmatrix}

### 2016-02-12 homework/homework_1/src/OmniRobot.m

@@ -128,7 +128,7 @@ classdef OmniRobot
                 omega = [omega_1; omega_2; omega_3];
                 e = RE * sqrt(Re) * randn(n,1);
                 G = this.G(mu(3), omega);
-                x(:,t) = x(:,t-1) + this.g(x(3, t - 1), omega) * this.dt + e;
+                x(:,t) = x(:,t-1) + this.g_dot(x(3, t - 1), omega) * this.dt + e;
                 
                 % update measurement
                 d = DE * sqrt(De) * randn(m, 1);
@@ -136,7 +136,7 @@ classdef OmniRobot
 
                 % EKF
                 % prediction update
-                mup = mu + this.g(mu(3), omega) * this.dt;
+                mup = mu + this.g_dot(mu(3), omega) * this.dt;
                 Sp = G * S * G' + this.R;
 
                 % measurement update

### 2016-02-12 homework/homework_1/src/OmniRobot.m
WE IS DONE NOW GIBS FUD

@@ -92,6 +92,12 @@ classdef OmniRobot
         function simulateEKF(this)
             T = 0:this.dt:this.Tf;
             
+            Q_better = [
+                .01^2, 0, 0;
+                0, .01^2, 0;
+                0, 0, deg2rad(10^2);
+            ];
+            
             % state
             n = length(this.x_0);
             x = zeros(n, length(T));
@@ -101,12 +107,13 @@ classdef OmniRobot
             mu = this.mu_0;
             S = 1 * eye(3);  % covariance (Sigma)
             [RE, Re] = eig(this.R);
+            
 
             % measurement related
             m = length(this.Q(:, 1));
             y = zeros(m, length(T));
-            [DE, De] = eig(this.Q);
-
+            
+            
             % inputs
             omega_1 = -15.5;
             omega_2 = 10.5;
@@ -117,14 +124,7 @@ classdef OmniRobot
             mu_S = zeros(n, length(T));
             St = zeros(n,n,length(T));
           
-            % create AVI thisect
-            makemovie = 0;
-            if(makemovie)
-                vidthis = VideoWriter('ekf.avi');
-                vidthis.Quality = 100;
-                vidthis.FrameRate = 8;
-                open(vidthis);
-            end       
+                 
             
             for t = 2:length(T)
                 % update state
@@ -134,7 +134,20 @@ classdef OmniRobot
                 x(:,t) = x(:,t-1) + this.g(x(3, t - 1), omega) * this.dt + e;
                 
                 % update measurement
-                d = DE * sqrt(De) * randn(m, 1);
+                if mod(T(t),1) == 0 % every 1 second use gps correction
+                    [DE, De] = eig(Q_better);
+                    d = DE * sqrt(De) * randn(m, 1);
+                    Q_t = Q_better;
+                else
+                    [DE, De] = eig(this.Q);
+                    d = DE * sqrt(De) * randn(m, 1); 
+                    Q_t = this.Q;
+                end
+                
+%                 [DE, De] = eig(this.Q);
+%                 d = DE * sqrt(De) * randn(m, 1);
+%                 Q_t = this.Q;
+
                 y(:,t) = x(:,t) + d + [0; 0; deg2rad(-9.7)];
 
                 % EKF
@@ -143,8 +156,8 @@ classdef OmniRobot
                 Sp = G * S * G' + this.R;
 
                 % measurement update
-                Ht = eye(3);
[…]

### 2016-02-12 homework/homework_1/src/omni_robot_ekf.m

@@ -1,6 +1,6 @@
 % clear environment
 clear;
-clc;
+%clc;
 close all;
 
 robot = OmniRobot();

### 2016-02-24 include/awesomo/camera.hpp
Add ability to accurately obtain AprilTag pose estimates

@@ -17,12 +17,24 @@
 #include <AprilTags/TagDetector.h>
 #include <AprilTags/Tag16h5.h>
 
+#include <yaml-cpp/yaml.h>
+
 
 class Camera
 {
     private:
         AprilTags::TagDetector* tag_detector;
 
+        int camera_index;
+        int image_width;
+        int image_height;
+
+        cv::Mat camera_matrix;
+        cv::Mat rectification_matrix;
+        cv::Mat distortion_coefficients;
+        cv::Mat projection_matrix;
+
+        void loadCalibrationFile(const std::string calibration_fp);
         void printFPS(double &last_tic, int &frame);
         float calculateFocalLength(void);
         double standardRad(double t);
@@ -36,13 +48,9 @@ class Camera
         int processImage(cv::Mat &image, cv::Mat &image_gray);
 
     public:
-        int camera_index;
-        int image_width;
-        int image_height;
-
         vector<AprilTags::TagDetection> apriltags;
 
-        Camera(void);
+        Camera(int camera_index, const std::string calibration_fp);
         int run(void);
 };
 

### 2016-02-24 src/camera.cpp

@@ -9,13 +9,88 @@ static double tic(void)
 }
 
 
-Camera::Camera(void)
+Camera::Camera(int camera_index, const std::string calibration_fp)
 {
     this->tag_detector = new AprilTags::TagDetector(AprilTags::tagCodes16h5);
+    this->camera_index = camera_index;
+    this->loadCalibrationFile(calibration_fp);
+}
 
-    this->camera_index = 0;
-    this->image_width = 680;
-    this->image_height = 480;
+static int checkMatrixYaml(YAML::Node matrix_yaml)
+{
+    const std::string targets[3] = { "rows", "cols", "data" };
+
+    // pre-check
+    if (matrix_yaml == NULL) {
+        return -1;
+    }
+
+    for (int i = 0; i < 3; i++) {
+        if (!matrix_yaml[targets[i]]) {
+            return -1;
+        }
+    }
+
+    return 0;
+}
+
+static cv::Mat loadMatrixFromYaml(YAML::Node matrix_yaml)
+{
+    int rows;
+    int cols;
+    int index;
+    double value;
+
+    // load matrix
+    rows = matrix_yaml["rows"].as<int>();
+    cols = matrix_yaml["cols"].as<int>();
+    cv::Mat mat(rows, cols, CV_64F);
+
+    index = 0;
+    for (int i = 0; i < rows; i++) {
+        for (int j = 0; j < cols; j++) {
+            value = matrix_yaml["data"][index].as<double>();
+            mat.at<double>(i, j) = value;
+            index++;
+        }
+    }
+
+    return mat;
+}
+
+void Camera::loadCalibrationFile(const std::string calibration_fp)
+{
+    YAML::Node config = YAML::LoadFile(calibration_fp);
+
+    // image width
+    if (config["image_width"]) {
+        this->image_width = config["image_width"].as<int>();
+    }
+
+    // image height
+    if (config["image_height"]) {
+        this->image_height = config["image_height"].as<int>();
+    }
+
+    // camera matrix
+    if (config["camera_matrix"]) {
+        this->camera_matrix = loadMatrixFromYaml(config["camera_matrix"]);
+    }
+
+    // distortion coefficients
+    if (config["distortion_coefficients"]) {
+        this->distortion_coefficients = loadMatrixFromYaml(config["distortion_coefficients"]);
+    }
+
+    // rectification matrix
+    if (config["rectification_matrix"]) {
[…]

### 2016-02-24 docs/interim_report/interim_report.tex
Update docs

\documentclass{article}[12pt]

% GRAPHICS
\usepackage{float}
\usepackage{graphicx}

% HYPERLINKS
\usepackage{hyperref}

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.2in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

%COMMENTING
\usepackage{comment}

\begin{document}

% TITLE
\title{Autonomous Quadrotor Landing on a Moving Platform}
\author{Stan Brown \& Chris Choi}
\date{}
\maketitle

\section*{Introduction}
Our goal is to autonomously land a quadrotor onto a moving platform. In this 
interim-report we will discuss our efforts so far, and any preliminary results 
we may have. So far we have spent a considerable amount of effort getting 
different components of the project working. In this report we will be 
discussing progress in both hardware and software aspects of the project, 
specifically:

\begin{itemize}
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{Quadrotor Setup and Onboard Computer}
	\item{Camera}
\end{itemize}

\section*{Hardware}
For the hardware, we have chosen to reuse equipment that is readily available 
to us in the Wave Lab. For the quadrotor we are using

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v1.5}
\end{figure}

\section*{Software}
\subsection*{Pixhawk Firmware}

\subsection*{Simulator}

\subsection*{AprilTag}

\bibliography{proposal}{}
\bibliographystyle{ieeetr}

\end{document}

### 2016-02-27 docs/interim_report/interim_report.tex
Add interim report

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 \usepackage{titlesec}
-\usepackage[margin=1.2in]{geometry}
+\usepackage[margin=1.5in]{geometry}
 \setlength{\parskip}{\baselineskip}%
@@
 \section*{Introduction}
-Our goal is to autonomously land a quadrotor onto a moving platform. In this 
-interim-report we will discuss our efforts so far, and any preliminary results 
-we may have. So far we have spent a considerable amount of effort getting 
-different components of the project working. In this report we will be 
-discussing progress in both hardware and software aspects of the project, 
-specifically:
+Our goal is to autonomously land a quadrotor onto a moving platform, the main 
+significance of this work is to disgard GPS and perform autonomous precision 
+landing using low cost sensors, such as sonar and vision.
 
-\begin{itemize}
-	\vspace{-0.4cm}
-	\setlength{\itemsep}{0pt}
-	\setlength{\parskip}{0pt}
-	\setlength{\parsep}{0pt}
+In this interim-report we will discuss our progress, and any preliminary 
+results we may have. So far we have spent a considerable amount of effort 
+getting different components of the project working. In this report we will be 
+discussing changes, progress in both hardware and software aspects of the 
+project and remaining project schedule.
 
-	\item{Quadrotor Setup and Onboard Computer}
-	\item{Camera}
-\end{itemize}
+\section*{Changes in Direction or Project Scope}
 
-\section*{Hardware}
+Due to time constraints, we will be forgoing our idea of using gimbal cameras 
+for this project. We initially had hoped we would be using the gimbal camera 
+to locate the landing target from afar and approach the target.
+
+Since we are omitting gimbal cameras, we will be assuming that the 
+quadrotor will be directly above the moving landing target as its intial 
+conditions, and that is where our autonomous system will be to start its 
+autonoums precision landing.
+
+\section*{Project Progress}
+\subsection*{Hardware}
+\subsubsection*{Quadrotor Setup}
 For the hardware, we have chosen to reuse equipment that is readily available 
-to us in the Wave Lab. For the quadrotor we are using
+to us in the Wave Lab. For the quadrotor we have been using the DJI F450 
+quadrotor frame, Emax 2213-935KV motors with complimentary 1045R propellers, 
+Thunder Power lipo 11.1V 4200mah battery, DJI E310 420S 20A electronic speed 
+controller and Pixhawk v2.4 as our flight controller. At current our quadrotor 
+flies reasonably well with some \textit{minor} setbacks, mainly due to the 
+instability of the firmware, and lack of good documentation for the firmware 
+and software packages. Our problems thus far with the quadcopter are mostly 
+software based.
 
@@
 
-\section*{Software}
-\subsection*{Pixhawk Firmware}
+\subsubsection*{Onboard Autonomous Control System}
+In terms of onboard autonoumos control, we have decided to use the Odriod 
+XU4 due to its size and processing power available, and a Logitech C270 HD 
+webcam as our vision sensor. One problem we may face very soon is the narrow 
+field of view and relatively low frame rate (25Hz) the logitech webcam has. We 
+will be keeping our options open, and plan on replacing the logitech webcam 
+with a Ximia xiQ USB3 camera with a wide angle lens in the near 
+future.
 
-\subsection*{Simulator}
+\subsection*{Software}
+\subsubsection*{Pixhawk Firmware}
+As mentioned in the hardware section, we have had numerous issues with 
+regards to using the software suite for the Pixhawk Flight Controller, 
+as well as the PX4 firmware itself. There are many instances where we could not 
+explain the instability of the quadrotor during flight, many of which lead to 
+costly crashes, but we believe through these experiences we have developed a 
+procedure to lower the risk for such instances from happening often.
 
-\subsection*{AprilTag}
+\subsubsection*{Odriod to Pixhawk Communication}
+For our autonomous system to control the quadrotor directly, the Odriod has to 
+be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS 
+package) comes into play. Mavlink is a popular UAV communication protocol 
+between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS 
+node to enable developers to monitor and issue mavlink commands with ease. We 
+have successfully used mavros to arm and disarm Pixhawk (tested), in the near 
+future we should be able to send velocity/attitude commands to control the 
+quadrotor.
+
+\subsubsection*{Simulator}
+Initially we have explored the possibility of using the combination of PX4's 
+Software in the Loop Simulation (SITL) and Gazebo 6 as our simulation 
+environment for our project, however we found the combination of install 
+instructions changing at a fast pace, and the documentation not up to date to 
+be a major concern for us. We have therefore decided to fallback on developing 
+the estimation and control loop in Matlab.
+
+\subsubsection*{AprilTag}
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_1.png}
+		\caption{2 Apriltags Detected}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_3.png}
+		\caption{1 Apriltag Detected }
+	\end{subfigure}
+	\caption{Apriltag Inception - To mitigate the FOV problem}
+	\label{fig:apriltag}
+\end{figure}
+
+On the landing target from we have successfully calibrated the logitech webcam 
+and used the Apriltag library to obtain a pose estimate, and have manually 
+verified the estimates are accurate, for distance the error is $\pm 1$cm. We 
+have also successfully implemented the ability to identify two different 
+apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from 
+both apriltags are equal.
+
+Next is to workout how to transform the measurements from the pose estimates of 
+the apriltags in relation to the quadrotor's body frame.
+
+\section*{Schedule}
+
+\begin{itemize}
+	\vspace{-0.2cm}
+	\setlength{\itemsep}{5pt}
+	\setlength{\parskip}{0pt}
+	\setlength{\parsep}{0pt}
+
+	\item{\textbf{6th March}: Implement and show in simulation that we can land 
+	a quadrotor successfully on to a moving platform}
+	\item{\textbf{13th March}: Perform Autonomous Flying Outdoors and Implement 
+	Control code for the Huskey}
+	\item{\textbf{21st March}: Perform Autonomous Flying Indoors}
+	\item{\textbf{28th March}: Attempt to Autonomous Land the Quadrotor Indoors}
+\end{itemize}
 

### 2016-02-27 docs/proposal/proposal.tex
Add interim report

@@
-\documentclass{article}
+\documentclass{article}[12pt]
 
@@
 \usepackage{titlesec}
-\usepackage[margin=1.5in]{geometry}
+\usepackage[margin=1.2in]{geometry}
 \setlength{\parskip}{\baselineskip}%
@@
 \titlespacing*{\section}{0pt}{2ex}{0ex}
-\titlespacing*{\subsection}{0pt}{2ex}{-2ex}
+\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
 \titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}
+
+%COMMENTING
+\usepackage{comment}
 
@@
 \author{Stan Brown \& Chris Choi}
+\date{}
 \maketitle
 
-\section*{Introduction}
+\section*{Project Outline}
 Landing a quadrotor on a moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem.
@@
 It is our goal to replicate one of the successful solutions with the aim of extending the solution to land outdoors.
+Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform.
 
-\subsection*{Applications}
-Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform, landing in high wind conditions.
-
-\section*{Related Work} 
 The problem of autonomous landing on a moving platform seems to be divided into three separate parts in literature.
@@
 
-In the majority of the literature reviewed, rendezvous planning was neglected and it was assumed that quadrotor has a clear view of its landing location.
+\subsubsection*{Planning}
+In the majority of the literature reviewed, rendezvous planning was neglected and it was assumed that quadrotor has a clear view of its landing target.
+Most authors tend to focus on the detection and estimation of the quadrotor's pose relative to the target and maintaining an accurate estimation throughout the landing procedure which is mostly handled by a series of control loops.
 
-From the literature we reviewed planning is the least concern, perception and control seems to be the main factor to sucess.
-For perception existing solutions could be as simple as using basic color detection techniques to identify the landing target\cite{Kim2014}, to sophisticated techniques such as \cite{Herisse2012} where they used the optical flow in images captured onboard the quadrotor to obtain necessary relative information for control.
+\subsubsection*{Perception and State Estimation}
+For perception existing solutions use a variety of simple to complex techniques.
+In  \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.
+
+\subsubsection*{Control}
+A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}.
+However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
+In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement.
+While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing.
+Additionally the experiments did not seem to account for pitch or roll of the platform.
 
@@
 
+In reviewing the prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing pad throughout the entire manoeuvre.
+As the quadrotor approaches the landing pad, visible targets used to guide the quadrotor becomes difficult to locate, causing camera based navigation techniques to fail.
+Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.
+
+To address both of these issues, we propose a novel solution utilizing two cameras and two gimbals.
+In the proposed set up the quadrotor will have a gimballed camera and so will the moving landing platform.
+Both of the cameras will have an AprilTag attached allow cameras to track each other and provide two estimations of the quadrotor's current pose relative to the landing platform.
+
+We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform.
+We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.
+
+\section*{Hardware and Software Status}
+
+For this project we will be using a DJI F450 Flamewheel quadrotor using the Pixhawk flight controller \cite{pixhawk} running the PX4 firmware \cite{px4}.
+The gimbal design and camera specifications have yet to be decided, for the prototyping and testing phase we will be using fixed USB cameras.
+For the AprilTag detection and pose estimation we will use the AprilTag Library implemented by \cite{apriltags}.
+OpenCV will be used for image analysis tasks and the controllers will be implemented using ROS.
+
+\section*{Milestones and Goals for the Semester}
+Over the term we have set a series of goals and deadlines in order to evaluate progress throughout the term.
+Later on additional goals will be added as the requirements change depending on test results.
+\begin{enumerate}
+	\item{Evaluate AprilTag detection algorithms and libraries - Jan 15}
+	\item{Set the simulation environment in Gazebo - Jan 15} 
+	\item{Perform automated landing in simulation - Feb 1}
+	\item{Acquire gimbals and cameras and test the tracking code - Feb 7}
+	\item{Attempt landing indoors and duplicate the work of \cite{Ling2014} - Feb 19}
+	\item{Add the gimbals to the quadrotor and landing pad  - Feb 27}
+	\item{Implement the proposed methods outlined above - April 15}
+	\item{Attempt to land in outdoor conditions 	- April 20}
+
+\end{enumerate}
+
+\begin{comment}
+CHRIS IS A LITTLE BITCH
 \begin{itemize}
@@
 \end{itemize}
+\end{comment}
 
-\section*{Milestones}
-\begin{enumerate}
-	\item{Perform tracking and follow in simulation}
-	\item{Perform automated landing in simulation}
-	\item{Perform the above successfully in real life}
-\end{enumerate}
-
-\section*{Possible Expansion}
-
-Trajectory Planning for high wind or fast moving platform.
+\newpage
 
 \bibliography{proposal}{}
-\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
 

### 2016-02-27 src/camera.cpp

@@ -223,14 +223,17 @@ int Camera::processImage(cv::Mat &image, cv::Mat &image_gray)
 {
     // detect april tags (requires a gray scale image)
     cv::cvtColor(image, image_gray, CV_BGR2GRAY);
-    cv::imshow("camera", image_gray);
     this->apriltags = this->tag_detector->extractTags(image_gray);
 
     // print out each apriltags
-    std::cout << "TAGS:" << this->apriltags.size() << std::endl;
+    // std::cout << "TAGS:" << this->apriltags.size() << std::endl;
     for (int i = 0; i < this->apriltags.size(); i++) {
         this->printDetection(this->apriltags[i]);
+        // this->apriltags[i].draw(image);
     }
+
+    // cv::imshow("camera", image);
+    // cv::imshow("gray scale", image_gray);
 
     return this->apriltags.size();
 }

### 2016-02-28 docs/report/report.tex
Add draft report

\documentclass[11pt, twocolumn]{article}

% GRAPHICS
\usepackage{float}
\usepackage{graphicx}
\usepackage{subcaption}

% HYPERLINKS
\usepackage{hyperref}

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=0.8in]{geometry}
%\setlength{\parskip}{\baselineskip}%
%\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{2ex}{0ex}
\titlespacing*{\subsection}{0pt}{2ex}{0ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{0ex}

%COMMENTING
\usepackage{comment}

\begin{document}

% TITLE
\title{Autonomous Quadrotor Landing on a Moving Platform}
\author{Stan Brown \& Chris Choi}
\date{}
\maketitle

\section{Introduction}
Autonomous 	precision landing of a quadrotor onto moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem. Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform and more.

The major challenge with autnomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts include lighting, and color.

\section{Related Work}
The challenging of autonoums landing can be categorized into three distinct parts. First, it must sense or detect the landing target to obtain positional estimates relative to the quadrotor. Secondly, the quadrotor must plan its rendezvous trajectory with the landing target. Third and finally, the quadrotor must apply a set of controller commands to approach the platform, matching both speed and heading on the approach and land on the moving target. We discuss the three different parts in the following subsections.

\subsection{Perception and State Estimation}
For perception existing solutions use a variety of simple to complex techniques. In  \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.

\subsection{Planning}
In the literature we reviewed, rendezvous planning was neglected as it was assumed that quadrotor has a clear view of its landing target. Most authors tend to focus on the detection and estimation of the quadrotor's pose relative to the target and maintaining an accurate estimation throughout the landing procedure which is mostly handled by a series of control loops.

\subsection{Control}
A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}. However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC. In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement. While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing. Additionally the experiments did not seem to account for pitch or roll of the platform.

\section{Proposed Methodology}
In reviewing prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing target throughout the entire manoeuvre. As the quadrotor approaches the landing target, the target often goes beyond the camera's field of view, causing camera based navigation techniques to fail. Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.

To address both of these issues, we propose a novel solution utilizing an nested apriltags which we term inception apriltag. We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform. We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.

\section{Project Progress}
\subsection{Hardware Setup}
\subsubsection{Quadrotor}
For the hardware, we have chosen to reuse equipment that is readily available to us in the Wave Lab. For the quadrotor we have been using the DJI F450 quadrotor frame, Emax 2213-935KV motors with complimentary 1045R propellers, Thunder Power lipo 11.1V 4200mah battery, DJI E310 420S 20A electronic speed controller and Pixhawk v2.4 as our flight controller.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
	\caption{DJI F450 with Pixhawk v1.5}
\end{figure}

\subsubsection{Onboard Autonomous Control System}
In terms of onboard autonoumos control, we have decided to use the Odriod XU4 due to its size and processing power available, and a Logitech C270 HD webcam as our vision sensor. One problem we may face very soon is the narrow field of view and relatively low frame rate (25Hz) the logitech webcam has. We will be keeping our options open, and plan on replacing the logitech webcam with a Ximia xiQ USB3 camera with a wide angle lens in the near future.

\subsection{Software Setup}
\subsubsection{Pixhawk Firmware - PX4}
As mentioned in the hardware section, we have had numerous issues with regards to using the software suite for the Pixhawk Flight Controller, as well as the PX4 firmware itself. There are many instances where we could not explain the instability of the quadrotor during flight, many of which lead to costly crashes, but we believe through these experiences we have developed a procedure to lower the risk for such instances from happening often.

\subsubsection{Odriod to Pixhawk Communication}
For our autonomous system to control the quadrotor directly, the Odriod has to be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS package) comes into play. Mavlink is a popular UAV communication protocol between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS node to enable developers to monitor and issue mavlink commands with ease. We have successfully used mavros to arm and disarm Pixhawk (tested), in the near future we should be able to send velocity/attitude commands to control the quadrotor.

\subsubsection{Simulator}
Initially we have explored the possibility of using the combination of PX4's Software in the Loop Simulation (SITL) and Gazebo 6 as our simulation environment for our project, however we found the combination of install instructions changing at a fast pace, and the documentation not up to date to be a major concern for us. We have therefore decided to fallback on developing the estimation and control loop in Matlab.

\subsubsection{AprilTag}
\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/apriltags_1.png}
		\caption{2 Apriltags Detected}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/apriltags_3.png}
		\caption{1 Apriltag Detected }
	\end{subfigure}
	\caption{Apriltag Inception - To mitigate the FOV problem}
	\label{fig:apriltag}
\end{figure}

On the landing target from we have successfully calibrated the logitech webcam and used the Apriltag library to obtain a pose estimate, and have manually verified the estimates are accurate, for distance the error is $\pm 1$cm. We have also successfully implemented the ability to identify two different apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from both apriltags are equal.

Next is to workout how to transform the measurements from the pose estimates of the apriltags in relation to the quadrotor's body frame.

\bibliography{report}{}
\bibliographystyle{ieeetr}

\end{document}

### 2016-03-03 src/camera.cpp
Add ability to record apriltag pose estimates

@@ -103,42 +103,6 @@ void Camera::printFPS(double &last_tic, int &frame)
     }
 }
 
-int Camera::run(void)
-{
-    int frame_index;
-    double last_tic;
-    cv::Mat image;
-    cv::Mat image_gray;
-    cv::VideoCapture capture(this->camera_index);
-
-    // setup
-    frame_index = 0;
-    last_tic = tic();
-
-    // open capture device
-    if (capture.isOpened() == 0) {
-        std::cout << "Failed to open webcam!";
-        return -1;
-    } else {
-        capture.set(CV_CAP_PROP_FRAME_WIDTH, this->image_width);
-        capture.set(CV_CAP_PROP_FRAME_HEIGHT, this->image_height);
-    }
-
-    // read capture device
-    while (true) {
-        capture.read(image);
-
-        this->processImage(image, image_gray);
-        this->printFPS(last_tic, frame_index);
-
-        if (cv::waitKey(30) >= 0) {
-            break;
-        }
-    }
-
-    return 0;
-}
-
 double Camera::standardRad(double t)
 {
     // normalize angle to be within the interval [-pi,pi].
@@ -165,16 +129,13 @@ void Camera::convertToEuler(
     roll  = this->standardRad(atan2(wRo(0,2)*s - wRo(1,2)*c, -wRo(0,1)*s + wRo(1,1)*c));
 }
 
-void Camera::printDetection(AprilTags::TagDetection& detection)
+PoseEstimate Camera::obtainPoseEstimate(AprilTags::TagDetection& detection)
 {
-    double yaw;
-    double pitch;
-    double roll;
+    PoseEstimate pose;
     double m_tag_size;
 
-    Eigen::Vector3d translation;
-    Eigen::Matrix3d rotation;
     Eigen::Matrix3d F;
+    Eigen::Matrix3d rotation;
     Eigen::Matrix3d fixed_rot;
 
     // setup
@@ -182,6 +143,7 @@ void Camera::printDetection(AprilTags::TagDetection& detection)
          0, -1, 0,
          0, 0, 1;
 
+    // change tag size according to tag id
     if (detection.id == 0) {
         m_tag_size = 0.048;
     } else {
@@ -195,22 +157,30 @@ void Camera::printDetection(AprilTags::TagDetection& detection)
         this->camera_matrix.at<double>(1, 1),
         this->camera_matrix.at<double>(0, 2),
         this->camera_matrix.at<double>(1, 2),
-        translation,
[…]

### 2016-03-03 docs/interim_report/interim_report.tex

--- 2016-02-24 docs/interim_report/interim_report.tex
@@
 \usepackage{titlesec}
-\usepackage[margin=1.2in]{geometry}
+\usepackage[margin=1.0in]{geometry}
 \setlength{\parskip}{\baselineskip}%
@@
 \usepackage{comment}
-
 \begin{document}
@@
 % TITLE
+\vspace{-5cm}
 \title{Autonomous Quadrotor Landing on a Moving Platform}
@@
 \section*{Introduction}
-Our goal is to autonomously land a quadrotor onto a moving platform. In this 
-interim-report we will discuss our efforts so far, and any preliminary results 
-we may have. So far we have spent a considerable amount of effort getting 
-different components of the project working. In this report we will be 
-discussing progress in both hardware and software aspects of the project, 
-specifically:
+The goal of this project is to develop a set of controllers and methods that allow a quadcopter equipped with a downward facing camera and sonar to perform fully autonomous landing on a moving platform without relying on high accuracy GPS measurements.
+In this interim report we provide an update on the progress made so far on the software and hardware aspects, as well as changes made to the project scope.
+Additionally we provide an updated project schedule for the remainder of the term.
+
+\section*{Project Progress}
+\subsection*{Hardware Status}
+\subsubsection*{Flight Controller and Quadroter}
+For the flight controller, which handles the low level control loops and keeps the quadrotor steady, we have selected a Pixhawk v2.4 running the PX4 firmware stack, and for the quadrotor frame we have selected a DJI 450 Flamewheel.
+The powertrain of the quadrootr consistes of a set of Emax 2213-935KV motors with complimentary 1045R propellers, a Thunder Power lipo 11.1V 4200mah battery, and a set of DJI E310 420S 20A electronic speed
+controllers. At current our quadrotor flies \textit{reasonably well} with some \textit{minor} setbacks, mainly due to the instability of the firmware, and lack of documentation for the firmware 
+and software packages. The project setbacks thus far have almost all been entirely related to PX4 firmware stack. Figure \ref{hardware} shows the state of the quadrotor at the time of this report.
+
+\begin{figure}[]
+	\centering
+	\includegraphics[width=0.6\linewidth]{images/quadrotor.jpg}
+	\caption{DJI F450 with Pixhawk v1.5}
+	\label{hardware}
+\end{figure}
+
+\subsubsection*{Onboard Autonomous Control System and Vision Processing}
+For high level control and vision processing we have selected an Odroid XU4 microcomputer because of its small size, low weight, low power consumption relative to its processing power.
+The Odroid will be mounted on the quadrotor frame and will be powered directly from the quad rotor battery pack.
+
+Visual data will, for now,  be captured using a Logitech C270 HD webcam whcih runs at a frame rate of 25Hz.
+We plan to use this web cam for the initial testing stages and once we are confident in the high level control systems such that the chance of an accident occurring as the result of a software glitch is considered low we will upgraded to a Ximia xiQ USB3 camera.
+Compared to the Logitech web cameara, the Ximia camera has a number of additional features, such as a higher frame rate (60Hz), interchangeable lenses and a set ROS drivers that can access the `al camera settings.
+
+\subsection*{Software}
+\subsubsection*{Pixhawk Firmware}
+As mentioned in the hardware section, we have had numerous issues using the software suite for the Pixhawk Flight Controller, as well as the PX4 firmware itself.
+There are many instances where we could not explain the instability of the quadrotor during flight, many of which lead to
+costly crashes, but we believe through these experiences we have developed a 
+procedure to lower the risk for such instances from happening often.
+
+\subsubsection*{Odriod to Pixhawk Communication}
+For our autonomous system to control the quadrotor directly, the Odriod has to 
+be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS 
+package) comes into play. Mavlink is a popular UAV communication protocol 
+between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS 
+node to enable developers to monitor and issue mavlink commands with ease. We 
+have successfully used mavros to arm and disarm Pixhawk (tested), in the near 
+future we should be able to send velocity/attitude commands to control the 
+quadrotor.
+
+\subsubsection*{Simulator}
+Initially we explored the possibility of using the combination of PX4's 
+Software in the Loop Simulation (SITL) and Gazebo 6 as our simulation 
+environment for our project, however we found the combination of poor installation instructions that were inconsistently updated along with poor, often outdated, documentation major concern for us.
+After spending more than 15 hours in attempting to install and run the simulator we have decided to abandon the SITL simulation and create a simple simulation in Matlab to test our estimation and control loops.
+We therefore implicitly assume that the Pixhawk will execute any velocity/attitude commands accurately and without any delays.
+
+\subsubsection*{AprilTag Software}
+Using a set of April tags and camera calibration functions provided in the OpenCV library, we been able to successfully obtained accurate pose estimations between the Logitech webcam and a single AprilTag.
+The translational error in the pose estimation appears to be below $\pm 1$cm while the rotational error has not yet been measured.
+We plan to use the Optitrack Motion capture system system currently installed in the lab to take a large set of measurements in order to provide an accurate estimation of the errors associated with using the AprilTag Software.
+
+The current rate AprilTag software operates at 20fps on the Odroid and we will investigate a modified version of the AprilTag library made by Kevin Ling, a former Wave Lab member who optimitize the AprilTag source code in a previous project.
+We have also successfully measured the pose from two April tags simultaneously by placing a small AprilTag inside a larger one such that when the larger AprilTag goes out of the cameras FOV measurements pose estimates will be provided by the smaller one.
+This has the advantage of continuously providing pose estimation with the quadrotor is less than a meter above the target which is point at which a 40cm by 40cm april tag goes out of the camera view.
+An example of the two AprilTags providing simultaneous measurements is shown in Figure \ref{fig:apriltag}.
+
+\begin{figure}[]
+	\centering
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_1.png}
+		\caption{2 Apriltags Detected}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_3.png}
+		\caption{1 Apriltag Detected }
+	\end{subfigure}
+	\caption{Apriltag Inception - By using secondary AprilTag inside a larger one the FOV problem associated with AprilTags when the camera is either to far away or two close is avoided.}
+	\label{fig:apriltag}
+\end{figure}
+
+\section*{Alterations to Project Scope}
+Due to unforeseen difficulties in getting the software and hardware to interface with each other along with difficulties in getting an accurate simulation operational we will no longer be using a gimballed camera for this stage of the project.
+We had initially hoped to use attach gimbal to the downward facing camera on the quadcopter to make tracking the target easier in cases where the quadrotor is required to make rapid corrections.
+
+The removal of the gimbal only pertains to the portion of the project that will be completed by the end of this academic term (April 2016) and we plan to revisit once we have a base solution that works in situations where there is low wind and the platform is moving relatively slowly.
+A new updated project schedule is summarized in the next section.
+
+\section*{Schedule}
 
 \begin{itemize}
-	\vspace{-0.4cm}
-	\setlength{\itemsep}{0pt}
+	\vspace{-0.2cm}
+	\setlength{\itemsep}{5pt}
 	\setlength{\parskip}{0pt}
@@
 
-	\item{Quadrotor Setup and Onboard Computer}
-	\item{Camera}
+	\item{\textbf{6th March}: Implement and show in simulation that we can land 
+	a quadrotor successfully on to a moving platform}
+	\item{\textbf{21st March}: Perform autonomous flying indoors}
+	\item{\textbf{13th March}: Perform autonomous flying outdoors}
+	\item{\textbf{28th March}: Attempt to autonomous land the quadrotor Indoors}
 \end{itemize}
-
-\section*{Hardware}
-For the hardware, we have chosen to reuse equipment that is readily available 
-to us in the Wave Lab. For the quadrotor we are using
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.6\textwidth]{images/quadrotor.jpg}
-	\caption{DJI F450 with Pixhawk v1.5}
-\end{figure}
-
-\section*{Software}
-\subsection*{Pixhawk Firmware}
-
-\subsection*{Simulator}
-
-\subsection*{AprilTag}
 

### 2016-03-07 src/quadrotor.cpp
Update

@@ -106,7 +106,7 @@ int main(int argc, char **argv)
     quad.disarm();
 
     // loop
-    ros::spin();
+    // ros::spin();
 
     return 0;
 }

### 2016-03-07 docs/interim_report/interim_report.tex

@@
 Using a set of April tags and camera calibration functions provided in the OpenCV library, we been able to successfully obtained accurate pose estimations between the Logitech webcam and a single AprilTag.
-The translational error in the pose estimation appears to be below $\pm 1$cm while the rotational error has not yet been measured.
+The translational error in the pose estimation appears to be below $\pm 1$ cm while the rotational error has not yet been measured.
 We plan to use the Optitrack Motion capture system system currently installed in the lab to take a large set of measurements in order to provide an accurate estimation of the errors associated with using the AprilTag Software.
 
-The current rate AprilTag software operates at 20fps on the Odroid and we will investigate a modified version of the AprilTag library made by Kevin Ling, a former Wave Lab member who optimitize the AprilTag source code in a previous project.
+The current rate AprilTag software operates at 20 fps on the Odroid and we will investigate a modified version of the AprilTag library made by Kevin Ling, a former Wave Lab member who optimitize the AprilTag source code in a previous project.
 We have also successfully measured the pose from two April tags simultaneously by placing a small AprilTag inside a larger one such that when the larger AprilTag goes out of the cameras FOV measurements pose estimates will be provided by the smaller one.

### 2016-03-31 src/ros/camera_node.cpp
saving before changing a bunch of stuff

@@ -60,10 +60,15 @@ void fix_coordinate_frames(
     // translate from camera frame to ENU
     // x is times by -1 because april tag was in left-hand
     // co-ordinate frame commonly used by cameras
-    pos[0] = -1 * pose.translation[0];
-    pos[1] = pose.translation[1];
-    pos[2] = pose.translation[2];
-    mat3_dot_vec3(rot_mat, vec_pos, pos);
+    pos[0] = pose.translation[1];
+    pos[1] = -1 * pose.translation[2];
+    pos[2] = pose.translation[0];
+    // mat3_dot_vec3(rot_mat, pos, vec_pos);
+    // pos[0] = vec_pos[0];
+    // pos[1] = vec_pos[1];
+    // pos[2] = vec_pos[2];
+    // ROS_INFO("POSE X HERE IS %f", pose.translation[0]);
+    // ROS_INFO("returned POSE X HERE IS %f", pos[0]);
 
     // convert euler angles to quaternions
     quat = euler2quat(pose.pitch, pose.roll, pose.yaw);
@@ -103,7 +108,7 @@ static void build_pose_stamped_cov_msg(
     int seq,
     TagPose &pose,
 	double *rot_mat,
-    geometry_msgs::PoseWithCovarianceStamped pose_msg
+    geometry_msgs::PoseWithCovarianceStamped &pose_msg
 )
 {
 	double pos[3];
@@ -123,15 +128,18 @@ static void build_pose_stamped_cov_msg(
     pose_msg.pose.pose.position.z = pos[2];
 
     // pose orientation
-    pose_msg.pose.pose.orientation.x = 0;
-    pose_msg.pose.pose.orientation.y = 0;
-    pose_msg.pose.pose.orientation.z = 0;
-    pose_msg.pose.pose.orientation.w = 0;
+    pose_msg.pose.pose.orientation.x = quat.x();
+    pose_msg.pose.pose.orientation.y = quat.y();
+    pose_msg.pose.pose.orientation.z = quat.z();
+    pose_msg.pose.pose.orientation.w = quat.w();
 
     // pose covariance
-    pose_msg.pose.covariance[0] = 1;
-    pose_msg.pose.covariance[7] = 1;
-    pose_msg.pose.covariance[14] = 1;
+    pose_msg.pose.covariance[0] = 0.01;
+    pose_msg.pose.covariance[7] = 0.01;
+    pose_msg.pose.covariance[14] =0.01;
[…]

### 2016-03-31 src/ros/quadrotor_node.cpp

@@ -206,7 +206,7 @@ int main(int argc, char **argv)
         pose.header.stamp = ros::Time::now();
         pose.header.seq = count;
         pose.header.frame_id = 1;
-        ROS_INFO("x: 0.0\ty: 0.0\tz: 1.0");
+        // ROS_INFO("x: 0.0\ty: 0.0\tz: 1.0");
 		pose.pose.position.z = 1.0;
         pose.pose.position.x = 0.0;
         pose.pose.position.y = 0.0;

### 2016-03-31 assignments/assignment_2/report.tex

\documentclass{article}

% MATHS
\usepackage{amsmath}
\usepackage{gensymb}

\usepackage{mathtools}
\newcommand\coolover[2]{\mathrlap{\smash{\overbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}^{\mbox{$#1$}}}}#2} 
\newcommand\coolunder[2]{\mathrlap{\smash{\underbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}_{\mbox{$#1$}}}}#2}

\newcommand\coolleftbrace[2]{%
#1\left\{\vphantom{\begin{matrix} #2 \end{matrix}}\right.}

\newcommand\coolrightbrace[2]{%
\left.\vphantom{\begin{matrix} #1 \end{matrix}}\right\}#2}

% GRAPHICS
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{tikzscale}
\usetikzlibrary{calc}
\usepackage{graphicx}

% HYPERLINKS
\usepackage{hyperref}

% DOCUMENT PADDING AND MARGINS
\usepackage{titlesec}
\usepackage[margin=1.2in]{geometry}
\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}
\titlespacing*{\section}{0pt}{5ex}{2ex}
\titlespacing*{\subsection}{0pt}{1ex}{-2ex}
\titlespacing*{\subsubsection}{0pt}{2ex}{-2ex}

%COMMENTING
\usepackage{comment}

\begin{document}

% TITLE
\title{ME780 Assignment 2}
\author{Stan Brown \& Chris Choi}
\date{}
\maketitle

\section{Motion Model of a Bicycle}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{images/bicycle_model.png}
	\caption{Bicycle in World Frame}
	\label{fig:bicycle}
\end{figure}

Motion of front wheel:

\begin{align}
	x_{f} &= x + L \cos(\theta) \\
	y_{f} &= y + L \sin(\theta) \\
 	\begin{bmatrix}
        x_{f, t} \\
        y_{f, t} \\
    \end{bmatrix}  
    &=
    \begin{bmatrix}
	    x_{f, t - 1} + v_{f, t} \cos(\theta_{f, t - 1} + \delta_{t}) dt \\
		y_{f, t - 1} + v_{f, t} \sin(\theta_{f, t - 1} + \delta_{t}) dt \\
    \end{bmatrix}
\end{align}

Motion of rear wheel:

\begin{align}
 	\begin{bmatrix}
        x_{r, t} \\
        y_{r, t} \\
    \end{bmatrix}  
    &=
    \begin{bmatrix}
	    x_{r, t - 1} + v_{r, t} \cos(\theta_{r, t - 1}) dt \\
		y_{r, t - 1} + v_{r, t} \sin(\theta_{r, t - 1}) dt \\
    \end{bmatrix}
\end{align}

At current we have a motion model for both the front and the rear wheel of the bicycle, however we can simplify it using the Instantaneous Center of Rotation to combine both the front and rear wheel together.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{images/bicycle_icr.png}
	\caption{Simplifying the Bicycle Model with ICR}
	\label{fig:bicycle_icr}
\end{figure}

From Fig~\ref{fig:bicycle_icr} we can derive the relationship between the steering angle $\delta$ relative to the bicycle's heading:

\begin{equation}
	\label{eq:icr_steering_angle}
	\tan(\delta) = \dfrac{L}{R}
\end{equation}

Further, we know that the angular velocity $\omega$ from the point ICR of both the front and rear wheel is:

\begin{equation}
	\label{eq:icr_angluar_velocity}
	\omega = \dfrac{v \tan(\delta)}{L} = \dfrac{v}{R}
\end{equation}

Now that we have the angular velocity of the bicycle over time, the bicycle's change in heading over time is simply:

\begin{equation}
	\theta_{t} = \theta_{t - 1} + \dfrac{v_{t} \tan(\delta_{t})}{L} dt
\end{equation}

For the complete motion model of the bicycle we have:

\begin{align}
 	\begin{bmatrix}
        x_{t} \\
        y_{t} \\
        \theta_{t}
    \end{bmatrix}  
    &=
    \begin{bmatrix}
	    x_{t - 1} + v_{t} \cos(\theta_{t - 1}) dt \\
		y_{t - 1} + v_{t} \sin(\theta_{t - 1}) dt \\
		\theta_{t - 1} + \dfrac{v_{t} \tan(\delta_{t})}{L} dt
    \end{bmatrix}
\end{align}

Implementing the bicycle motion model in Matlab and simulating the motion for 20 seconds with the following parameters, we obtain a motion that resembles Fig~\ref{fig:bicycle_20s}.

\begin{itemize}	
	\vspace{-0.4cm}
	\setlength{\itemsep}{0pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}

	\item{Simulation time step $dt$: 0.1s}
	\item{Velocity $v$: $3 \text{ms}^{-1}$}
	\item{Length of bicycle $L$: 0.3m}
	\item{Steering angle $\delta$: $10 - t$ degrees}
	\item{Steering angle limit: $\pm 30$ degrees}
	\item{Standard deviation on $x$ and $y$: 0.02m}
	\item{Standard deviation on $\theta$: 1 degree}
\end{itemize}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{images/bicycle_motion_20s.jpg}
	\caption{Simulating the Bicycle Model for 20s starting from (0, 0)}
	\label{fig:bicycle_20s}
\end{figure}

Just looking at Fig~\ref{fig:bicycle_20s} we can roughly validate the motion as valid, since the angle starts from +10 and ends at -10 degrees over time (20 seconds).

\newpage
\section{Carrot Controller for Bicycle}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\textwidth]{images/carrot_controller.png}
	\caption{Carrot Controller}
	\label{fig:carrot_controller}
\end{figure}

A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line ahead of the closest point on the line to the current robot position.

\newpage
\section{Planner}

\end{document}

### 2016-03-31 src/ros/camera_node.cpp
some fixes, need to check matrix mult

@@ -41,12 +41,29 @@ void rotation_matrix(double phi, double theta, double psi, double *rot_mat)
     rot_mat[8] = cos(theta) * cos(psi);
 }
 
+void single_rotation_matrix(double psi, double *rot_mat)
+{
+    //  rotation matrix
+    rot_mat[0] = cos(psi);
+    rot_mat[1] = -sin(psi);
+    rot_mat[2] = 0;
+
+    rot_mat[3] = sin(psi);
+    rot_mat[4] = cos(psi);
+    rot_mat[5] = 0;
+
+    rot_mat[6] = 0;
+    rot_mat[7] = 0;
+    rot_mat[8] = 1;
+}
+
 void mat3_dot_vec3(double *m, double *v, double *out)
 {
     out[0] = m[0] * v[0] + m[3] * v[1] + m[6] * v[2];
     out[1] = m[1] * v[0] + m[4] * v[1] + m[7] * v[2];
     out[2] = m[2] * v[0] + m[5] * v[1] + m[8] * v[2];
 }
+
 
 void fix_coordinate_frames(
     TagPose &pose,
@@ -55,6 +72,8 @@ void fix_coordinate_frames(
     tf::Quaternion &quat
 )
 {
+    double rot_out[9];
+    single_rotation_matrix(pose.yaw, rot_out);
 	double vec_pos[3];
 
     // translate from camera frame to ENU
@@ -63,10 +82,10 @@ void fix_coordinate_frames(
     pos[0] = pose.translation[1];
     pos[1] = -1 * pose.translation[2];
     pos[2] = pose.translation[0];
-    // mat3_dot_vec3(rot_mat, pos, vec_pos);
-    // pos[0] = vec_pos[0];
-    // pos[1] = vec_pos[1];
-    // pos[2] = vec_pos[2];
+    mat3_dot_vec3(rot_out, pos, vec_pos);
+    pos[0] = vec_pos[0];
+    pos[1] = vec_pos[1];
+    pos[2] = vec_pos[2];
     // ROS_INFO("POSE X HERE IS %f", pose.translation[0]);
     // ROS_INFO("returned POSE X HERE IS %f", pos[0]);
 

### 2016-03-31 assignments/assignment_2/report.tex
Add working prm for assignment

@@
 
-A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line ahead of the closest point on the line to the current robot position.
+A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line, ahead of the closest point on the trajectory line to the current robot position.
+
+\subsection{Closest Point on the Trajectory Line to the Robot}
+The closest point between the robot's position and the trajectory line can be calculated, .
+Let $A$ and $B$ be the start and end of a trajectory line, the first step is to find the gradient $m_{1}$ of trajectory line $AB$.
+
+\begin{align}
+
+\end{align}
+
+The closest point $Q$ on the trajectory line $AB$ relative to the robot at point $P$ is then:
+
+m_{2} = -1 / m_{1};
+x = (m_{1} * x_{1} - m_{2} * a + b - y_{1}) / (m_{1} - m_{2});
+y = m_{2} * (x - a) + b;
 

### 2016-03-31 assignments/assignment_2/src/IGVCmap.m

@@ -4,135 +4,320 @@ source('planning.m');
 I = imread('IGVCmap.jpg');
 map = im2bw(I, 0.7);  % Convert to 0 - 1 image
 map = 1 - flipud(map)'; % Convert to 0 free, 1 occupied and flip.
+% map = zeros(100, 100);
 [M, N] = size(map);  % Map size
+map_min = [1 1];
+map_max = [M N];
 
 % robot start position
-% dxy = 0.1;
 dxy = 0.1;
 pos_start = [40 5 pi];
-
-% target location
 pos_end = [50 10];
 
-% set up the map
-xMax = [M N]; % State bounds
-xMin = [1 1];
-xR = xMax - xMin;
+
+function path = backtrack_path(closed_set, nodes, start, finish)
+    done = 0;
+    cur = finish;
+    curC = find(closed_set(:,1) == finish);
+    prev =  closed_set(curC,2);
+    i = 2;
+
+    path = [];
+    while (!done)
+        if (prev == start)
+            done = 1;
+        end
+
+        if (cur ~= start && cur ~= finish)
+            path = [path; nodes(cur, :)];
+        end
+
+        figure(1);
+        hold on;
+        plot([nodes(prev,1) nodes(cur,1)], [nodes(prev,2) nodes(cur,2)], 'g', 'LineWidth', 2)
+        cur = prev;
+        curC = find(closed_set(:, 1) == cur);
+        prev = closed_set(curC, 2);
+    end
+    Cend = find(closed_set(:,1) == finish);
+    plen = closed_set(Cend,4);
+
+    % return shortest path
+    node_start = nodes(start, :);
+    node_finish = nodes(finish, :);
+    path = [node_start; path; node_finish];
+end
+
+function [spath,sdist] = shortestpath(nodes, edges, start, finish)
+%SHORTESTPATH Find shortest path using A-star search
+% Inputs:
+%   nodes: list of n node locations in 2D
+%   edges: nXn connectivity of nodes (1 = connected), symmetric only uses
+%           upper triangle
+%   start: index of start node
+%   finish: index of finish node
+
+    % Find edge lengths
+    n = length(nodes);
+    dists= zeros(n,n);
+    for i = 1:n
+        for j = i:n
+            if (edges(i,j))
+                dx = nodes(i, 1) - nodes(j, 1);
+                dy = nodes(i, 2) - nodes(j, 2);
+                dists(i,j) = sqrt(dx^2 + dy^2);
[…]

### 2016-03-31 assignments/assignment_2/src/ME597-8-PRM/prm.m

@@ -49,55 +49,55 @@ drawnow();
 disp('Time to create environment');
 % toc;
 
-% %% Multi-query PRM, created in batch
-% tic;
-%
-% % Get milestones
-% nS = 500;
-% samples = [xR(1)*rand(nS,1)+xMin(1) xR(2)*rand(nS,1)+xMin(2)];
-% keep = inpolygon(samples(:,1),samples(:,2), env(:,1),env(:,2));
-% milestones = [x0; xF; samples(find(keep==1),:)];
-% figure(1); hold on;
-% plot(samples(:,1),samples(:,2),'k.');
-% plot(milestones(:,1),milestones(:,2),'m.');
-% nM = length(milestones(:,1));
-% disp('Time to generate milestones');
-% nM
-% toc;
+%% Multi-query PRM, created in batch
+tic;
 
-% % Attempt to add closest p edges
-% tic;
-% p = 20;
-% e = zeros(nM,nM);
-% D = zeros*ones(nM,nM);
-% for i = 1:nM
-%     % Find closest neighbours
-%     for j = 1:nM
-%         d(j) = norm(milestones(i,:)-milestones(j,:));
-%     end
-%     [d2,ind] = sort(d);
-%     % Check for edge collisions (no need to check if entire edge is
-%     % contained in obstacles as both endpoints are in free space)
-%     for j=1:p
-%         cur = ind(j);
-%         if (i<cur)
-%             if (~CheckCollision(milestones(i,:),milestones(cur,:), obsEdges))
-%                 e(i,cur) = 1;
-%                 e(cur,i) = 1;
-%                 plot([milestones(i,1) milestones(cur,1)],[milestones(i,2) milestones(cur,2)],'m');
-%             end
-%         end
-%     end
-% end
-% disp('Time to connect roadmap');
-% toc;
+% Get milestones
+nS = 500;
+samples = [xR(1)*rand(nS,1)+xMin(1) xR(2)*rand(nS,1)+xMin(2)];
+keep = inpolygon(samples(:,1),samples(:,2), env(:,1),env(:,2));
+milestones = [x0; xF; samples(find(keep==1),:)];
+figure(1); hold on;
+plot(samples(:,1),samples(:,2),'k.');
+plot(milestones(:,1),milestones(:,2),'m.');
+nM = length(milestones(:,1));
+disp('Time to generate milestones');
+nM
+toc;
+
+% Attempt to add closest p edges
+tic;
+p = 20;
+e = zeros(nM,nM);
[…]

### 2016-03-31 assignments/assignment_2/src/ME597-8-PRM/prmII.m

@@ -16,7 +16,7 @@ xF = [6 1];
 
 % Set up the obstacles
 rand('state', 1);
-nO = 30; % number of obstacles
+nO = 10; % number of obstacles
 nE = 4; % number of edges per obstacle (not changeable).
 minLen.a = 1; % Obstacle size bounds
 maxLen.a = 4;
@@ -53,7 +53,7 @@ milestones = [x0; xF];
 e = zeros(2,2);
 % Number of edges to add
 p = 8;
-t= 0;
+t = 0;
 tm = 0;
 te = 0;
 ts = 0;
@@ -92,6 +92,7 @@ while ((~done) && (t < 100))
             e(ind(j),cur) = 1;
             e(cur,ind(j)) = 1;
             plot([milestones(ind(j),1) milestones(cur,1)],[milestones(ind(j),2) milestones(cur,2)],'m');
+            drawnow;
         else 
             e(ind(j),cur) = 0;
             e(cur,ind(j)) = 0;
@@ -101,7 +102,10 @@ while ((~done) && (t < 100))
     te = te + t3 - t2;
     % Check if a path from start to end is found
     t4 = cputime;
+    e
+    milestones
     [sp, sd] = shortestpath(milestones, e, 1, 2);
+
     if (sd>0)
         done = 1;
         for i=1:length(sp)-1
@@ -117,3 +121,4 @@ ts
 ec
 disp('Time to find shortest path');
 toc;
+pause;

### 2016-03-31 assignments/assignment_2/src/ME597-8-PRM/trajrollout.m

@@ -39,7 +39,7 @@ for i=1:nO
     obsEdges = [obsEdges; obsPtsStore(1:nE,2*(i-1)+1:2*i) obsPtsStore([2:nE 1],2*(i-1)+1:2*i)];
 end
 
-% Plot obstacles
+% plot obstacles
 figure(1); clf; hold on;
 plotEnvironment(obsPtsStore,xMin, xMax, x0, xF);
 drawnow();
@@ -47,48 +47,44 @@ figure(1); hold on;
 disp('Time to create environment');
 toc;
 
-%# create AVI object
-vidObj = VideoWriter('traj_rollout4.avi');
-vidObj.Quality = 100;
-vidObj.FrameRate = 5;
-open(vidObj);
-
-
-%% Vehicle
+% vehicle
 dt = 0.01;
 uMin = [2 -2]; % bounds on inputs, [velocity, rotation rate]
 uMax = [2 2]; % bounds on inputs, [velocity, rotation rate]
 uR = uMax-uMin; % range of inputs
 sMin = 20; % steps to move
 sMax = 100; % steps to compute for rollout
-n_traj = 15; % number of trajectories to roll out
+n_traj = 5; % number of trajectories to roll out
 
 %% Trajectory rollout, created until solution found
 tic;
 done = 0;
 x_cur = x0; %current position
 t= 0;
-T = 100;
+T = 120;
 f = 1;
 
 
 while ((~done) && (t < T))
     score_step = inf;
-    for i = 1:n_traj
-        % Constant speed, linear distribution of turn rates
-        input = [uR(1)/2+uMin(1) uR(2)*(i-1)/(n_traj-1)+uMin(2)];
-        steps = sMax; 
 
-        % Propagate Dynamics
+    % roll out trajectory
+    for i = 1:n_traj
+        % constant speed, linear distribution of turn rates
+        input = [uR(1)/2+uMin(1) uR(2)*(i-1)/(n_traj-1)+uMin(2)];
+        steps = sMax;
+
+        % propagate dynamics
         x = x_cur;
-        for j=2:steps
-            x(j,:) = x(j-1,:)+[input(1)*cos(x(j-1,3))*dt input(1)*sin(x(j-1,3))*dt input(2)*dt]; 
+        for j = 2:steps
+            x(j, :) = x(j - 1, :) + [input(1)*cos(x(j-1,3))*dt input(1)*sin(x(j-1,3))*dt input(2)*dt];
         end
[…]

### 2016-03-31 assignments/assignment_2/src/astar_example.m

@@ -1,24 +1,0 @@
-source('planning.m');
-
-%% Generate a graph
-n = 100; % Nodes
-s = 10; % Space
-
-% Random nodes
-nodes = s * rand(n, 2);
-e = sparse(zeros(n, n));
-D = sparse(zeros*ones(n, n));
-
-
-% add closest p edges
-[e, D] = create_closest_edges(nodes);
-
-% pick furthest apart start and end node
-[dmax, start, finish] = calculate_furthest_distance_betweeen_nodes(nodes);
-
-% plot graph
-plot_nodes(1, nodes, start, finish);
-astar(nodes, start, finish, dmax, e, D);
-
-drawnow;
-pause;

### 2016-03-31 assignments/assignment_2/src/igvc_path_wavefront.m

@@ -1,7 +1,7 @@
 % source('lib/wavefront.m');
 % source('lib/shortest_wavefront_path.m');
 % source('lib/image_to_binary_map.m');
-addpath('lib/')
+addpath('wavefront_scripts/')
 map = imread('IGVCmap.jpg');
 map = image_to_binary_map(map);
 imshow(map);
@@ -11,15 +11,14 @@ end_pos = [5.0, 1.0];
 
 
 % convert start and end points to grid locations
-start_pos = start_pos*10/dxy;
-end_pos = end_pos*10/dxy;
+start_pos = start_pos * 10 / dxy;
+end_pos = end_pos *10 / dxy;
 
-[wavefrontmap, path]= wavefront(map, start_pos, end_pos, 0, 1);
+[wavefrontmap, path] = wavefront(map, start_pos, end_pos, 0, 1);
 imagesc(wavefrontmap);
 
 set(gca, 'YDir', 'normal')
 hold on
 plot(path(:,1), path(:,2), '-r');
 colorbar;
-
-
+pause

### 2016-03-31 assignments/assignment_2/src/planning.m

@@ -1,243 +1,0 @@
-function [samples, milestones] = sample_map(nb_samples, map, xR, xMin, pos_start, pos_end)
-    samples_x = int32(xR(1) * rand(nb_samples, 1) + xMin(1));
-    samples_y = int32(xR(2) * rand(nb_samples, 1) + xMin(2));
-    samples = [samples_x, samples_y];
-
-    milestones = [pos_start(1:2); pos_end;];
-    for i = 1:length(samples)
-        sample = samples(i, :);
-
-        if map(sample(1), sample(2)) == 0
-            map(sample(1), sample(2));
-            milestones = [milestones; sample];
-        end
-    end
-end
-
-function [dmax, start, finish] = calculate_furthest_distance_betweeen_nodes(nodes)
-    dmax = 0;
-    start = 0;
-    finish = 0;
-    n = length(nodes);
-
-    for i = 1:n
-        for j = i:n
-            d = norm(nodes(i,:) - nodes(j,:));
-
-            if (d > dmax)
-                dmax = d;
-                start = i;
-                finish = j;
-            end
-        end
-    end
-end
-
-function [node, index] = closest_node(nodes, x, y)
-    index = 0;
-    i = length(nodes);
-    random_node = nodes(i, :);
-    dx = x - random_node(1);
-    dy = y - random_node(2);
-    dmin = sqrt(dx^2 + dy^2);
-
-    for i = 1:length(nodes)
-        dx = x - nodes(i, 1);
-        dy = y - nodes(i, 2);
-        d = sqrt(dx^2 + dy^2);
-
-        if (d != 0 && d < dmin)
-            dmin = d;
-            index = i;
-        end
-    end
-
-    node = nodes(index, :);
-    index = index;
-end
-
-function [edges, dists] = create_closest_edges(nodes)
-    p = 5;
-    n = length(nodes);
-    edges = sparse(zeros(n, n));
-    dists = sparse(zeros*ones(n, n));
-
-    for i = 1:n
-        % calculate distances between nodes
-        for j = 1:n
-            dx = nodes(i, 1) - nodes(j, 1);
-            dy = nodes(i, 2) - nodes(j, 2);
-            d(j) = sqrt(dx^2 + dy^2);
-        end
-
-        % sort calculated distances between nodes
-        [d2, indicies] = sort(d);
-
-        % create edges to p closest nodes
-        for j = 1:p
-            if (i != indicies(j))
-                edges(i, indicies(j)) = 1;
-                edges(indicies(j), i) = 1;
[…]

### 2016-03-31 assignments/assignment_2/src/util.m

@@ -187,7 +187,7 @@ function plot_samples(fig_index, samples, milestones)
     figure(fig_index);
     hold on;
 
-    % plot(samples(:, 1), samples(:, 2), 'r.');
+    % plot(samples(:, 1), samples(:, 2), 'go');
     plot(milestones(:, 1), milestones(:, 2), 'bo');
 end
 
@@ -204,5 +204,4 @@ function plot_map(fig_index, map, pos_start, pos_end, dxy)
 
     % plot parameters
     axis equal
-    pause
 end

### 2016-03-31 assignments/assignment_2/src/wavefront_scripts/image_to_binary_map.m

@@ -1,5 +1,4 @@
 function [imout] = image_to_binary_map(I)
-imout = im2bw(I, 0.7); % Convert to 0-1 image
-imout = 1-flipud(imout)'; % Convert to 0 free, 1 occupied and flip.
+    imout = im2bw(I, 0.7);  % Convert to 0-1 image
+    imout = 1 - flipud(imout)';  % Convert to 0 free, 1 occupied and flip.
 end
-

### 2016-03-31 assignments/assignment_2/src/astar_example.m
Forgot to add certain files

@@ -1,0 +1,24 @@
+source('planning.m');
+
+%% Generate a graph
+n = 10; % Nodes
+s = 10; % Space
+
+% Random nodes
+nodes = s * rand(n, 2);
+e = sparse(zeros(n, n));
+D = sparse(zeros*ones(n, n));
+
+
+% add closest p edges
+[e, D] = create_closest_edges(nodes);
+
+% pick furthest apart start and end node
+[dmax, start, finish] = calculate_furthest_distance_betweeen_nodes(nodes);
+
+% plot graph
+plot_nodes(1, nodes, start, finish);
+astar(nodes, start, finish, dmax, e, D);
+
+drawnow;
+pause;

### 2016-03-31 assignments/assignment_2/src/planning.m

@@ -1,0 +1,376 @@
+function [samples, milestones] = sample_map(nb_samples, map, map_min, map_max, pos_start, pos_end)
+    map_range = map_max - map_min;
+    samples_x = int32(map_range(1) * rand(nb_samples, 1) + map_min(1));
+    samples_y = int32(map_range(2) * rand(nb_samples, 1) + map_min(2));
+    samples = [samples_x, samples_y];
+
+    milestones = [
+        pos_start(1:2) / 0.1;
+        pos_end / 0.1
+    ];
+    for i = 1:length(samples)
+        sample = samples(i, :);
+
+        if map(sample(1), sample(2)) == 0
+            milestones = [milestones; sample];
+        end
+    end
+end
+
+function [dmax, start, finish] = calculate_furthest_distance_betweeen_nodes(nodes)
+    dmax = 0;
+    start = 0;
+    finish = 0;
+    n = length(nodes);
+
+    for i = 1:n
+        for j = i:n
+            dx = nodes(i, 1) - nodes(j, 1);
+            dy = nodes(i, 2) - nodes(j, 2);
+            d = sqrt(dx^2 + dy^2);
+
+            if (d > dmax)
+                dmax = d;
+                start = i;
+                finish = j;
+            end
+        end
+    end
+end
+
+function [node, index] = closest_node(nodes, x, y)
+    index = 0;
+    i = length(nodes);
+    random_node = nodes(i, :);
+    dx = x - random_node(1);
+    dy = y - random_node(2);
+    dmin = sqrt(dx^2 + dy^2);
+
+    for i = 1:length(nodes)
+        dx = x - nodes(i, 1);
+        dy = y - nodes(i, 2);
+        d = sqrt(dx^2 + dy^2);
+
+        if (d ~= 0 && d < dmin)
+            dmin = d;
+            index = i;
+        end
+    end
+
+    node = nodes(index, :);
+    index = index;
+end
+
+function [edges, dists] = create_closest_edges(map, nodes, nb_edges)
+    n = length(nodes);
+    edges = zeros(n, n);
+    dists = zeros*ones(n, n);
+
+    for i = 1:n
+
+        % calculate distances between nodes
+        for j = 1:n
+            dx = nodes(j, 1) - nodes(i, 1);
+            dy = nodes(j, 2) - nodes(i, 2);
+            d(j) = sqrt(dx^2 + dy^2);
+        end
+
+        % sort calculated distances between nodes
+        [d2, indicies] = sort(d);
+
[…]

### 2016-04-02 assignments/assignment_2/report.tex
Update assignment 2 report

--- 2016-03-31 assignments/assignment_2/report.tex
@@
 \documentclass{article}
+
+% GRAPHICS
+\usepackage{float}
+\usepackage{subcaption}
+\usepackage{tikz}
+\usepackage{tikzscale}
+\usetikzlibrary{calc}
+\usepackage{graphicx}
 
@@
 
-A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line ahead of the closest point on the line to the current robot position.
+A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line, ahead of the closest point on the trajectory line to the current robot position.
+
+\subsection{Closest Point on the Trajectory Line to the Robot}
+The closest point between the robot's position and the trajectory line can be calculated.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{images/dot_product_projection.png}
+	\caption{Dot Product Projection)}
+	\label{fig:dot_product_projection}
+\end{figure}
+
+Let the vector $a$ denote the vector from the start of the trajectory line to the position of the robot, and vector $b$ denote the start and end of the trajectory line.
+To calculate the closest point on vector $b$ to the robot position one simply has to project vector $a$ onto vector $b$, this can be calculated via:
+
+\begin{equation}
+	\text{proj}_{\vec{a}\vec{b}} 
+		= \dfrac{\vec{a} \cdot \vec{b}}{|\vec{a}|}
+			\dfrac{\vec{a}}{|\vec{a}|} 
+		= \dfrac{\vec{a} \cdot \vec{b}}{|\vec{a}|^{2}}
+			\vec{a}
+\end{equation}
 
 \newpage
-\section{Planner}
+\subsection{Calculation of the Carrot Point}
+Once the closest point on the trajectory line to the robot is found, calculating a carrot point along the trajectory line is the closest point on the trajectory line $p_{\text{closest}}$ plus the product of look ahead distance $r$ times the unit vector of the trajectory line $b$.
+
+\begin{equation}
+	\text{carrot} = p_{\text{closest}} + r \dfrac{\vec{b}}{|\vec{b}|}
+\end{equation}
+
+\subsection{Carrot Controller}
+We implemented a proportional carrot controller and traced a rectangle of $20m$ by $5m$ at $3ms^{-1}$.
+This is the resulting motion of the bicycle (See Fig~\ref{fig:bicycle_carrot}), we used a proportional gain $k_{p} = 2$ and look ahead distance $r$ at $2$, $0.2$ and $5$.
+
+From Fig~\ref{fig:bicycle_carrot} we can see that different look ahead distance $r$ impacts the way the robot traces a rectangle.
+If the look ahead distance is too low (i.e.
+Fig~\ref{fig:bicycle_carrot_bad} where $r = 0.2$), the carrot will be a very small distance ahead of the robot, making small adjustments unlikely thereby the angle of the steering oscillates between $-30$ degrees to $30$ degrees (the max steering angle).
+
+If the carrot is at a medium look ahead distance away from the robot  (i.e.
+Fig~\ref{fig:bicycle_carrot_ok} where $r = 2$), the robot tends to be quite agreessive in compensating for overshooting the trajectory.
+As we increase the look ahead distance $r$ however, the correction angle is dampened, causing a less agreessive correction, but longer time to return to the trajectory line.
+
+\begin{figure}[H]
+	\centering
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot_bad.jpg}
+		\caption{$k_{p} = 2$, $r = 0.2$}
+		\label{fig:bicycle_carrot_bad}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot.jpg}
+		\caption{$k_{p} = 2$ and $r = 2$}
+		\label{fig:bicycle_carrot_ok}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot_better.jpg}
+		\caption{$k_{p} = 2$, $r = 5$}
+		\label{fig:bicycle_carrot_better}
+	\end{subfigure}
+
+	\caption{Bicycle motion using carrot controller starting at (23, 10)}
+	\label{fig:bicycle_carrot}
+\end{figure}
+
+\newpage
+\section{IGVC Planner}
+\label{sec:igvc_planner}
+We were given a map of the Intelligent Ground Vehicle Competition in the form of a $926 \times 716$ element grid, where each cell
+represents a 10 cm X 10 cm area of the course, creating a 92.6 m X 71.6 m environment.
+
+Our goal is to implement a planner and present a combined motion planning solution that finds a straight-line path through the environment, then uses the carrot planner to locally drive the vehicle to the goal location.
+Where the start and end locations are ($4.0m$, $0.5m$, $3.14159 rad$) and ($5.0 m$, $1.0 m$, not defined) for $x$, $y$ and $θ$.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\textwidth]{images/IGVCmap.jpg}
+	\caption{IGVC Map}
+	\label{fig:igvc_map}
+\end{figure}
+
+\newpage
+\subsection{Wavefront Planner}
+\label{subsec:wavefront}
+Since the map given represents an occupancy grid of free space and obstacles, our intial approach was to use the breadth first search based planner, by using the wavefront method to calculate the cost distance to traverse from start to goal point, and finding the lowest cost path.
+In Fig~\ref{fig:wavefront} you can see the result of one wavefront plan and the lowest cost path leading from the start to goal point.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\textwidth]{images/wavefront_igvc.eps}
+	\caption{Wavefront IGVC Map}
+	\label{fig:wavefront}
+\end{figure}
+
+The problem with wavefront is as follows:
+
+\begin{itemize}
+	\item{\textbf{Manhattan Distance}: Due to the nature of how the wavefront traverses the map, the paths found have inherently right angle turns, using a carrot controller following paths with right angles can be problematic.}
+
+	\item{\textbf{Difficult to represent robot}: This is not limited to the wavefront method, but for any occupancy grid planner methods, the grid size should be smaller than the robot.}
+
+	\item{\textbf{Exploits holes in map}: Holes between objects can be a problem such as Fig~\ref{fig:wavefront}, near the start point wavefront finds a small gap between the circular obstacles, however, in reality the physical robot will not be able to fit through the gap.}
+\end{itemize}
+
+In conclusion, we gave up on the wavefront planner because the paths produced were not suitable for the carrot controller.
+
+\newpage
+\subsection{Probablistic Roadmap Planner}
+\label{subsec:prm}
+In our next approach we used the Probablistic Roadmap (PRM) planner, purely out of curiosity and it seemed like an intuitive alternative to wavefront planner.
+
+For the implementation we had to make modifications to the PRM example code given, as the code given assumes the obstacles are in the form of polygon points, the example code makes use of Matlab's `inpolygon()` function to detect whether a sample point is within a polygon.
+However the map given represents an occupancy grid instead of the obstacle polygons as points, we therefore had to replace the collision checking to use a ray tracing algorithm such as Bresenham's line algorthm, so that we can traverse between the PRM sample points and create collision free edges.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_200.jpg}
+		\caption{200 Samples}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_500.jpg}
+		\caption{500 Samples}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_1000.jpg}
+		\caption{1000 Samples}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_5000.jpg}
+		\caption{5000 Samples}
+	\end{subfigure}
+	\caption{PRM Planner and Carrot Controller}
+	\label{fig:prm}
+\end{figure}
+
+\newpage
+From Fig~\ref{fig:prm} we show the combination of PRM and carrot controller through the IGVC map with varying number of samples (200, 500, 1000, 5000).
+While 200 sample points was sufficient, it is easy to recognize the path as sub-optimal compared to the paths generated with 500 sample points and beyond, we can observe that the path gets more and more optimal as we increase the number of sample points in the map.
+
+\subsubsection{PRM Planner with Sample Points Padded}
+\label{subsec:prm_padding}
+We attempted to make improvements with the PRM approach so that the bicycle forward motion does not collide with the obstacles, we improved the PRM planner by ensuring the sample points are a set distance away from the obstacles, this is done by performing a line search on 8 directions (N, NE, E, SE, S, SW, W, NW), if collision is detected the sample point is dropped.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/prm_resampling.jpg}
+	\caption{PRM Resampling}
+	\label{fig:prm_resampling}
+\end{figure}
+
+\section{Limitations and Future Improvements to the PRM Planner}
+\subsection{Limitations}
+Previously in Section~\ref{sec:igvc_planner} we have explored both wavefront and PRM path planning methods, both methods alone are not satifactory in planning a path for the bicycle through the IGVC course, we will discuss three limitations below:
+
+\begin{itemize}
+	\item{\textbf{Path is not smooth}: The paths generated by both wavefront and PRM while optimal it does not take into account the motion model of the bicycle.
+Some of the planned paths particularly nearer towards the middle of the course where the bicycle has to make a U-turn, the angle change is very sharp and sudden, improvement in either the controller or path planned should take the motion model into account and create a smooth path or motion through the turn.}
+
+	\item{\textbf{No collision detection}: The above two methods does not perform collision dection of the robot with regards to the obstacles in the map, there are methods such as trajectory rollout that iterates at every timestep performing collision check at every possible motion change to make sure the path is valid.}
+
+	\item{\textbf{Wasted Computation Around Non-Optimal Areas}:}
+
+\end{itemize}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/collision_example.jpg}
+	\caption{Collision Example}
+	\label{fig:collision_example}
+\end{figure}
+
+\subsection{Future Improvements}
+While padding was useful, it suffers around the choke points in the map (figure example...).
+
+Trajectory roll out please...
 

### 2016-04-03 assignments/assignment_2/report.tex
updated paper more to do

--- 2016-03-31 assignments/assignment_2/report.tex
@@
 
-At current we have a motion model for both the front and the rear wheel of the bicycle, however we can simplify it using the Instantaneous Center of Rotation to combine both the front and rear wheel together.
+At current we have a motion model for both the front and the rear wheel of the bicycle, however we can simplify it using the Instantaneous Center of Rotation (ICR) to combine both the front and rear wheel together.
 
@@
 
-Implementing the bicycle motion model in Matlab and simulating the motion for 20 seconds with the following parameters, we obtain a motion that resembles Fig~\ref{fig:bicycle_20s}.
+Implementing the bicycle motion model in Matlab and simulating the motion for 20 seconds with the following parameters, we obtain the trajectory observed in Fig~\ref{fig:bicycle_20s}.
+From the inputs outlined below, the observed trajectory appears to be valid as the heading starts at 10 degrees and then decreases at a rate of -1 degree per second.
+This means during the first half of the run the steering angle is positive, causing it to steer to the left, straighten out for a portion and then begin starting to turn to the right as the steering angle becomes negative.
 
@@
 
-Just looking at Fig~\ref{fig:bicycle_20s} we can roughly validate the motion as valid, since the angle starts from +10 and ends at -10 degrees over time (20 seconds).
-
 \newpage
@@
 
-A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line ahead of the closest point on the line to the current robot position.
+A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line, ahead of the closest point on the trajectory line to the current robot position.
+
+\subsection{Closest Point on the Trajectory Line to the Robot}
+The closest point between the robot's position and the trajectory line can be calculated by first calculating the projection of the vector formed by the current location and the desired
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\textwidth]{images/dot_product_projection.png}
+	\caption{Dot Product Projection)}
+	\label{fig:dot_product_projection}
+\end{figure}
+
+Let the vector $a$ denote the vector from the start of the trajectory line to the position of the robot, and vector $b$ denote the start and end of the trajectory line.
+To calculate the closest point on vector $b$ to the robot position one simply has to project vector $a$ onto vector $b$, this can be calculated via:
+
+\begin{equation}
+	\text{proj}_{\vec{a}\vec{b}} 
+		= \dfrac{\vec{a} \cdot \vec{b}}{|\vec{a}|}
+			\dfrac{\vec{a}}{|\vec{a}|} 
+		= \dfrac{\vec{a} \cdot \vec{b}}{|\vec{a}|^{2}}
+			\vec{a}
+\end{equation}
 
 \newpage
-\section{Planner}
+\subsection{Calculation of the Carrot Point}
+Once the closest point on the trajectory line to the robot is found, calculating a carrot point along the trajectory line is the closest point on the trajectory line $p_{\text{closest}}$ plus the product of look ahead distance $r$ times the unit vector of the trajectory line $b$.
+
+\begin{equation}
+	\text{carrot} = p_{\text{closest}} + r \dfrac{\vec{b}}{|\vec{b}|}
+\end{equation}
+
+\subsection{Carrot Controller}
+We implemented a proportional carrot controller and traced a rectangle of $20m$ by $5m$ at $3ms^{-1}$.
+This is the resulting motion of the bicycle (See Fig~\ref{fig:bicycle_carrot}), we used a proportional gain $k_{p} = 2$ and look ahead distance $r$ at $2$, $0.2$ and $5$.
+
+From Fig~\ref{fig:bicycle_carrot} we can see that different look ahead distance $r$ impacts the way the robot traces a rectangle.
+If the look ahead distance is too low (i.e.
+Fig~\ref{fig:bicycle_carrot_bad} where $r = 0.2$), the carrot will be a very small distance ahead of the robot, making small adjustments unlikely thereby the angle of the steering oscillates between $-30$ degrees to $30$ degrees (the max steering angle).
+
+If the carrot is at a medium look ahead distance away from the robot  (i.e.
+Fig~\ref{fig:bicycle_carrot_ok} where $r = 2$), the robot tends to be quite agreessive in compensating for overshooting the trajectory.
+As we increase the look ahead distance $r$ however, the correction angle is dampened, causing a less agreessive correction, but longer time to return to the trajectory line.
+
+\begin{figure}[H]
+	\centering
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot_bad.jpg}
+		\caption{$k_{p} = 2$, $r = 0.2$}
+		\label{fig:bicycle_carrot_bad}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot.jpg}
+		\caption{$k_{p} = 2$ and $r = 2$}
+		\label{fig:bicycle_carrot_ok}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{images/bicycle_carrot_better.jpg}
+		\caption{$k_{p} = 2$, $r = 5$}
+		\label{fig:bicycle_carrot_better}
+	\end{subfigure}
+
+	\caption{Bicycle motion using carrot controller starting at (23, 10)}
+	\label{fig:bicycle_carrot}
+\end{figure}
+
+\newpage
+\section{IGVC Planner}
+\label{sec:igvc_planner}
+We were given a map of the Intelligent Ground Vehicle Competition in the form of a $926 \times 716$ element grid, where each cell
+represents a 10 cm X 10 cm area of the course, resulting in a 92.6 m X 71.6 m environment.
+
+Our goal is to implement a planner and present a combined motion planning solution that finds a straight-line path through the environment, then uses the carrot controller to provide the inputs required to drive the robot to the start and end locations which are ocated at ($x = 4.0m$, $y = 0.5m$, $\theta = 3.14159 rad$) and ($x = 5.0 m$, $y = 1.0 m$, $theta =$ not defined) respectively.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\textwidth]{images/IGVCmap.jpg}
+	\caption{IGVC Map}
+	\label{fig:igvc_map}
+\end{figure}
+
+\newpage
+\subsection{Wavefront Planner}
+\label{subsec:wavefront}
+Since the map given represents an occupancy grid of free space and obstacles, our initial approach to the planning portion was to apply the wavefront a path that finds an optional path between start to goal point.
+Fig~\ref{fig:wavefront} highlights the results of the wavefront planner and highlights the resulting path found by gradient decent.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\textwidth]{images/wavefront_igvc.eps}
+	\caption{Wavefront IGVC Map}
+	\label{fig:wavefront}
+\end{figure}
+
+While the wavefront method found a solution optimal on the grid based environment, it is far from optimal then a path generated in the continuous space.
+The first problem stems from the fact that wavefront method is a grid based method based on a breadth first search that starts and the end goal and calculates a distance between the end goal and all points in the map.
+Because the distance is based on the number of grids between the start and end point the distance calculated actually reflects the Manhattan Distance between the start and end goals rather than the Euclidian Distance.
+This means that driving at a $45^o $ angle has the same distance as two paths that first travel horizontal and then upward.
+Furthermore the robots trajectory is restricted to the exploration directions used to generate the wavefront which in this case were a set 4 moves, mainly move up, move right, move left and move down.
+
+Additional problems are realized when one takes into account that the fact that robot is likely larger than the grid cells which makes collision avoidance and detection difficult.
+In many cases the grid cells are assumed to be the size of the robot but this has the additional drawback of causing obstacles to become very course and poorly represented.
+In Fig~\ref{fig:wavefront} it can be noted that the wavefront planner slips between a very small gap between two pylons on the course, which unless the robot is 10cm by 10cm, would be an impossible path for the robot to follow.
+Additionally the robot also tends to hug obstacles very closely which means that any errors in possession or heading are likely to result in collisions.
+
+Lastly, for this large map, the run time was over 40 seconds without any collision checking procedures and therefore this approach was abandoned in favour of a Probabilistic Roadmap Planner (PRM).
+
+\subsection{Probabilistic Roadmap Planner}
+\label{subsec:prm}
+In our next approach we used the Probabilistic Roadmap (PRM) planner, purely out of curiosity and it seemed like an intuitive alternative to wavefront planner.
+
+For the PRM implementation on a grid based environment, we had to make modifications to the PRM example code given, which assumes the obstacles are in the form of set of polygon points and exploits Matlab's inpolygon function to detect whether a sample point located within a polygon.
+However the map given represents an occupancy grid instead of the obstacle polygons as points, and therefore had the collision checking to be replaced by a ray tracing algorithm.
+In our implementation we utilized a modified version of Bresenham's line algorithm, to find create collision free edges between sample points.
+
+We implemented a PRM planner and then applied the carrot controller outlined in Question 2 to the resulting paths which are shown in  Fig~\ref{fig:prm} which also highlights the effect of using varying sample sizes in the PRM.
+From testing it appears that a sample size of 200 will yield a valid solution in about 50 percent of the time, a sample size of 500 will yield a solution is 90 percent of cases and a sample size of over 1000 always resulted in a solution in all of our tests.
+
+Higher sample sizes also tend to lead to smoother and more optimal paths which can be observed by comparing  the 200 sample case to the 5000 sample case highlighted in Fig~\ref{fig:collision_example}.
+The run time of the PRM when using 5000 points less than 3 seconds compared to the wavefront planner which took approximately a minute to find a solution.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_200.jpg}
+		\caption{200 Samples}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_500.jpg}
+		\caption{500 Samples}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_1000.jpg}
+		\caption{1000 Samples}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{images/prm_5000.jpg}
+		\caption{5000 Samples}
+	\end{subfigure}
+	\caption{PRM Planner and Carrot Controller}
+	\label{fig:prm}
+\end{figure}
+
+\subsubsection{PRM Planner with Sample Points Padded}
+\label{subsec:prm_padding}
+
+While the PRM all yielded valid solutions, it was noted that at some locations along the path the robot comes either very close to an obstacle cuts the corners extremely tightly due to a lack of particles in locations near choke points.
+An example of the PRM cutting a corner to tightly is highlighted in  Fig~\ref{fig:prm}.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/collision_example.jpg}
+	\caption{Collision Example}
+	\label{fig:collision_example}
+\end{figure}
+
+We attempted to address this issue by adjusting the way that sample points were created in the PRM planner by checking for any obstacles within that are within 0.5 m  of each sample point.
+If an obstacle is detected with 1 m of a point, the point is deleted and a set of 5 additional points are created and randomly distributed within a circle centred at the deleted sample point with a radius of 1.5 m.
+These points are again checked for proximity to obstacles and pruned in a the same manner described as above.
+
+This approach resulted in areas near walls and obstacles to be sampled much more heavily compared to open spaces and also resulted in smoother paths near obstacles and are higlighted in Fig~\ref{fig:prm_resampling}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{images/prm_resampling.jpg}
+	\caption{PRM Resampling with 1000 points and a collision check raduis of 0.5 m}
+	\label{fig:prm_resampling}
+\end{figure}
+
+\section{Limitations and Future Improvements to the PRM Planner}
+\subsection{Limitations}
+
+Previously in Section~\ref{sec:igvc_planner}  explored both wavefront and PRM path planning methods, both methods alone are not satisfactory in planning a path for the bicycle through the IGVC course, we will discuss three limitations below:
+
+\begin{itemize}
+	\item{\textbf{Path is not smooth}: The paths generated by both wavefront and PRM do not account motion model of the bicycle.
+Some portions of the planned paths have very sharp edges or corners, particularly in locations near very sharp obstacles such as the wall located in the middle of the course.
+Such an angle is to sharp for the controller and therefore results in a non optimal turn around the obstacle that could be avoided if the planner could take into account the robots turning radius.
+}
+
+\item{\textbf{No collision detection}: None of the explored methods explicitly perform collision detection of a robot with an actual size.
+We approximated some collision checking using our re-sampling approach which did eliminate a significant portion of collisions but not all of them.
+One possible way to perform collision checking in the PRM approach would be to modify the A* search algorithm to check for collisions with obstacles when selecting an edge to transverse.
+One option for collision checking would be to check parallel line segments located at a distance 0.5 robot widths above and below the line segment formed by a selected edge for collision.
+If one of these lines was to found to interest an obstacle the edge should not be added to the final path.
+}
+
+\item{\textbf{Map is assumed to be known, accurate and static}: Probably the largest limitation to our approach is the assumption that the map is accurate and static.
+A local planner such as trajectory roll-out combined with some kind of range sensor, such as lidar, would allow the robot to determine paths that avoid uncounted for obstacles.
+In the case of non-static obstacles, such as other robots (since it is a race) a real time object tracker could be implemented and used to make predictions as to where moving obstacles will be in future which could then be used by the local planner to come up with a collision free trajectory.
+}
+
+\end{itemize}
 

### 2016-04-03 assignments/assignment_2/report.tex
stans edits v2

@@
 \section{Motion Model of a Bicycle}
-
+Define the bicycle motion model for an Ackermann steered robot as shown in the configuration below(and presented in the motion modelling lecture notes). 
 \begin{figure}[H]
@@
 
-Motion of front wheel:
+From the lecture notes, the motion of front wheel can be written as follows:
 
@@
 
-Motion of rear wheel:
+Similarly the motion of the rear wheel is as follows:
 
@@
 
-At current we have a motion model for both the front and the rear wheel of the bicycle, however we can simplify it using the Instantaneous Center of Rotation (ICR) to combine both the front and rear wheel together.
+These two equations can be linked and simplified by using the Instantaneous Center of Rotation (ICR) to combine equations of motion for the front and rear wheels as follows.
 
@@
 
-From Fig~\ref{fig:bicycle_icr} we can derive the relationship between the steering angle $\delta$ relative to the bicycle's heading:
+From Fig~\ref{fig:bicycle_icr} the relationship between the steering angle $\delta$ relative to the bicycle's heading can be written as:
 
@@
 
-Further, we know that the angular velocity $\omega$ from the point ICR of both the front and rear wheel is:
+Moreover, we know that the angular velocity $\omega$ from the point ICR of both the front and rear wheel is:
 
@@
 
-Implementing the bicycle motion model in Matlab and simulating the motion for 20 seconds with the following parameters, we obtain the trajectory observed in Fig~\ref{fig:bicycle_20s}.
-From the inputs outlined below, the observed trajectory appears to be valid as the heading starts at 10 degrees and then decreases at a rate of -1 degree per second.
-This means during the first half of the run the steering angle is positive, causing it to steer to the left, straighten out for a portion and then begin starting to turn to the right as the steering angle becomes negative.
+Using Equation 8, the bicycle motion model was simulated in Matlab over a period of 20 seconds with the following parameters:
 
@@
 
+The resulting trajectory from the simulation inputs is shown in Fig~\ref{fig:bicycle_20s}.
+Based on the simulation inputs the the observed trajectory appears to be valid as the heading starts at 10 degrees and then decreases at a rate of -1 degree per second.
+This means during the first half of the run the steering angle is positive, causing it to steer to the left, straighten out for a portion and then begin starting to turn to the right as the steering angle becomes negative.
+These motions result in the "S" shape that is depicted in  Fig~\ref{fig:bicycle_20s}
+
 \begin{figure}[H]
@@
 \section{Carrot Controller for Bicycle}
+
+Develop a carrot following controller.
+The way this controller works is you define a carrot, or point on the desired trajectory line a fixed distance, $r$, ahead of the closest point on the line to the current robot position.
 
@@
 \subsection{Carrot Controller}
-We implemented a proportional carrot controller and traced a rectangle of $20m$ by $5m$ at $3ms^{-1}$.
+We implemented a proportional (P) carrot controller and traced a rectangle of $20m$ by $5m$ at $3ms^{-1}$.
 This is the resulting motion of the bicycle (See Fig~\ref{fig:bicycle_carrot}), we used a proportional gain $k_{p} = 2$ and look ahead distance $r$ at $2$, $0.2$ and $5$.
@@
 
-While the wavefront method found a solution optimal on the grid based environment, it is far from optimal then a path generated in the continuous space.
-The first problem stems from the fact that wavefront method is a grid based method based on a breadth first search that starts and the end goal and calculates a distance between the end goal and all points in the map.
-Because the distance is based on the number of grids between the start and end point the distance calculated actually reflects the Manhattan Distance between the start and end goals rather than the Euclidian Distance.
+While the wavefront method successfully found an optimal solution on the grid based environment, it is far from optimal then a path generated in the continuous space.
+This problem stems from the fact that wavefront method is a grid based method based on a breadth first search that starts and the end goal and calculates a distance between the end goal and all points in the map.
+Because the distance is based on the number of grids between the start and end point the distance calculated actually reflects the Manhattan Distance between the start and end goals rather than the Euclidean Distance.
 This means that driving at a $45^o $ angle has the same distance as two paths that first travel horizontal and then upward.
@@
 
-For the PRM implementation on a grid based environment, we had to make modifications to the PRM example code given, which assumes the obstacles are in the form of set of polygon points and exploits Matlab's inpolygon function to detect whether a sample point located within a polygon.
-However the map given represents an occupancy grid instead of the obstacle polygons as points, and therefore had the collision checking to be replaced by a ray tracing algorithm.
+For the PRM implementation on a grid based environment, we had to make modifications to the provided PRM example, which assumes the obstacles are in the form of set of polygon points.
+This allows the PRM planner implemented in the ME 597 example code to exploit Matlab's \textit{inpolygon }function to detect whether a sample point located within a polygon.
+
+However the map given in this assignment is represented an occupancy grid instead of set of polygons, and therefore the collision checking portion of the PRM code to be replaced by a ray tracing algorithm.
 In our implementation we utilized a modified version of Bresenham's line algorithm, to find create collision free edges between sample points.
@@
 We implemented a PRM planner and then applied the carrot controller outlined in Question 2 to the resulting paths which are shown in  Fig~\ref{fig:prm} which also highlights the effect of using varying sample sizes in the PRM.
-From testing it appears that a sample size of 200 will yield a valid solution in about 50 percent of the time, a sample size of 500 will yield a solution is 90 percent of cases and a sample size of over 1000 always resulted in a solution in all of our tests.
+From testing it appears that a sample size of 200 will yield a valid solution in about 50 percent of the time, a sample size of 500 will yield a solution is 90 percent of cases and a sample sizes with more than 1000 sample points always resulted in a solution.
 
-Higher sample sizes also tend to lead to smoother and more optimal paths which can be observed by comparing  the 200 sample case to the 5000 sample case highlighted in Fig~\ref{fig:collision_example}.
-The run time of the PRM when using 5000 points less than 3 seconds compared to the wavefront planner which took approximately a minute to find a solution.
+Higher sample sizes also tended to lead to smoother and more optimal paths which can be observed by comparing  the 200 sample case to the 5000 sample case highlighted in Fig~\ref{fig:collision_example}.
+The run time of the PRM when using 5000 points less than 3 seconds which is a significant improvement over the wavefront planner which took over a minute to find a solution.
 
@@
 
-While the PRM all yielded valid solutions, it was noted that at some locations along the path the robot comes either very close to an obstacle cuts the corners extremely tightly due to a lack of particles in locations near choke points.
+While the PRM yielded a complete path between teh start and end goals, it was noted that at some locations along the path the robot will pass extremely close to obstacles due to the PRM cutting the corners extremely tightly.
+This behaviour is due to a lack of particles in locations near choke points.
 An example of the PRM cutting a corner to tightly is highlighted in  Fig~\ref{fig:prm}.
@@
 
-We attempted to address this issue by adjusting the way that sample points were created in the PRM planner by checking for any obstacles within that are within 0.5 m  of each sample point.
-If an obstacle is detected with 1 m of a point, the point is deleted and a set of 5 additional points are created and randomly distributed within a circle centred at the deleted sample point with a radius of 1.5 m.
+We attempted to address this issue by adjusting the way that sample points were created in the PRM planner by checking for any obstacles within that are within 0.5 m circle  of each sample point.
+If an obstacle is detected with 0.5 m of a point, the point is deleted and a set of 5 additional points are created and randomly distributed within a circle centred at the deleted sample point with a radius of 1.5 m.
 These points are again checked for proximity to obstacles and pruned in a the same manner described as above.
 
-This approach resulted in areas near walls and obstacles to be sampled much more heavily compared to open spaces and also resulted in smoother paths near obstacles and are higlighted in Fig~\ref{fig:prm_resampling}
+This approach resulted in areas near walls and obstacles to be sampled much more heavily compared to open spaces and also resulted in smoother paths near obstacles and are highlighted in Fig~\ref{fig:prm_resampling}
 
@@
 
-Previously in Section~\ref{sec:igvc_planner}  explored both wavefront and PRM path planning methods, both methods alone are not satisfactory in planning a path for the bicycle through the IGVC course, we will discuss three limitations below:
+Previously in Section~\ref{sec:igvc_planner}  explored both wavefront and PRM path planning methods, both methods alone are not satisfactory in planning a path for the bicycle through the IGVC course, we will discuss three limitations below along with possible solutions:
 
 \begin{itemize}
+
 	\item{\textbf{Path is not smooth}: The paths generated by both wavefront and PRM do not account motion model of the bicycle.

### 2016-04-03 assignments/assignment_2/report.tex
last round of edits

@@
 \section{Motion Model of a Bicycle}
-Define the bicycle motion model for an Ackermann steered robot as shown in the configuration below(and presented in the motion modelling lecture notes). 
+\textit{Define the bicycle motion model for an Ackermann steered robot as shown in the configuration below(and presented in the motion modelling lecture notes). }
 \begin{figure}[H]
@@
 
-Develop a carrot following controller.
-The way this controller works is you define a carrot, or point on the desired trajectory line a fixed distance, $r$, ahead of the closest point on the line to the current robot position.
+\textit{Develop a carrot following controller.
+The way this controller works is you define a carrot, or point on the desired trajectory line a fixed distance, $r$, ahead of the closest point on the line to the current robot position.}
 
@@
 
-A carrot controller is a controller that has a carrot point with a fixed distance $r$ on the trajectory line, ahead of the closest point on the trajectory line to the current robot position.
-
 \subsection{Closest Point on the Trajectory Line to the Robot}
-The closest point between the robot's position and the trajectory line can be calculated by first calculating the projection of the vector formed by the current location and the desired
+The first step in implementing the the carrot controller for the outlined problem is to first determine a way to calculate the correct location of the carrot point given the robot's current position.
+To do we can use the projection equation between two vectors.
 
@@
 
-\newpage
-\subsection{Calculation of the Carrot Point}
-Once the closest point on the trajectory line to the robot is found, calculating a carrot point along the trajectory line is the closest point on the trajectory line $p_{\text{closest}}$ plus the product of look ahead distance $r$ times the unit vector of the trajectory line $b$.
-
+Next we need to determine where to place the carrot point.
+Having already found the closest point on the trajectory line $p_{\text{closest}}$, the carrot is simply calculated by adding the look ahead distance $r$ times the unit vector of the trajectory line $b$ to the value of $p_{\text{closest}}$.
 \begin{equation}
@@
 
-\subsection{Carrot Controller}
+\subsection{Carrot Controller Implementation}
 We implemented a proportional (P) carrot controller and traced a rectangle of $20m$ by $5m$ at $3ms^{-1}$.
-This is the resulting motion of the bicycle (See Fig~\ref{fig:bicycle_carrot}), we used a proportional gain $k_{p} = 2$ and look ahead distance $r$ at $2$, $0.2$ and $5$.
+This is the resulting motion of the bicycle (See Fig~\ref{fig:bicycle_carrot}), we used a proportional gain $k_{p} = 2$ and tested look ahead distances $r$ at $2$, $0.2$ and $5$.
 
-From Fig~\ref{fig:bicycle_carrot} we can see that different look ahead distance $r$ impacts the way the robot traces a rectangle.
+From Fig~\ref{fig:bicycle_carrot} we can see that different look ahead distance $r$ greatly impact the way the robot traces a rectangle.
 If the look ahead distance is too low (i.e.
-Fig~\ref{fig:bicycle_carrot_bad} where $r = 0.2$), the carrot will be a very small distance ahead of the robot, making small adjustments unlikely thereby the angle of the steering oscillates between $-30$ degrees to $30$ degrees (the max steering angle).
+Fig~\ref{fig:bicycle_carrot_bad} where $r = 0.2$), the carrot is always very small distance ahead to the robot which in turn causes the angle between the carrot's location and the robot to be relatively large.
+This combined with the course time step of $dt = 0.1s$ cause the robot to overshoot and cross over the desired path line at each time step, causing a large error in the heading which then causes it to overshoot again, leading to the oscillatory motion observed in Fig~\ref{fig:bicycle_carrot_bad}.
+This problem may be avoided if one was to use a PD controller, reduce the P gains or decrease the time step.
 
-If the carrot is at a medium look ahead distance away from the robot  (i.e.
-Fig~\ref{fig:bicycle_carrot_ok} where $r = 2$), the robot tends to be quite agreessive in compensating for overshooting the trajectory.
-As we increase the look ahead distance $r$ however, the correction angle is dampened, causing a less agreessive correction, but longer time to return to the trajectory line.
+When the carrot was set to a look ahead distance of $r = 5m$ we found that robot had trouble hitting a way point and we had to increase the way point reached threshold from $0.2 m $ to $0.5m$ to compensate for this problem.
+The way point reached threshold represented the circle that the robot must enter in order for the carrot controller to consider the way point to have been reached.
+This difficulty of hitting way points, along with larger overshoots compared to the carrot distances were $r= 0.2$ and $r = 2m$ are caused by the large distance between the carrot and the robot which reduces the calculated angle between the robot and the carrot at each time step, making it less sensitive to heading errors and in turn dampening the turning rate of the robot.
+
+Overall we found that a lookahead distance of $r = 2m$ provided the best results for the time steps and proportional gains provided.
+We were able to use a detection radius of 0.2 at each way point to detect if the robot had reached the way point goal.
+Moreover, after passing a way point and slightly overshooting, the robot's trajectory matched the on the next path segment within approximately $5m$ of last way point compared to the runs where $r = 5m$ in which case the robot took over $10m$ to pass directly on the path segments.
 
@@
 \label{sec:igvc_planner}
-We were given a map of the Intelligent Ground Vehicle Competition in the form of a $926 \times 716$ element grid, where each cell
+\textit{Using the map provided with the homework (IGVCmap.mand IGVCmap.jpg), identify a planning strategy that can be used in conjunction with the carrot planner of part 2)to navigate the Intelligent Ground Vehicle Competition auto-navigation course.}
+
+The provided map of the Intelligent Ground Vehicle Competition in the form of a $926 \times 716$ element grid, where each cell
 represents a 10 cm X 10 cm area of the course, resulting in a 92.6 m X 71.6 m environment.
@@
 
-\newpage
 \subsection{Wavefront Planner}
@@
 
-Lastly, for this large map, the run time was over 40 seconds without any collision checking procedures and therefore this approach was abandoned in favour of a Probabilistic Roadmap Planner (PRM).
+Lastly, for this large map, the run time was over 1 minute without any collision checking procedures and therefore this approach was abandoned in favour of a Probabilistic Roadmap Planner (PRM).
 
@@
 \section{Limitations and Future Improvements to the PRM Planner}
-\subsection{Limitations}
 

### 2016-04-03 assignments/assignment_2/report.tex
Update report and refactor ros code

@@
 The first step in implementing the the carrot controller for the outlined problem is to first determine a way to calculate the correct location of the carrot point given the robot's current position.
-To do we can use the projection equation between two vectors.
+To do this we can use the projection equation between two vectors.
 
@@
 Fig~\ref{fig:bicycle_carrot_bad} where $r = 0.2$), the carrot is always very small distance ahead to the robot which in turn causes the angle between the carrot's location and the robot to be relatively large.
-This combined with the course time step of $dt = 0.1s$ cause the robot to overshoot and cross over the desired path line at each time step, causing a large error in the heading which then causes it to overshoot again, leading to the oscillatory motion observed in Fig~\ref{fig:bicycle_carrot_bad}.
-This problem may be avoided if one was to use a PD controller, reduce the P gains or decrease the time step.
+This combined with the coarse time step of $dt = 0.1s$ causes the robot to overshoot and cross over the desired path line at each time step, inducing a large error in the heading which then causes it to overshoot again, leading to the oscillatory motion observed in Fig~\ref{fig:bicycle_carrot_bad}.
+This problem can be avoided if one was to use a PD controller, reduce the P gains or decrease the time step.
 
-When the carrot was set to a look ahead distance of $r = 5m$ we found that robot had trouble hitting a way point and we had to increase the way point reached threshold from $0.2 m $ to $0.5m$ to compensate for this problem.
-The way point reached threshold represented the circle that the robot must enter in order for the carrot controller to consider the way point to have been reached.
+When the carrot was set to a look ahead distance of $r = 5m$ we found that robot had trouble hitting way points and we had to increase the way point reached threshold from $0.2 m $ to $0.5m$ to compensate for this problem.
+The way point reached threshold represents a virtual circle that the robot must enter in order for the carrot controller to consider the way point has been reached.
 This difficulty of hitting way points, along with larger overshoots compared to the carrot distances were $r= 0.2$ and $r = 2m$ are caused by the large distance between the carrot and the robot which reduces the calculated angle between the robot and the carrot at each time step, making it less sensitive to heading errors and in turn dampening the turning rate of the robot.
@@
 Overall we found that a lookahead distance of $r = 2m$ provided the best results for the time steps and proportional gains provided.
-We were able to use a detection radius of 0.2 at each way point to detect if the robot had reached the way point goal.
+We were able to use a detection radius of $0.2m$ at each way point to detect if the robot had reached the way point goal.
 Moreover, after passing a way point and slightly overshooting, the robot's trajectory matched the on the next path segment within approximately $5m$ of last way point compared to the runs where $r = 5m$ in which case the robot took over $10m$ to pass directly on the path segments.
@@
 
-Our goal is to implement a planner and present a combined motion planning solution that finds a straight-line path through the environment, then uses the carrot controller to provide the inputs required to drive the robot to the start and end locations which are ocated at ($x = 4.0m$, $y = 0.5m$, $\theta = 3.14159 rad$) and ($x = 5.0 m$, $y = 1.0 m$, $theta =$ not defined) respectively.
+Our goal is to implement a planner and present a combined motion planning solution that finds a straight-line path through the environment, then uses the carrot controller to provide the inputs required to drive the robot to the start and end locations which are ocated at ($x = 4.0m$, $y = 0.5m$, $\theta = 3.14159 rad$) and ($x = 5.0 m$, $y = 1.0 m$, $\theta =$ not defined) respectively.
 
@@
 This behaviour is due to a lack of particles in locations near choke points.
-An example of the PRM cutting a corner to tightly is highlighted in  Fig~\ref{fig:prm}.
+An example of the PRM cutting a corner too tightly is highlighted in  Fig~\ref{fig:prm}.
 

### 2016-04-03 include/awesomo/ros/camera_node.hpp

@@ -1,0 +1,32 @@
+#ifndef __CAMERA_NODE_HPP__
+#define __CAMERA_NODE_HPP__
+
+#include <cmath>
+
+#include <ros/ros.h>
+#include <std_msgs/Float64.h>
+#include <geometry_msgs/Pose.h>
+#include <geometry_msgs/PoseStamped.h>
+#include <geometry_msgs/PoseWithCovariance.h>
+#include <geometry_msgs/PoseWithCovarianceStamped.h>
+
+#include "awesomo/util.hpp"
+#include "awesomo/camera.hpp"
+#include "awesomo/ros/ros_util.hpp"
+
+
+// DEFINES
+#define ROS_TOPIC "awesomo/apriltag_pose"
+// #define ROS_TOPIC "mavros/vision_pose/pose"
+// #define ROS_TOPIC "mavros/mocap/pose"
+// #define ROS_TOPIC "mavros/vision_pose/pose_cov"
+
+#define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+#define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+#define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+
+// #define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+// #define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+// #define FIREFLY_160 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+
+#endif

### 2016-04-03 include/awesomo/ros/ros_util.hpp

@@ -1,0 +1,41 @@
+#ifndef __ROS_UTIL_HPP__
+#define __ROS_UTIL_HPP__
+
+#include <cmath>
+
+#include <ros/ros.h>
+#include <std_msgs/Float64.h>
+#include <geometry_msgs/Pose.h>
+#include <geometry_msgs/PoseStamped.h>
+#include <geometry_msgs/PoseWithCovariance.h>
+#include <geometry_msgs/PoseWithCovarianceStamped.h>
+
+#include "awesomo/camera.hpp"
+
+
+// FUNCTIONS
+void rotation_matrix(double phi, double theta, double psi, double *rot_mat);
+void single_rotation_matrix(double psi, double *rot_mat);
+void mat3_dot_vec3(double *m, double *v, double *out);
+void fix_coordinate_frames(
+    TagPose &pose,
+	double *rot_mat,
+    double *pos,
+    tf::Quaternion &quat
+);
+void build_pose_stamped_msg(
+    int seq,
+    TagPose &pose,
+	double *rot_mat,
+    geometry_msgs::PoseStamped &pose_msg
+);
+void build_pose_stamped_cov_msg(
+    int seq,
+    TagPose &pose,
+	double *rot_mat,
+    geometry_msgs::PoseWithCovarianceStamped &pose_msg
+);
+void print_pose_stamped_msg(geometry_msgs::PoseStamped &pose_msg);
+void print_pose_cov_stamped_msg(geometry_msgs::PoseWithCovarianceStamped &pose_msg);
+
+#endif

### 2016-04-03 src/apriltag.cpp

@@ -143,6 +143,8 @@ TagPose TagDetector::obtainPose(
     Eigen::Matrix3d F;
     Eigen::Matrix3d rotation;
     Eigen::Matrix3d fixed_rot;
+    Eigen::Matrix4d transform;
+    Eigen::Vector3d translation;
 
     // setup
     F << 1, 0, 0,
@@ -154,21 +156,40 @@ TagPose TagDetector::obtainPose(
         tag_size = 0.048;
     } else if (detection.id == 5) {
         tag_size = 0.343;
+    } else {
+        tag_size = 1;
     }
 
-    // recovering the relative pose of a tag:
-    detection.getRelativeTranslationRotation(
+    transform = detection.getRelativeTransform(
         tag_size,
-        camera_matrix.at<double>(0, 0),
-        camera_matrix.at<double>(1, 1),
-        camera_matrix.at<double>(0, 2),
-        camera_matrix.at<double>(1, 2),
-        pose.translation,
-        rotation
+        camera_matrix.at<double>(0, 0),  // fx
+        camera_matrix.at<double>(1, 1),  // fy
+        camera_matrix.at<double>(0, 2),  // px
+        camera_matrix.at<double>(1, 2)  // py
     );
-    fixed_rot = F * rotation;
-    pose.distance = pose.translation.norm();
-    convertToEuler(fixed_rot, pose.yaw, pose.pitch, pose.roll);
+
+    translation = transform.col(3).head(3);
+    pose.translation[0] = translation[1];
+    pose.translation[1] = translation[2];
+    pose.translation[2] = translation[0];
+    pose.distance = 0;
+    pose.yaw = 0;
+    pose.pitch = 0;
+    pose.roll = 0;
+
+    // recovering the relative pose of a tag:
+    // detection.getRelativeTranslationRotation(
+    //     tag_size,
+    //     camera_matrix.at<double>(0, 0),
+    //     camera_matrix.at<double>(1, 1),
+    //     camera_matrix.at<double>(0, 2),
+    //     camera_matrix.at<double>(1, 2),
+    //     pose.translation,
+    //     rotation
+    // );
+    // fixed_rot = F * rotation;
+    // pose.distance = pose.translation.norm();
+    // convertToEuler(fixed_rot, pose.yaw, pose.pitch, pose.roll);
 
     return pose;
 }

### 2016-04-03 src/quadrotor.cpp

@@ -146,22 +146,22 @@ int quadrotor_update(struct quadrotor *q, double gravity, double dt)
     quadrotor_calculate_angular_acceleration(q);
 
     // update - using euler approximation (todo: need to do rk4 at least)
-    q.angular_velocity_body_frame(0) += q.angular_acceleration_body_frame(0) * dt;
-    q.angular_velocity_body_frame(1) += q.angular_acceleration_body_frame(1) * dt;
-    q.angular_velocity_body_frame(2) += q.angular_acceleration_body_frame(2) * dt;
+    q->angular_velocity_body_frame(0) += q->angular_acceleration_body_frame(0) * dt;
+    q->angular_velocity_body_frame(1) += q->angular_acceleration_body_frame(1) * dt;
+    q->angular_velocity_body_frame(2) += q->angular_acceleration_body_frame(2) * dt;
     quadrotor_convert_angular_velocity_to_inertial_frame(q);
 
-    q.orientation(0) += q.angular_velocity(0) * dt;
-    q.orientation(1) += q.angular_velocity(1) * dt;
-    q.orientation(2) += q.angular_velocity(2) * dt;
+    q->orientation(0) += q->angular_velocity(0) * dt;
+    q->orientation(1) += q->angular_velocity(1) * dt;
+    q->orientation(2) += q->angular_velocity(2) * dt;
 
-    q.velocity(0) += q.acceleration(0) * dt;
-    q.velocity(1) += q.acceleration(1) * dt;
-    q.velocity(2) += q.acceleration(2) * dt;
+    q->velocity(0) += q->acceleration(0) * dt;
+    q->velocity(1) += q->acceleration(1) * dt;
+    q->velocity(2) += q->acceleration(2) * dt;
 
-    q.position(0) += q.velocity(0) * dt;
-    q.position(1) += q.velocity(1) * dt;
-    q.position(2) += q.velocity(2) * dt;
+    q->position(0) += q->velocity(0) * dt;
+    q->position(1) += q->velocity(1) * dt;
+    q->position(2) += q->velocity(2) * dt;
 
     return 0;
 }

### 2016-04-03 src/ros/camera_node.cpp

@@ -1,198 +1,5 @@
-#include <cmath>
+#include "awesomo/ros/camera_node.hpp"
 
-#include <ros/ros.h>
-#include <std_msgs/Float64.h>
-#include <geometry_msgs/Pose.h>
-#include <geometry_msgs/PoseStamped.h>
-#include <geometry_msgs/PoseWithCovariance.h>
-#include <geometry_msgs/PoseWithCovarianceStamped.h>
-
-#include "awesomo/camera.hpp"
-#include "awesomo/util.hpp"
-
-#define ROS_TOPIC "awesomo/apriltag_pose"
-// #define ROS_TOPIC "mavros/vision_pose/pose"
-// #define ROS_TOPIC "mavros/mocap/pose"
-// #define ROS_TOPIC "mavros/vision_pose/pose_cov"
-
-// #define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-// #define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-// #define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
-
-#define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-#define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-#define FIREFLY_160 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_160.yaml"
-
-
-// YPR
-void rotation_matrix(double phi, double theta, double psi, double *rot_mat)
-{
-    //  rotation matrix
-    rot_mat[0] = cos(phi) * cos(theta);
-    rot_mat[1] = sin(phi) * cos(theta);
-    rot_mat[2] = -1 * sin(theta);
-
-    rot_mat[3] = cos(phi) * sin(theta) * sin(psi) - cos(psi) * sin(phi);
-    rot_mat[4] = cos(phi) * cos(psi) + sin(phi) * sin(theta) * sin(psi);
-    rot_mat[5] = cos(theta) * sin(psi);
-
-    rot_mat[6] = sin(phi) * sin(psi) + cos(phi) * cos(psi) * sin(theta);
[…]

### 2016-04-03 src/ros/ros_util.cpp

@@ -1,0 +1,170 @@
+#include "awesomo/ros/ros_util.hpp"
+
+
+// YPR
+void rotation_matrix(double phi, double theta, double psi, double *rot_mat)
+{
+    //  rotation matrix
+    rot_mat[0] = cos(phi) * cos(theta);
+    rot_mat[1] = sin(phi) * cos(theta);
+    rot_mat[2] = -1 * sin(theta);
+
+    rot_mat[3] = cos(phi) * sin(theta) * sin(psi) - cos(psi) * sin(phi);
+    rot_mat[4] = cos(phi) * cos(psi) + sin(phi) * sin(theta) * sin(psi);
+    rot_mat[5] = cos(theta) * sin(psi);
+
+    rot_mat[6] = sin(phi) * sin(psi) + cos(phi) * cos(psi) * sin(theta);
+    rot_mat[7] = cos(psi) * sin(phi) * sin(theta) - cos(phi) * sin(psi);
+    rot_mat[8] = cos(theta) * cos(psi);
+}
+
+void single_rotation_matrix(double psi, double *rot_mat)
+{
+    //  rotation matrix
+    rot_mat[0] = cos(psi);
+    rot_mat[1] = -sin(psi);
+    rot_mat[2] = 0;
+
+    rot_mat[3] = sin(psi);
+    rot_mat[4] = cos(psi);
+    rot_mat[5] = 0;
+
+    rot_mat[6] = 0;
+    rot_mat[7] = 0;
+    rot_mat[8] = 1;
+}
+
+void mat3_dot_vec3(double *m, double *v, double *out)
+{
+    out[0] = m[0] * v[0] + m[3] * v[1] + m[6] * v[2];
+    out[1] = m[1] * v[0] + m[4] * v[1] + m[7] * v[2];
+    out[2] = m[2] * v[0] + m[5] * v[1] + m[8] * v[2];
+}
+
+void fix_coordinate_frames(
+    TagPose &pose,
+	double *rot_mat,
+    double *pos,
+    tf::Quaternion &quat
+)
+{
+    double rot_out[9];
+    single_rotation_matrix(pose.yaw, rot_out);
+	double vec_pos[3];
+
+    // translate from camera frame to ENU
+    // x is times by -1 because april tag was in left-hand
+    // co-ordinate frame commonly used by cameras
+    pos[0] = pose.translation[1];
+    pos[1] = -1 * pose.translation[2];
[…]

### 2016-04-03 tests/ros/ros_util_test.cpp

@@ -1,0 +1,160 @@
+#include "awesomo/munit.h"
+#include "awesomo/ros/ros_util.hpp"
+
+// TESTS
+int test_rotation_matrix(void);
+int test_single_rotation_matrx(void);
+int test_mat3_dot_vec3(void);
+int test_fix_coordinate_frames(void);
+int test_build_pose_stamped_msg(void);
+int test_build_pose_cov_stamped_msg(void);
+int test_print_pose_stamped_msg(void);
+int test_print_pose_cov_stamped_msg(void);
+void test_suite(void);
+
+
+int test_rotation_matrix(void)
+{
+    double rot_mat[9];
+    double phi;
+    double theta;
+    double psi;
+
+    // setup
+    phi = 0.0;
+    theta = 0.0;
+    psi = 0.0;
+
+    // test and assert
+    rotation_matrix(phi, theta, psi, rot_mat);
+    mu_check(fltcmp(rot_mat[0], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[1], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[2], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[3], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[4], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[5], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[6], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[7], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[8], 0.0) == 0);
+
+    return 0;
+}
+
+int test_single_rotation_matrx(void)
+{
+    double rot_mat[9];
+    double phi;
+    double theta;
+    double psi;
+
+    // setup
+    phi = 0.0;
+    theta = 0.0;
+    psi = 0.0;
+
+    // test and assert
+    single_rotation_matrix(psi, rot_mat);
+    mu_check(fltcmp(rot_mat[0], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[1], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[2], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[3], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[4], 0.0) == 0);
+    mu_check(fltcmp(rot_mat[5], 0.0) == 0);
[…]

### 2016-04-04 src/apriltag.cpp
Update camera code

@@ -74,7 +74,7 @@ std::vector<TagPose> TagDetector::processImage(
     cv::Mat masked(image_gray.rows, image_gray.cols, CV_8UC1, cv::Scalar(0));
     cv::rectangle(mask, this->roi_rect, 255, -1);
     image_gray.copyTo(masked, mask);
-    masked.convertTo(masked, -1, 1, -100);
+    // masked.convertTo(masked, -1, 1, -100);
 
     // extract apriltags and estimate pose
     apriltags = this->detector->extractTags(masked);
@@ -97,9 +97,9 @@ std::vector<TagPose> TagDetector::processImage(
     }
 
     // display result
-    // cv::imshow("camera - masked", masked);
+    cv::imshow("camera - masked", masked);
     // cv::imshow("camera - grayscale", masked);
-    // cv::waitKey(1);
+    cv::waitKey(1);
 
     return pose_estimates;
 }
@@ -143,8 +143,6 @@ TagPose TagDetector::obtainPose(
     Eigen::Matrix3d F;
     Eigen::Matrix3d rotation;
     Eigen::Matrix3d fixed_rot;
-    Eigen::Matrix4d transform;
-    Eigen::Vector3d translation;
 
     // setup
     F << 1, 0, 0,
@@ -160,36 +158,44 @@ TagPose TagDetector::obtainPose(
         tag_size = 1;
     }
 
-    transform = detection.getRelativeTransform(
-        tag_size,
-        camera_matrix.at<double>(0, 0),  // fx
-        camera_matrix.at<double>(1, 1),  // fy
-        camera_matrix.at<double>(0, 2),  // px
-        camera_matrix.at<double>(1, 2)  // py
-    );
-
-    translation = transform.col(3).head(3);
-    pose.translation[0] = translation[1];
-    pose.translation[1] = translation[2];
-    pose.translation[2] = translation[0];
-    pose.distance = 0;
-    pose.yaw = 0;
-    pose.pitch = 0;
-    pose.roll = 0;
-
-    // recovering the relative pose of a tag:
-    // detection.getRelativeTranslationRotation(
+    // Eigen::Matrix4d transform;
+    // Eigen::Vector3d translation;
+    // transform = detection.getRelativeTransform(
     //     tag_size,
     //     camera_matrix.at<double>(0, 0),
     //     camera_matrix.at<double>(1, 1),
     //     camera_matrix.at<double>(0, 2),
[…]

### 2016-04-04 src/ros/ros_util.cpp

@@ -48,25 +48,50 @@ void fix_coordinate_frames(
     tf::Quaternion &quat
 )
 {
-    double rot_out[9];
-    single_rotation_matrix(pose.yaw, rot_out);
+	double rot[9];
 	double vec_pos[3];
+	double x_adjusted;
+	double y_adjusted;
 
-    // translate from camera frame to ENU
-    // x is times by -1 because april tag was in left-hand
-    // co-ordinate frame commonly used by cameras
-    pos[0] = pose.translation[1];
-    pos[1] = -1 * pose.translation[2];
-    pos[2] = pose.translation[0];
-    mat3_dot_vec3(rot_out, pos, vec_pos);
-    pos[0] = vec_pos[0];
-    pos[1] = vec_pos[1];
-    pos[2] = vec_pos[2];
-    // ROS_INFO("POSE X HERE IS %f", pose.translation[0]);
-    // ROS_INFO("returned POSE X HERE IS %f", pos[0]);
+    // tag
+	// pos[0] = pose.translation[0];
+	// pos[1] = pose.translation[1];
+	// pos[2] = pose.translation[2];
+
+    // [ENU camera]  [tag (forward, left, up)]
+	pos[0] = -1 * pose.translation[1];
+	pos[1] = pose.translation[2];
+	pos[2] = pose.translation[0];
+
+    // [ENU WORLD] [ENU camera]
+	pos[0] = -pos[0];
+	pos[1] = -pos[1];
+	pos[2] = pos[2];
+
+    // Eigen::AngleAxisd roll_angle(pose.roll, Eigen::Vector3d::UnitZ());
+    // Eigen::AngleAxisd yaw_angle(pose.yaw, Eigen::Vector3d::UnitY());
+    // Eigen::AngleAxisd pitch_angle(pose.pitch, Eigen::Vector3d::UnitX());
+    // Eigen::Quaternion<double> q = roll_angle * yaw_angle * pitch_angle;
+    // Eigen::Matrix3d rotation_matrix = q.matrix();
+    // Eigen::Vector3d pos_vector(pos[0], pos[1], pos[2]);
+    // Eigen::Vector3d position;
+    // position = rotation_matrix * pos_vector;
+    //
+    // pos[0] = position(0);
+    // pos[1] = position(1);
+    // pos[2] = position(2);
+
+	// // adjust according to roll, pitch
[…]

### 2016-04-04 tests/ros/ros_util_test.cpp

@@ -131,6 +131,11 @@ int test_stupid(void)
     Eigen::Matrix4d M;
     Eigen::Matrix4d MT;
 
+    T << 0, 0, 1, 0,
+         -1, 0, 0, 0,
+         0, -1, 0, 0,
+         0, 0, 0, 1;
+
     M << 0, 0, 1, 0,
          -1, 0, 0, 0,
          0, -1, 0, 0,

### 2016-04-04 include/awesomo/controller.hpp
Add controller draft code

@@ -1,0 +1,41 @@
+#ifndef __CONTROLLER_HPP__
+#define __CONTROLLER_HPP__
+
+#include <iostream>
+#include <deque>
+
+#include <Eigen/Dense>
+
+
+class CarrotController
+{
+    public:
+        std::deque<Eigen::Vector3d> waypoints;
+        int initialized;
+        double look_ahead_dist;
+        double wp_threshold;
+        Eigen::Vector3d wp_start;
+        Eigen::Vector3d wp_end;
+
+        CarrotController();
+        CarrotController(double look_ahead_dist, double wp_threshold);
+        Eigen::Vector3d closestPoint(
+            Eigen::Vector3d position,
+            Eigen::Vector3d wp_start,
+            Eigen::Vector3d wp_end
+        );
+        Eigen::Vector3d calculateCarrotPoint(
+            Eigen::Vector3d position,
+            double r,
+            Eigen::Vector3d wp_start,
+            Eigen::Vector3d wp_end
+        );
+        int waypointReached(
+            Eigen::Vector3d position,
+            Eigen::Vector3d waypoint,
+            double threshold
+        );
+        int update(Eigen::Vector3d position, Eigen::Vector3d &carrot);
+};
+
+#endif

### 2016-04-04 src/controller.cpp

@@ -1,0 +1,111 @@
+#include "awesomo/controller.hpp"
+
+
+CarrotController::CarrotController() : initialized(0)
+{
+
+}
+
+CarrotController::CarrotController(double look_ahead_dist, double wp_threshold)
+{
+    this->look_ahead_dist = look_ahead_dist;
+    this->wp_threshold = wp_threshold;
+}
+
+Eigen::Vector3d CarrotController::closestPoint(
+    Eigen::Vector3d position,
+    Eigen::Vector3d wp_start,
+    Eigen::Vector3d wp_end
+)
+{
+    double t;
+    Eigen::Vector3d v1;
+    Eigen::Vector3d v2;
+
+	// calculate closest point
+	v1 = position - wp_start;
+	v2 = wp_end - wp_start;
+	t = v1.dot(v2) / v2.squaredNorm();
+
+    // make sure the point is between wp_start and wp_end
+	if (t < 0) {
+		return wp_start;
+    } else if (t > 1) {
+		return wp_end;
+    }
+
+    // result
+    return wp_start + t * v2;
+}
+
+Eigen::Vector3d CarrotController::calculateCarrotPoint(
+    Eigen::Vector3d position,
+    double r,
+    Eigen::Vector3d wp_start,
+    Eigen::Vector3d wp_end
+)
+{
+    Eigen::Vector3d u;
+    Eigen::Vector3d v;
+    Eigen::Vector3d pt_on_line;
+
+    // get closest point
+    pt_on_line = this->closestPoint(position, wp_start, wp_end);
+
+    // calculate carrot point on wp_start and wp_end
+    v = wp_end - wp_start;
+    u = v / v.norm();
+    return pt_on_line + r * u;
+}
+
+int CarrotController::waypointReached(
+    Eigen::Vector3d position,
+    Eigen::Vector3d waypoint,
+    double threshold
+)
+{
+    double dist;
+    Eigen::Vector3d x;
+
+    // calculate distance to waypoint
+    x = waypoint - position;
+    dist = x.norm();
+
+    // waypoint reached?
+    if (dist > threshold) {
+        return 0;
+    } else {
+        return 1;
+    }
+}
+
+int CarrotController::update(Eigen::Vector3d position, Eigen::Vector3d &carrot)
+{
+    int nb_waypoints;
+
+    // pre-check
+    if (this->initialized == 0) {
+        return -1;
+    }
+
+    // waypoint reached? get new wp_start and wp_end
+    if (this->waypointReached(position, wp_end, 1)) {
[…]

### 2016-04-04 src/util.cpp

@@ -1,9 +1,9 @@
 #include "awesomo/util.hpp"
 
-int euler2Quaternion( const double roll,
-                  const double pitch,
-                  const double yaw,
-                  Eigen::Quaterniond &q)
+int euler2Quaternion(const double roll,
+                     const double pitch,
+                     const double yaw,
+                     Eigen::Quaterniond &q)
 {
     Eigen::AngleAxisd rollAngle(roll, Eigen::Vector3d::UnitX());
     Eigen::AngleAxisd pitchAngle(pitch, Eigen::Vector3d::UnitY());
@@ -14,17 +14,16 @@ int euler2Quaternion( const double roll,
     return 0;
 }
 
-int euler2RotationMatrix( const double roll,
-                        const double pitch,
-                        const double yaw,
-                        Eigen::Matrix3d &rot)
+int euler2RotationMatrix(const double roll,
+                         const double pitch,
+                         const double yaw,
+                         Eigen::Matrix3d &rot)
 {
     Eigen::Quaterniond q_normalized;
     euler2Quaternion(roll, pitch, yaw, q_normalized);
     rot = q_normalized.toRotationMatrix();
     return 0;
 }
-
 
 double deg2rad(double d)
 {

### 2016-04-04 tests/util_test.cpp

@@ -156,17 +156,17 @@ int test_euler2RotationMatrix(void)
     r22 = 0;
     r23 = -1;
 
-    mu_check(fltcmp(r01,rot(0,0)) == 0);
-    mu_check(fltcmp(r02,rot(0,1)) == 0);
-    mu_check(fltcmp(r03,rot(0,2)) == 0);
+    mu_check(fltcmp(r01, rot(0, 0)) == 0);
+    mu_check(fltcmp(r02, rot(0, 1)) == 0);
+    mu_check(fltcmp(r03, rot(0, 2)) == 0);
 
-    mu_check(fltcmp(r11,rot(1,0)) == 0);
-    mu_check(fltcmp(r12,rot(1,1)) == 0);
-    mu_check(fltcmp(r13,rot(1,2)) == 0);
+    mu_check(fltcmp(r11, rot(1, 0)) == 0);
+    mu_check(fltcmp(r12, rot(1, 1)) == 0);
+    mu_check(fltcmp(r13, rot(1, 2)) == 0);
 
-    mu_check(fltcmp(r21,rot(2,0)) == 0);
-    mu_check(fltcmp(r22,rot(2,1)) == 0);
-    mu_check(fltcmp(r23,rot(2,2)) == 0);
+    mu_check(fltcmp(r21, rot(2, 0)) == 0);
+    mu_check(fltcmp(r22, rot(2, 1)) == 0);
+    mu_check(fltcmp(r23, rot(2, 2)) == 0);
 
     roll = M_PI;
     pitch = M_PI/2;
@@ -184,17 +184,17 @@ int test_euler2RotationMatrix(void)
     r22 = 0;
     r23 = 0;
 
-    mu_check(fltcmp(r01,rot(0,0)) == 0);
-    mu_check(fltcmp(r02,rot(0,1)) == 0);
-    mu_check(fltcmp(r03,rot(0,2)) == 0);
+    mu_check(fltcmp(r01, rot(0, 0)) == 0);
+    mu_check(fltcmp(r02, rot(0, 1)) == 0);
+    mu_check(fltcmp(r03, rot(0, 2)) == 0);
 
-    mu_check(fltcmp(r11,rot(1,0)) == 0);
-    mu_check(fltcmp(r12,rot(1,1)) == 0);
-    mu_check(fltcmp(r13,rot(1,2)) == 0);
+    mu_check(fltcmp(r11, rot(1, 0)) == 0);
[…]

### 2016-04-05 assignments/presentation/presentation.tex
Update carrot controller and start presentation deck

\documentclass{beamer}
\begin{document}
  \begin{frame}
    \frametitle{This is the first slide}
    %Content goes here
  \end{frame}
  \begin{frame}
    \frametitle{This is the second slide}
    \framesubtitle{A bit more information about this}
    %More content goes here
  \end{frame}
% etc
\end{document}

### 2016-04-05 include/awesomo/controller.hpp

@@ -18,7 +18,11 @@ class CarrotController
         Eigen::Vector3d wp_end;
 
         CarrotController();
-        CarrotController(double look_ahead_dist, double wp_threshold);
+        CarrotController(
+            std::deque<Eigen::Vector3d> waypoints,
+            double look_ahead_dist,
+            double wp_threshold
+        );
         Eigen::Vector3d closestPoint(
             Eigen::Vector3d position,
             Eigen::Vector3d wp_start,

### 2016-04-05 include/awesomo/munit.h

@@ -2,6 +2,7 @@
 #define __MUNIT_H__
 
 #include <iostream>
+#include <fstream>
 #include <cmath>
 #include <stdio.h>
 

### 2016-04-05 src/controller.cpp

@@ -1,13 +1,16 @@
 #include "awesomo/controller.hpp"
 
 
-CarrotController::CarrotController() : initialized(0)
-{
+CarrotController::CarrotController() : initialized(0) { }
 
-}
-
-CarrotController::CarrotController(double look_ahead_dist, double wp_threshold)
+CarrotController::CarrotController(
+    std::deque<Eigen::Vector3d> waypoints,
+    double look_ahead_dist,
+    double wp_threshold
+)
 {
+    this->initialized = 1;
+    this->waypoints = waypoints;
     this->look_ahead_dist = look_ahead_dist;
     this->wp_threshold = wp_threshold;
 }
@@ -85,7 +88,7 @@ int CarrotController::update(Eigen::Vector3d position, Eigen::Vector3d &carrot)
 
     // pre-check
     if (this->initialized == 0) {
-        return -1;
+        return -2;
     }
 
     // waypoint reached? get new wp_start and wp_end
@@ -95,7 +98,7 @@ int CarrotController::update(Eigen::Vector3d position, Eigen::Vector3d &carrot)
             this->wp_start = this->waypoints.at(0);
             this->wp_end = this->waypoints.at(1);
         } else {
-            return -1;
+            return 0;
         }
     }
 
@@ -107,5 +110,5 @@ int CarrotController::update(Eigen::Vector3d position, Eigen::Vector3d &carrot)
         this->wp_end
     );
 
-    return 0;
+    return 1;
 }

### 2016-04-05 tests/controller_test.cpp

@@ -102,15 +102,50 @@ int testUpdate(void)
     // setup
     position << 2, 2, 0;
     wp << 0, 0, 0;
+    controller.wp_start = wp;
     controller.waypoints.push_back(wp);
     wp << 10, 10, 0;
+    controller.wp_end = wp;
     controller.waypoints.push_back(wp);
+    wp << 15, 10, 0;
+    controller.waypoints.push_back(wp);
+    controller.look_ahead_dist = 1;
+    controller.wp_threshold = 0.1;
+    controller.initialized = 1;
 
     // test and assert
-    retval = controller.update(position, carrot);
+    std::ofstream outfile;
+    outfile.open("update.dat");
 
-    std::cout << retval << std::endl;
-    std::cout << carrot << std::endl;
+    for (int i = 0; i < 40; i++) {
+        // carrot update
+        retval = controller.update(position, carrot);
+        mu_check(retval == 1);
+
+        // record
+        outfile << controller.wp_start(0) << ", ";
+        outfile << controller.wp_start(1) << ", ";
+        outfile << controller.wp_start(2) << std::endl;
+
+        outfile << controller.wp_end(0) << ", ";
+        outfile << controller.wp_end(1) << ", ";
+        outfile << controller.wp_end(2) << std::endl;
+
+        outfile << position(0) << ", ";
+        outfile << position(1) << ", ";
+        outfile << position(2) << std::endl;
+
+        outfile << carrot(0) << ", ";
+        outfile << carrot(1) << ", ";
+        outfile << carrot(2) << std::endl;
+        outfile << std::endl;
+
+        // update position
+        position(0) = position(0) + 0.5;
+        position(1) = position(1) + 0.5;
+    }
+
+    outfile.close();
 }
 
 void testSuite(void)

### 2016-04-05 include/awesomo/ros/camera_node.hpp
Add draft mission for quadrotor node

@@ -21,12 +21,4 @@
 // #define ROS_TOPIC "mavros/mocap/pose"
 // #define ROS_TOPIC "mavros/vision_pose/pose_cov"
 
-#define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-#define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-#define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
-
-// #define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-// #define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-// #define FIREFLY_160 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_160.yaml"
-
 #endif

### 2016-04-05 assignments/presentation/presentation.tex
Add warsaw theme to presentation
adding image caputure code

@@
 \documentclass{beamer}
+
+\usepackage{media9}
+\usetheme{Warsaw}
+
 \begin{document}
+\title{Quadrotor landing on a moving platform}
+\subtitle{}
+\author[]{Stan Brown \and Chris Choi}
+
+\frame{\titlepage}
+
   \begin{frame}
-    \frametitle{This is the first slide}
-    %Content goes here
+    \frametitle{Introduction}
+     \textbf{Presentation Outline}
+     \begin{itemize}     
+        \item Project Overview and Goals       
+        \item Hardware used in the project
+        \item System overview
+        \item Approaches used to simplify the problem
+        \item Milestones and Progress through the term       
+    \end{itemize}
   \end{frame}
+
    \begin{frame}
-    \frametitle{This is the second slide}
-    \framesubtitle{A bit more information about this}
-    %More content goes here
+    \frametitle{Project Overview and Goals}
+     The goal of this work was to design and implement a set of methods that could be used 			to land a quadrotor on a moving platform.
+In our approach we broke the problem down 		in to a series of steps and goals along with the requirements for each step.
+     \begin{itemize}     
+        \item Develop a way to land on a stationary location on the ground
+        \item Expand the methods employed in the first step to work on a moving platform 						operating in a planar, disturbance free environment
+        \item Further expand the methods to be able to account for wind, non planar motion 					of the platform (ie identify and handle cases were the landing pad is 						located on a sloped surface).
+    \end{itemize}     
 \end{frame}
+
+ \begin{frame}
+    \frametitle{Hardware}
+     The hardware used in this project was selected from a set of parts that we had laying 			around the WAVELAB. 
+     \begin{itemize}    
+        \item Develop a way to land on a stationary location on the ground
+        \item Expand the methods employed in the first step to work on a moving platform 						operating in a planar, disturbance free environment
+        \item Further expand the methods to be able to account for wind, non planar motion 					of the platform (ie identify and handle cases were the landing pad is 						located on a sloped surface).
+    \end{itemize}     
+\end{frame}
+
 % etc

### 2016-04-05 include/awesomo/camera.hpp

@@ -67,6 +67,7 @@ class Camera
         int loadConfig(std::string camera_mode);
         int run(void);
         int getFrame(cv::Mat &image);
+        int photoMode(void);
         std::vector<TagPose> step(int &timeout);
 };
 

### 2016-04-05 include/awesomo/ros/camera_node.hpp

@@ -21,9 +21,13 @@
 // #define ROS_TOPIC "mavros/mocap/pose"
 // #define ROS_TOPIC "mavros/vision_pose/pose_cov"
 
-#define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-#define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-#define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+// #define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+// #define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+// #define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+
+#define FIREFLY_640 "/home/stan/Projects/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+#define FIREFLY_320 "/home/stan/Projects/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+#define FIREFLY_160 "/home/stan/Projects/awesomo/configs/pointgrey_firefly/ost_160.yaml"
 
 // #define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
 // #define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"

### 2016-04-05 src/camera.cpp

@@ -330,6 +330,7 @@ int Camera::run(void)
             timeout
         );
         this->adjustMode(pose_estimates, timeout);
+
         // this->printFPS(last_tic, frame_index);
         // cv::imshow("camera", image);
         // cv::waitKey(1);
@@ -343,7 +344,9 @@ std::vector<TagPose> Camera::step(int &timeout)
     cv::Mat image;
     std::vector<TagPose> pose_estimates;
 
+
     this->getFrame(image);
+
     pose_estimates = this->tag_detector->processImage(
         this->config->camera_matrix,
         image,
@@ -351,4 +354,48 @@ std::vector<TagPose> Camera::step(int &timeout)
     );
     this->adjustMode(pose_estimates, timeout);
     return pose_estimates;
+}
+
+
+int Camera::photoMode(void)
+{
+    int frame_index;
+    int timeout;
+    double last_tic;
+    cv::Mat image;
+    std::vector<TagPose> pose_estimates;
+
+    int key_input;
+    cv::Mat image_cap;
+    int image_number;
+
+    // setup
+    timeout = 0;
+    frame_index = 0;
+    last_tic = tic();
+
+    image_number = 1;
+
+    // read capture device
+    while (true) {
+        this->getFrame(image);
+        pose_estimates = this->tag_detector->processImage(
+            this->config->camera_matrix,
+            image,
+            timeout
+        );
+        this->adjustMode(pose_estimates, timeout);
+
+        // cv::imshow("camera", image);
+        // cv::waitKey(1);
+
+        key_input = cvWaitKey(100);
+        if((char) key_input == 49){
+            std::cout << "Saving a new image" << std::endl;
+            image.copyTo(image_cap);
+            imshow("image capture", image_cap);
+        }
+    }
+
+    return 0;
 }

### 2016-04-05 include/awesomo/ros/quadrotor_node.hpp
Quadrotor Update

@@ -65,8 +65,9 @@ class Quadrotor
         ros::ServiceClient arming_client;
 
         Camera *cam;
-        std::vector<TagPose> tag_poses;
         int tag_timeout;
+        std::vector<TagPose> tag_poses;
+        Eigen::Vector3d tag_position;
 
         void poseCallback(const geometry_msgs::PoseStamped &msg);
         void subscribeToPose(void);

### 2016-04-05 src/ros/quadrotor_node.cpp

@@ -224,14 +224,30 @@ void Quadrotor::runMission(geometry_msgs::PoseStamped &pose)
         pose_estimates = cam->step(this->tag_timeout);
         tag_poses.push_back(pose_estimates.at(0));
 
+        // average estimates
         if (tag_poses.size() == 10) {
+            double x = 0;
+            double y = 0;
+            double z = 0;
+
+            for (int i; i < tag_poses.size(); i++) {
+                x += tag_poses[i].translation(0);
+                y += tag_poses[i].translation(1);
+                z += tag_poses[i].translation(2);
+            }
+            this->tag_position << (x / 10.0), (y / 10.0), (z / 10.0);
+
             ROS_INFO("Collected enough tag estimations!");
+            ROS_INFO("Tag is at (%f, %f, %f)", (x / 10.0), (y / 10.0), (z / 10.0));
             ROS_INFO("Transitioning to carrot mode!");
+            this->mission_state = PLANNING_MODE;
         }
 
         break;
 
     case PLANNING_MODE:
+
+
         break;
 
     case CARROT_MODE:
@@ -259,18 +275,15 @@ int main(int argc, char **argv)
 	int count = 1;
 	int index = 0;
 
-
-
-
     while (ros::ok()){
         pose.header.stamp = ros::Time::now();
         pose.header.seq = count;
-        pose.header.frame_id = 1;
+        pose.header.frame_id = "awesomo_quad_offboard";
         // ROS_INFO("x: 0.0\ty: 0.0\tz: 1.0");
-		pose.pose.position.z = 1.0;
-        pose.pose.position.x = 0.0;
-        pose.pose.position.y = 0.0;
-		count++;
+		// pose.pose.position.z = 1.0;
+        // pose.pose.position.x = 0.0;
+        // pose.pose.position.y = 0.0;
+        quad.runMission(pose);
 
 		// if (ros::Time::now() - last_request > ros::Duration(10.0)) {
         //     if (index == 0) {
@@ -301,6 +314,10 @@ int main(int argc, char **argv)
 		// publish
 		quad.position_publisher.publish(pose);
 
+		// update
+		count++;
+
+		// end
 		ros::spinOnce();
 		rate.sleep();
     }

### 2016-04-05 include/awesomo/ros/quadrotor_node.hpp
Add planner and carrot controller for quad node

@@ -21,6 +21,7 @@
 
 #include "awesomo/util.hpp"
 #include "awesomo/camera.hpp"
+#include "awesomo/controller.hpp"
 
 
 // CONSTANTS
@@ -68,6 +69,8 @@ class Quadrotor
         int tag_timeout;
         std::vector<TagPose> tag_poses;
         Eigen::Vector3d tag_position;
+
+        CarrotController *controller;
 
         void poseCallback(const geometry_msgs::PoseStamped &msg);
         void subscribeToPose(void);

### 2016-04-05 src/controller.cpp

@@ -9,7 +9,9 @@ CarrotController::CarrotController(
     double wp_threshold
 )
 {
-    this->initialized = 1;
+    if (waypoints.size() > 0) {
+        this->initialized = 1;
+    }
     this->waypoints = waypoints;
     this->look_ahead_dist = look_ahead_dist;
     this->wp_threshold = wp_threshold;

### 2016-04-05 src/ros/quadrotor_node.cpp

@@ -38,7 +38,19 @@ Quadrotor::Quadrotor(void)
     cam->loadConfig("320", FIREFLY_320);
     cam->loadConfig("160", FIREFLY_160);
     cam->initCamera("320");
+
+    // intialize controller
+    double look_ahead_dist = 0.5;
+    double wp_threshold = 0.1;
+    std::deque<Eigen::Vector3d> waypoints;
+
+    this->controller = new CarrotController(
+        waypoints,
+        look_ahead_dist,
+        wp_threshold
+    );
 }
+
 
 void Quadrotor::poseCallback(const geometry_msgs::PoseStamped &msg)
 {
@@ -196,7 +208,9 @@ void Quadrotor::runMission(geometry_msgs::PoseStamped &pose)
 {
     double dist;
     Eigen::Vector3d pos;
+    Eigen::Vector3d wp;
     Eigen::Vector3d dest;
+    Eigen::Vector3d carrot;
 	std::vector<TagPose> pose_estimates;
 
     switch (this->mission_state) {
@@ -239,18 +253,68 @@ void Quadrotor::runMission(geometry_msgs::PoseStamped &pose)
 
             ROS_INFO("Collected enough tag estimations!");
             ROS_INFO("Tag is at (%f, %f, %f)", (x / 10.0), (y / 10.0), (z / 10.0));
-            ROS_INFO("Transitioning to carrot mode!");
+            ROS_INFO("Transitioning to planning mode!");
             this->mission_state = PLANNING_MODE;
         }
 
         break;
 
     case PLANNING_MODE:
+        if (this->controller->initialized == 0) {
+            // tag position
+            this->controller->waypoints.push_back(this->tag_position);
+            ROS_INFO(
+                "WAYPOINT 3 [Tag Position]: (%f, %f, %f)",
+                this->tag_position(0),
+                this->tag_position(1),
+                this->tag_position(2)
+            );
 
+            // above tag position
+            wp << this->tag_position(0), this->tag_position(1), 1.2;
+            this->controller->waypoints.push_back(wp);
+            ROS_INFO(
+                "WAYPOINT 2 [Above Tag]: (%f, %f, %f)",
+                wp(0),
+                wp(1),
+                wp(2)
+            );
+
+            // quad position
+            pos << this->pose_x, this->pose_y, this->pose_z;
+            this->controller->waypoints.push_back(pos);
+            ROS_INFO(
+                "WAYPOINT 1 [Quad Position]: (%f, %f, %f)",
+                pos(0),
[…]

### 2016-04-05 assignments/presentation/presentation.tex
presentation updated

--- 2016-04-05 assignments/presentation/presentation.tex
@@
 \documentclass{beamer}
+
+\usepackage{media9}
+\usetheme{Warsaw}
+
 \begin{document}
+\title{Quadrotor landing on a moving platform}
+\subtitle{but not really... (yet)}
+\author[]{Stan Brown \and Chris Choi}
+
+\frame{\titlepage}
    \begin{frame}
-    \frametitle{This is the first slide}
-    %Content goes here
+    \frametitle{Project Overview and Goals}
+     The goal of this work was to enable a quadrotor to autonomously land on a moving platform. In our approach we broke the problem down.
+     \begin{enumerate}
+        \item Develop a way to land on a stationary target
+        \item Expand these methods to work with a slow moving platform operating in a wind free environment
+        \item Further expand the methods to be able to account for wind
+    \end{enumerate}     
+\end{frame}
+
+ \begin{frame}
+    \frametitle{Hardware}
+     The hardware used in this project was selected from an assortment of parts that we had laying around the WAVELAB. 
+     \begin{itemize}    
+        \item Quadrotor
+        	\begin{itemize}
+        		\item Frame: DJI Flamewheel F450
+        		\item Motors: Emax 912 KV motors
+        		\item Flight Controller: Pixhawk running the PX4 flight stack
+        		\item Computer: Odroid XU4 (Snapdragon 8 core processor)
+        	\end{itemize}
+
+        	\item Additional Sensors
+        	\begin{itemize}
+        		\item Camera: PointGrey Firefly 2.0 Camera (60 FPS at 640 x 480p)
+        		\item Lens: 135 degree FOV
+        	\end{itemize}
+    \end{itemize}     
+\end{frame}
+
+\begin{frame}
+    \frametitle{Anastasia}
+    \includegraphics[width=\linewidth]{images/quad.jpg}
+\end{frame}
+
+\begin{frame}
+    \frametitle{Pixhawk}
+    \begin{center}
+    \includegraphics[width=0.25\linewidth]{images/pixhawk_crappy_thing.jpg}
+    \end{center}
+
+    All in one flight controller that controls all them motors and maintains stability.
+    	\begin{itemize}
+        		\item Produced by 3DR robotics at a cost of 200 USD
+        		\item Runs the PX4 and APM flight stacks (both open source)
+        		\item Direct communication to the odroid via a package called mavros
+        	\end{itemize}    
+\end{frame}
+
+\begin{frame}
+	\frametitle{Progress throughout the term}
+	Needless to say out goal for a term project was... \textit{ambitious}. Issues include:
+	\begin{itemize}
+        		\item Difficulties getting the Odroid to talk to the Pixhawk
+        		\item Issues with finding and understanding the PX4 and mavros documentation 
+        		\item Several parameters in QGroundcontrol that had to be set to make the quad work as expected
+    \end{itemize}
+
+    \textbf{But enough with the whining...}
+
+\end{frame}
+
+\begin{frame}
+	\frametitle{Solving the Pose Estimation Problem}
+	We used the MIT AprilTags Library for pose estimation:
+	\begin{itemize}
+	\item Uses a special type of 2D marker
+	\item Processing entire images resulted in very slow pose estimates (3 - 5 Hz) on the Odroid. Down sampling increased frame rate but reduced the range to 1.5 meters.	
+	\item  Varied down sampling size dynamically depending on the distance between the quad and the AprilTag
+	\item AprilTag Inception (Tag within a tag to solve FOV problems)
+	\item Black out image other than ROI
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+	\frametitle{Proposed Method to solve the landing problem}
+	 Our proposed method breaks down the landing problem into three separate parts:
+	\begin{enumerate}
+	\item \textbf{Detect} April Tag and get initial pose
+	\item \textbf{Align} the font of the quad with the current location of the landing zone.
+	\item \textbf{Move} towards the landing zone by pitching towards the landing zone
+	\item \textbf{Descend} once the quad is located over the landing zone with PID controller
+	\end{enumerate}
+
+	We call this the \textbf{DAMD} approach
+
 \end{frame}
 \begin{frame}
-    \frametitle{This is the second slide}
-    \framesubtitle{A bit more information about this}
-    %More content goes here
+\title{Testing out method}
+The WAVELab has a motion capture system (MOCAP) that we used to test our code that we ran on the Odroid.
+Some of the results are shown in the following videos that show the quad moving tracing a square and then from last night, landing on the AprilTags \\
+
+\href{https://www.youtube.com/watch?v=9oUxANr1j0o}{Partial Success} \\
+and of course a few fails along the way \\
+\href{https://youtu.be/2i0S6vrP9oc?t=53}{fails}
+
 \end{frame}
+
+\begin{frame}
+And here are some of the not so great moments we have had
+\begin{itemize}
+\item Early attempts at getting the quad to just take off: 
+	\begin{itemize}
+		\item \hyperlink{https://youtu.be/a6_0YQt9BuM?t=29}{\beamergotobutton{test}} \\
+		\item \hyperlink{https://youtu.be/9zpM9thEneg?t=10}{\beamergotobutton{}} \\
+		\item \hyperlink{https://youtu.be/5U7R6-7MHrY?t=137}{\beamergotobutton{}}
+	\end{itemize}
+\item MOCAP dropping out and causing the quad to crash:
+		\item \hyperlink{https://youtu.be/ZHCqoEdYbX0?t=30}{\beamergotobutton{crash}}
+
+\item And here is how we tested to see if our commands made sense:
+\href{https://youtu.be/0EvrlYkYMyY?t=175}{command checking}
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Conclusion}
+We have put a lot of hours into the project but greatly underestimated the time required to actually implement even the simple ideas that we came up for this project. \\
+
+\textit{However} we did get the quad to land (sort of). And so...
+\end{frame}
+
+  \begin{frame}
+    \frametitle{In summary..}
+    \includegraphics[width=\linewidth]{images/mission_accomplished.jpg}
+\end{frame}
+
 % etc

### 2016-04-05 assignments/presentation/presentation.tex
fixed hyperlinks

@@
 
-\href{https://www.youtube.com/watch?v=9oUxANr1j0o}{Partial Success} \\
+\href{https://www.youtube.com/watch?v=9oUxANr1j0o}{\beamergotobutton{Partial Success}} \\
 and of course a few fails along the way \\
-\href{https://youtu.be/2i0S6vrP9oc?t=53}{fails}
+\href{https://youtu.be/2i0S6vrP9oc?t=53}{\beamergotobutton{Not quite there yet}}
 
@@
 	\begin{itemize}
-		\item \hyperlink{https://youtu.be/a6_0YQt9BuM?t=29}{\beamergotobutton{test}} \\
-		\item \hyperlink{https://youtu.be/9zpM9thEneg?t=10}{\beamergotobutton{}} \\
-		\item \hyperlink{https://youtu.be/5U7R6-7MHrY?t=137}{\beamergotobutton{}}
+		\item \href{https://youtu.be/a6_0YQt9BuM?t=29}{\beamergotobutton{2nd test flight}} \\
+		\item \href{https://youtu.be/9zpM9thEneg?t=10}{\beamergotobutton{4th test flight}} \\
+		\item \href{https://youtu.be/5U7R6-7MHrY?t=137}{\beamergotobutton{9th test flight}}
 	\end{itemize}
 \item MOCAP dropping out and causing the quad to crash:
-		\item \hyperlink{https://youtu.be/ZHCqoEdYbX0?t=30}{\beamergotobutton{crash}}
+		\item \href{https://youtu.be/ZHCqoEdYbX0?t=30}{\beamergotobutton{crash}}
 
 \item And here is how we tested to see if our commands made sense:
-\href{https://youtu.be/0EvrlYkYMyY?t=175}{command checking}
+\href{https://youtu.be/0EvrlYkYMyY?t=175}{\beamergotobutton{checking Odroid command inputs}}
 

### 2016-04-17 include/awesomo/pid.hpp
Add draft xy position controller

@@ -7,6 +7,8 @@
 #include <stdlib.h>
 #include <sys/timeb.h>
 
+#include <ros/ros.h>
+
 
 // STRUCTURES
 struct pid_config
@@ -47,7 +49,7 @@ struct pid
 // FUNCTIONS
 struct pid *pid_setup(struct pid_config *c);
 void pid_destroy(void *target);
-int pid_calculate(struct pid *p, float actual);
+int pid_calculate(struct pid *p, float input, ros::Duration dt);
 
 
 #endif

### 2016-04-17 include/awesomo/ros/quadrotor_node.hpp

@@ -22,6 +22,7 @@
 #include "awesomo/util.hpp"
 #include "awesomo/camera.hpp"
 #include "awesomo/controller.hpp"
+#include "awesomo/pid.hpp"
 
 
 // CONSTANTS
@@ -112,6 +113,12 @@ class Quadrotor
         int disarm(void);
         int setOffboardModeOn(void);
         void runMission(geometry_msgs::PoseStamped &pose);
+        void runMission2(geometry_msgs::PoseStamped &pose);
+        void traceSquare(
+            geometry_msgs::PoseStamped &pose,
+            int *index,
+            ros::Time &last_request
+        );
 };
 
 #endif

### 2016-04-17 src/pid.cpp

@@ -36,44 +36,30 @@ void pid_destroy(void *target)
     p = NULL;
 }
 
-int pid_calculate(struct pid *p, float input)
+int pid_calculate(struct pid *p, float input, ros::Duration dt)
 {
-    int dt;
     float error;
-    struct timeb now;
 
-    // calculate dt - in miliseconds
-    ftime(&now);
-    dt = (float) (
-        1000.0 *
-        (now.time - p->last_updated.time) +
-        (now.millitm - p->last_updated.millitm)
-    );
+    // calculate errors
+    error = p->setpoint - input;
+    if (fabs(error) > p->dead_zone) {
+        p->sum_error += error * dt.toSec();
+    }
 
     // calculate output
-    if (dt >= p->sample_rate) {
-        // calculate errors
-        error = p->setpoint - input;
-        if (fabs(error) > p->dead_zone) {
-            p->sum_error += error * (float) (dt / 1000.0);
-        }
+    p->output = (p->k_p * error);
+    p->output += (p->k_i * p->sum_error);
+    p->output += (p->k_d * (input - p->prev_error));
 
-        // calculate output
-        p->output = (p->k_p * error);
-        p->output += (p->k_i * p->sum_error);
-        p->output -= (p->k_d * (input - p->prev_error));
-
-        // limit boundaries
-        if (p->output > p->max) {
-            p->output = p->max;
-        } else if (p->output < p->min) {
-            p->output = p->min;
-        }
-
-        // update error and last_updated
-        p->prev_error = error;
-        ftime(&p->last_updated);
+    // limit boundaries
+    if (p->output > p->max) {
+        p->output = p->max;
+    } else if (p->output < p->min) {
+        p->output = p->min;
     }
+
+    // update error
+    p->prev_error = error;
 
     return 0;
 }

### 2016-04-17 src/ros/quadrotor_node.cpp

@@ -27,10 +27,9 @@ Quadrotor::Quadrotor(void)
     this->arming_client = this->node.serviceClient<mavros_msgs::CommandBool>(ARM_TOPIC);
 
     // initialize publishers
-    this->position_publisher = this->node.advertise<geometry_msgs::PoseStamped>(POSITION_TOPIC, 50);
-    // this->attitude_publisher = this->node.advertise<geometry_msgs::PoseStamped>(ATTITUDE_TOPIC, 50);
-    // this->throttle_publisher = this->node.advertise<std_msgs::Float64>(THROTTLE_TOPIC, 50);
-    //
+    this->position_publisher = this->node.advertise<geometry_msgs::PoseStamped>(POSITION_TOPIC, 100);
+    this->attitude_publisher = this->node.advertise<geometry_msgs::PoseStamped>(ATTITUDE_TOPIC, 100);
+    this->throttle_publisher = this->node.advertise<std_msgs::Float64>(THROTTLE_TOPIC, 100);
 
     // state
     this->mission_state = HOVER_MODE;
@@ -365,9 +364,9 @@ void Quadrotor::runMission(geometry_msgs::PoseStamped &pose)
             );
         } else {
             // set hover coordinates
-            pose.pose.position.z = 0;
             pose.pose.position.x = 0;
             pose.pose.position.y = 0;
+            pose.pose.position.z = 0;
 
             ROS_INFO("Final Waypoint reached");
             ROS_INFO("MISSION ACCOMPLISHED!");
@@ -377,16 +376,53 @@ void Quadrotor::runMission(geometry_msgs::PoseStamped &pose)
     }
 }
 
+void Quadrotor::traceSquare(
+    geometry_msgs::PoseStamped &pose,
+    int *index,
+    ros::Time &last_request
+)
+{
+    if ((ros::Time::now() - last_request) > ros::Duration(10.0)) {
+        if (*index == 0) {
+            pose.pose.position.x = 0.5;
+            pose.pose.position.y = 0.5;
+            *index++;
+            ROS_INFO("x: 0.5\ty: 0.5");
+        } else if (*index == 1) {
+            pose.pose.position.x = 0.5;
+            pose.pose.position.y = -0.5;
+            ROS_INFO("x: 0.5\ty: -0.5");
+            *index++;
+        } else if (*index == 2) {
+            pose.pose.position.x = -0.5;
+            pose.pose.position.y = -0.5;
+            ROS_INFO("x: -0.5\ty: -0.5");
+            *index++;
[…]

### 2016-04-17 docs/report/report.tex
Update camera code
added camera methods section

@@
 
-%COMMENTING
+% COMMENTING
 \usepackage{comment}
+
+% MATH FONTS
+\usepackage{amsmath}
 
@@
 \section{Introduction}
-Autonomous 	precision landing of a quadrotor onto moving platform has been explored by a number of researchers \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}, and there exists a wide range of approaches to the problem.
+
+The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference).
+However most of these methods usually assume that the landing zone is static and that there is very little wind or disturbances.
+In cases of high wind or a rapidly moving platform, which from the quadrotor's reference frame can be be though of as nearly equivalent cases, normal autonomous landing procedures will likely fail.
+
+Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}.
+The problem has been explored from a fairly wide range of approaches.
+
 Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform and more.
 
-The major challenge with autnomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts include lighting, and color.
+The major challenge with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
 
 \section{Related Work}
-The challenging of autonoums landing can be categorized into three distinct parts.
-First, it must sense or detect the landing target to obtain positional estimates relative to the quadrotor.
+The challenging of autonomous landing can be categorized into three distinct parts.
+First, the quadrotor must sense or detect the landing target to obtain positional estimates relative to the quadrotor.
 Secondly, the quadrotor must plan its rendezvous trajectory with the landing target.
 Third and finally, the quadrotor must apply a set of controller commands to approach the platform, matching both speed and heading on the approach and land on the moving target.
-We discuss the three different parts in the following subsections.
 
@@
 
-\section{Proposed Methodology}
-In reviewing prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing target throughout the entire manoeuvre.
-As the quadrotor approaches the landing target, the target often goes beyond the camera's field of view, causing camera based navigation techniques to fail.
-Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.
+\section{Methodology}
 
-To address both of these issues, we propose a novel solution utilizing an nested apriltags which we term inception apriltag.
-We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform.
-We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.
-
-\section{Project Progress}
-\subsection{Hardware Setup}
-\subsubsection{Quadrotor}
+\section{Hardware}
+\subsection{Quadrotor}
 For the hardware, we have chosen to reuse equipment that is readily available to us in the Wave Lab.
@@
 
-\subsection{Software Setup}
+\subsection{Vision Capture}
+Firefly camera
+
 \subsubsection{Pixhawk Firmware - PX4}
@@
 
-\subsubsection{Simulator}
-Initially we have explored the possibility of using the combination of PX4's Software in the Loop Simulation (SITL) and Gazebo 6 as our simulation environment for our project, however we found the combination of install instructions changing at a fast pace, and the documentation not up to date to be a major concern for us.
-We have therefore decided to fallback on developing the estimation and control loop in Matlab.
+\subsubsection{AprilTag}
+On the landing target from we have successfully calibrated the Logitech webcam and used the Apriltag library to obtain a pose estimate, and have manually verified the estimates are accurate, for distance the error is $\pm 1$cm.
+We have also successfully implemented the ability to identify two different apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from both apriltags are equal.
 
-\subsubsection{AprilTag}
+Next is to workout how to transform the measurements from the pose estimates of the apriltags in relation to the quadrotor's body frame.
+
+\subsection{Quadrotor Control}
+In reviewing prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing target throughout the entire manoeuvre.
+As the quadrotor approaches the landing target, the target often goes beyond the camera's field of view, causing camera based navigation techniques to fail.
+Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.
+
+To address both of these issues, we propose a novel solution utilizing an nested apriltags which we term inception apriltag.
+We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform.
+We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.
+
+\subsection{Measurement and State Estimation}
+
+One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state.
+This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here).
+This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the april tag.
+An example of this implementation is shown in figure (Kevins image).
+This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also removed a lot of the robustification that is provided in the standard AprilTag library.
+
+In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the current distance between the quadrotors position relative to the landing pad.
+
+\subsection{Adaptive Image Preprocessing}
+
+As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is to low to be used effectively in a PID control loop.
+Building on the work of Ling, who noted that higher update rates were possible using AprilTags when the majority of the image is filled with black pixels, a set of image preprocessing methods were developed to maximize the update rate of the AprilTag library.
+
+\subsubsection{Adaptive Image Windowing}
+
+If one assumes that the quadrotor does not move to fast, there is relativity low rotation between image captures, and that the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
+Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to black out the protions of the image where the AprilTag is unlikely to be.
+An example of this implementation is highlighted in Figure (Adptive windowing).
+
+While the adaptive windowing procedure works well for when the AprilTag observed at a distance, where they do not take up a significant portion of the image, it begins to fail when the quadrotor approach the landing pad as the observed size of AprilTag begins to become larger and larger in the  image.
+This leads to the processing time of the AprilTags to increase as the quadrotor gets closer, which is a major issue as in these cases a higher update rate is actually required.
+In cases where the AprilTag is not observed in the expected location (bounding box), the size of the bounding box is set to the size of the image and the entire image is processed.
+
+\subsubsection{AprilTag Inception}
+ In order to be used for landing, the AprilTag attached to the landing pad must be relatively larger so that it can be detected from a distance of at least 15 meters which from our experience means the AprilTag must be at least 50 cm by 50 cm in size.
+The large size of the AprilTag becomes a major issue during the final portion of the landing procedure as the AprilTag image will both appear quite large in the captured image which causes to the Adaptive Windowing Procedure outlined above to become ineffective.
+Furthermore close proximity to the AprilTag also grealy increases the chance that a portion of the AprilTag will be located outside of the captured image, causing no state estimation to be provided at the critical stages of landing.
+
+To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing site of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag.
+This secondary AprilTag is assigned different family id, and is placed in the center of a primary AprilTag.
+Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture.
+An example of this procedure is highlighted in Figure \ref{fig:apriltagInception}.
+
 \begin{figure}[H]
@@
 	\end{subfigure}
-	\caption{Apriltag Inception - To mitigate the FOV problem}
-	\label{fig:apriltag}
+	\caption{Apriltag Inception - To mitigate the FOV problem assocaited with }
+	\label{fig:apriltagInception}
 \end{figure}
 
-On the landing target from we have successfully calibrated the logitech webcam and used the Apriltag library to obtain a pose estimate, and have manually verified the estimates are accurate, for distance the error is $\pm 1$cm.
-We have also successfully implemented the ability to identify two different apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from both apriltags are equal.
+\subsubsection{Adaptive Image Down-sampling}
+It was also noted that the image could be greatly down sampled as well if the quadrotor approaches the landing pad as not as many pixels are required to calculated the location and state of the AprilTag in the image.
+Therefore 3 image sampling sizes were also introduced into the code which sub-sample the image to 160 by 140 pixels and 320 by 280 (half and quarter resolution) when the distance between the camera and the AprilTag is less than 1.5 and 3 meters respectively.
+If the camera is further than 3 meters from the AprilTag the native resolution of 640 by 480 is used.
+This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of increasing the rate of AprilTag process.
 
-Next is to workout how to transform the measurements from the pose estimates of the apriltags in relation to the quadrotor's body frame.
+In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions.
+The calibration file passed to the AprilTag library during the state estimation proccedure is selected based on what the current camera resolution is set at.
+
+\section{Results}
+
+\subsubsection{Detection Delay}
+\begin{equation}
+    t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
+\end{equation}
 

### 2016-04-17 include/awesomo/camera.hpp
Update

@@ -22,13 +22,13 @@
 #define CAMERA_NORMAL 0
 #define CAMERA_FIREFLY 1
 
-#define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-#define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-#define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+// #define FIREFLY_640 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+// #define FIREFLY_320 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+// #define FIREFLY_160 "/home/chutsu/Dropbox/proj/awesomo/configs/pointgrey_firefly/ost_160.yaml"
 
-// #define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
-// #define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"
-// #define FIREFLY_160 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_160.yaml"
+#define FIREFLY_640 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_640.yaml"
+#define FIREFLY_320 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_320.yaml"
+#define FIREFLY_160 "/home/odroid/awesomo/configs/pointgrey_firefly/ost_160.yaml"
 
 
 

### 2016-04-17 src/ros/quadrotor_node.cpp

@@ -440,7 +440,7 @@ int main(int argc, char **argv)
     x_controller.dead_zone = 1.0;
     x_controller.min = deg2rad(-10);
     x_controller.max = deg2rad(10);
-    x_controller.k_p = 0.0;
+    x_controller.k_p = 1.0;
     x_controller.k_i = 0.0;
     x_controller.k_d = 0.0;
 
@@ -449,7 +449,7 @@ int main(int argc, char **argv)
     y_controller.dead_zone = 1.0;
     y_controller.min = deg2rad(-10);
     y_controller.max = deg2rad(10);
-    y_controller.k_p = 0.0;
+    y_controller.k_p = 1.0;
     y_controller.k_i = 0.0;
     y_controller.k_d = 0.0;
 
@@ -477,8 +477,10 @@ int main(int argc, char **argv)
         y_controller.setpoint = 0.0;
 
         dt = ros::Time::now() - last_request;
-        roll_input = pid_calculate(&x_controller, quad.roll, dt);
-        pitch_input = pid_calculate(&y_controller, quad.pitch, dt);
+        pid_calculate(&x_controller, quad.pose_x, dt);
+        pid_calculate(&y_controller, quad.pose_y, dt);
+        roll_input = x_controller.output;
+        pitch_input = y_controller.output;
         last_request = ros::Time::now();
 
         q = euler2quat(roll_input, pitch_input, 0);
@@ -499,13 +501,15 @@ int main(int argc, char **argv)
         quad.attitude_publisher.publish(attitude);
         quad.throttle_publisher.publish(throttle);
 
+        ROS_INFO("---");
         ROS_INFO("dt %f", dt.toSec());
-        ROS_INFO("quadrotor.roll %f", quad.roll);
-        ROS_INFO("quadrotor.pitch %f", quad.pitch);
+        ROS_INFO("quadrotor.pose_x %f", quad.pose_x);
+        ROS_INFO("quadrotor.pose_y %f", quad.pose_y);
+        ROS_INFO("quadrotor.roll %f", rad2deg(quad.roll));
+        ROS_INFO("quadrotor.pitch %f", rad2deg(quad.pitch));
         ROS_INFO("roll.controller %f", roll_input);
         ROS_INFO("pitch.controller %f", pitch_input);
-
-
+        ROS_INFO("---");
 
 		// update
 		count++;

### 2016-04-18 docs/report/report.tex
updated report, added outline list

@@
 
+\section{Layout for Report}
+\begin{itemize}
+	\item Introduction
+	\item Related work
+	\item Hardware
+	\item Software libraries used
+	\item Methods
+	\begin{itemize}
+		\item camera methods (image processing)
+		\item PID controllers
+	\end{itemize}
+	\item Results and Discussion
+	\begin{itemize}
+		\item Image Processing Results
+		\item PID Results and Testing
+		\item Hardware difficulties? 
+	\end{itemize}
+	\item Future work 
+	\item Conclusion
+\end{itemize}
+
 \section{Introduction}
-
 The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference).
@@
 In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions.
-The calibration file passed to the AprilTag library during the state estimation proccedure is selected based on what the current camera resolution is set at.
+The calibration file passed to the AprilTag library during the state estimation procedure is selected based on what the current camera resolution is set at.
 

### 2016-04-18 docs/report/report.tex
more updates to report

@@
 \section{Introduction}
-The idea of quadrotor has been explored by several companies and researchers since quadrotors became a popular alternative to fixed wing and single rotor aircraft (DJI auto landing, Pixhawk, make a reference).
-However most of these methods usually assume that the landing zone is static and that there is very little wind or disturbances.
-In cases of high wind or a rapidly moving platform, which from the quadrotor's reference frame can be be though of as nearly equivalent cases, normal autonomous landing procedures will likely fail.
-
 Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}.
@@
 
-\section{Related Work}
-The challenging of autonomous landing can be categorized into three distinct parts.
-First, the quadrotor must sense or detect the landing target to obtain positional estimates relative to the quadrotor.
-Secondly, the quadrotor must plan its rendezvous trajectory with the landing target.
-Third and finally, the quadrotor must apply a set of controller commands to approach the platform, matching both speed and heading on the approach and land on the moving target.
+The autonomous landing problem can be thought of as a set of three separate control problems or stages.
+First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods.
+Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory.
+Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.
 
-\subsection{Perception and State Estimation}
+In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.
+
+\section{Related Work} \textbf{(Needs love but might also just be cut.) }
+
 For perception existing solutions use a variety of simple to complex techniques.
@@
 
-\subsection{Planning}
-In the literature we reviewed, rendezvous planning was neglected as it was assumed that quadrotor has a clear view of its landing target.
-Most authors tend to focus on the detection and estimation of the quadrotor's pose relative to the target and maintaining an accurate estimation throughout the landing procedure which is mostly handled by a series of control loops.
-
-\subsection{Control}
 A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}.
@@
 \section{Methodology}
+The majority of effort in this project so far can be separated into two individual but complementary pieces.
+First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$.
+Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizonal plane.
 
-\section{Hardware}
-\subsection{Quadrotor}
-For the hardware, we have chosen to reuse equipment that is readily available to us in the Wave Lab.
-For the quadrotor we have been using the DJI F450 quadrotor frame, Emax 2213-935KV motors with complimentary 1045R propellers, Thunder Power lipo 11.1V 4200mah battery, DJI E310 420S 20A electronic speed controller and Pixhawk v2.4 as our flight controller.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
-	\caption{DJI F450 with Pixhawk v1.5}
-\end{figure}
-
-\subsubsection{Onboard Autonomous Control System}
-In terms of onboard autonoumos control, we have decided to use the Odriod XU4 due to its size and processing power available, and a Logitech C270 HD webcam as our vision sensor.
-One problem we may face very soon is the narrow field of view and relatively low frame rate (25Hz) the logitech webcam has.
-We will be keeping our options open, and plan on replacing the logitech webcam with a Ximia xiQ USB3 camera with a wide angle lens in the near future.
-
-\subsection{Vision Capture}
-Firefly camera
-
-\subsubsection{Pixhawk Firmware - PX4}
-As mentioned in the hardware section, we have had numerous issues with regards to using the software suite for the Pixhawk Flight Controller, as well as the PX4 firmware itself.
-There are many instances where we could not explain the instability of the quadrotor during flight, many of which lead to costly crashes, but we believe through these experiences we have developed a procedure to lower the risk for such instances from happening often.
-
-\subsubsection{Odriod to Pixhawk Communication}
-For our autonomous system to control the quadrotor directly, the Odriod has to be able to communicate with the Pixhawk, this is where \verb|mavros| (ROS package) comes into play.
-Mavlink is a popular UAV communication protocol between UAV and ground control softwares, \verb|mavros| creates a mavlink ROS node to enable developers to monitor and issue mavlink commands with ease.
-We have successfully used mavros to arm and disarm Pixhawk (tested), in the near future we should be able to send velocity/attitude commands to control the quadrotor.
-
-\subsubsection{AprilTag}
-On the landing target from we have successfully calibrated the Logitech webcam and used the Apriltag library to obtain a pose estimate, and have manually verified the estimates are accurate, for distance the error is $\pm 1$cm.
-We have also successfully implemented the ability to identify two different apriltags of different sizes (see Fig~\ref{fig:apriltag}), pose estimates from both apriltags are equal.
-
-Next is to workout how to transform the measurements from the pose estimates of the apriltags in relation to the quadrotor's body frame.
-
-\subsection{Quadrotor Control}
-In reviewing prior work, a reoccurring problem lies in the difficulty in maintaining an accurate pose estimation between the quadrotor and the landing target throughout the entire manoeuvre.
-As the quadrotor approaches the landing target, the target often goes beyond the camera's field of view, causing camera based navigation techniques to fail.
-Furthermore, in certain conditions the tilt angle of the quadrotor could cause difficulty in maintaining a visual on the landing pad for a downward facing or fixed camera.
-
-To address both of these issues, we propose a novel solution utilizing an nested apriltags which we term inception apriltag.
-We will replicate the experiment performed by \cite{Ling2014}, where we assume the quadrotor already has a visual of the landing platform.
-We aim to implement a series of controllers for the approach and landing of the quadrotor to the moving landing platform.
-
-\subsection{Measurement and State Estimation}
-
+\subsection{Measurement and State Estimation using AprilTags}
 One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state.
 This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here).
-This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the april tag.
+This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the AprilTag.
 An example of this implementation is shown in figure (Kevins image).
@@
 
-\subsection{Adaptive Image Preprocessing}
+\subsubsection{Adaptive Image Preprocessing}
 
@@
 
+\subsection{Controller and State Monitoring}
+
+\section{Experimental Hardware}
+The quadrotor used in this experiment assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers.
+The flight controller selected for the project was a Pixhawk v2.4 running the PX4 firmware stack.
+An Odroid XU4 was selected as the onboard computer to processes captured images from a video stream and sends attitude commands via usb to the Pixhawk based of the PID controllers and current state as outlined above.
+Communication between the Odroid and the Pixhawk is handled by the mavros package which is a wrapper around the popular Mavlink communication protocal for UAVs.
+Video was captured using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels along with a FujiFilm 135 degree FOV lens.
+The quadrotor and camera are highlighted in Figure \ref{Quadrotor}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
+	\caption{DJI F450 with Pixhawk v1.5}
+	\label{Quadrotor}
+\end{figure}
+
 \section{Results}
+\begin{itemize}
+	\item Results of the image stuff
+	\begin{itemize}
+		\item Plot of FPS vs distance
+		\item Plot of true state vs mocap state?
+	\end{itemize}
+
+	\item PID/Control results 
+	\begin{itemize}
+		\item Plot XY for the controller loop
+		\item Optimal PID settings
+		\item How we got there
+		\item Decent plot (V as a funtion of Z)
+		\item Decent planner
+		\item Video?
+	\end{itemize}
+
+\end{itemize}
 

### 2016-04-20 docs/report/report.tex
updated report again

@@
 
-\section{Layout for Report}
-\begin{itemize}
-	\item Introduction
-	\item Related work
-	\item Hardware
-	\item Software libraries used
-	\item Methods
-	\begin{itemize}
-		\item camera methods (image processing)
-		\item PID controllers
-	\end{itemize}
-	\item Results and Discussion
-	\begin{itemize}
-		\item Image Processing Results
-		\item PID Results and Testing
-		\item Hardware difficulties? 
-	\end{itemize}
-	\item Future work 
-	\item Conclusion
-\end{itemize}
+\section{Introduction}
+Over the years there has been been a growing interest in autonomous landing of quadrotors as landing is often one of the most dangerous and risk prone parts of flight.
+There are now several commercial and research based implementations of autonomous landing with the DJI Phantom and Pixhawk flight controller both being capable of automatic landing using a series of sensors and control algorithms.
+However there does not yet seem to be a reliable method of landing a quadrotor on either a moving platform or in cases where there is relatively large cross wind disturbance.
 
-\section{Introduction}
-Over the years there has been been at least some interest in the problem of landing a quadrotor on a moving platform and there have been at least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012}.
-The problem has been explored from a fairly wide range of approaches.
-
-Possible applications for this work include autonomous landing on a boat in high wind conditions, landing on a charging platform and more.
-
-The major challenge with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
+In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variaty of angles.
+Overall none of these approachs have solved the issue and most only work on very slow moving platforms with little or no wind disturbances.
+One of the most challenging with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
 
@@
 First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$.
-Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizonal plane.
+Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizontal plane.
 
@@
 \subsection{Controller and State Monitoring}
+In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and at all points in time has a clear view through the camera image of the landing target located on the target vehicle.
+The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle.
+Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
+Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.
+
+In order to achieve the described behaviour, a set of 3 of PID controllers are developed, one for the x, y and z directions respectively.
+During all stages of landing the x and y PID controllers work to minimize the displacement between the target and the qaudrotor which also has the side effect of maintaining the velocity relative to the target.
+During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one.
+Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.
+
+The PIDx and PIDy are designed such that thier output is mapped to attitude commands in the pitch and roll relative to the quadrotor frame as outlined in Equations \ref{PIDx}, \ref{PIDy}, \ref{PIDz} .
+The commanded throttle is also adjusted to account for the commanded roll and pitch using Equation \ref{Adjusted Throttle} to better maintain altitude when $\phi_t$ and $\psi_t$ are non-zero.
+
+\begin{equation}
+\label{PIDx}
+	\psi_t = cos(\theta) \left( K_p e_x + K_i \sum_{t=0}^{t} \dot{e_x}_{,t} dt + K_d \dot{e_x}_{,t}) \right)
+\end{equation}
+
+\begin{equation}
+\label{PIDy}
+	\phi_t = sin(\theta) \left( K_p e_y + K_i \sum_{t=0}^{t} \dot{e_y}_{,t} dt + K_d \dot{e_y}_{,t} \right)
+\end{equation}
+
+\begin{equation}
+\label{PIDz}
+	Thrust_z = K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
+\end{equation}
+
+\begin{equation}
+\label{Adjusted Throttle}
+	AdjustedThrust = \frac{Thrust_z}{cos(\phi_t) cos(\psi_t)}
+\end{equation}
 
@@
 		\item How we got there
-		\item Decent plot (V as a funtion of Z)
-		\item Decent planner
+		\item Decent plot (V as a function of Z)
 		\item Video?
@@
 \end{itemize}
+\subsection{PID and Controller Results}
 
-\subsubsection{Detection Delay}
+So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.
+
+\section{Conclusion and Future Work}
+
+\section{Proposed Future Work}
+In the coming weeks, the PID controllers tested and developed using the MOCAP system will be tested using state estimates that are produced from the AprilTag library and the image preprocessing methods outlined in section \textbf{\textit{OUTLINE OF IMAGE PREPROCESSSING}}.
+
+One major issue highlighted in Ling \cite{Ling2014} is that due to the relatively long processing time of the AprilTags library, the estimated state obtained at a time $t$ does not actually represent the current state due to a time lag.
+This time lag as outlined in \cite{Ling2014} and defined in \ref{Detection Delay} must be accounted for when using the camera to estimate state.
+Currently our proposed method to measure this lag is to use the MOCAP system to provide a ground truth for the state from which we can estimate the estimated state.
+
 \begin{equation}
+\label{Detection Delay}
     t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
 \end{equation}
+
+The next issue that will need to be address is the problem of the camera view.
+The dynamics of a quadrotor work in such a way that in order to move towards a goal point, the quadrotor must tilt away from the target which leads to problems with maintaining a view of the target when desired roll or pitch angles are greater than approximately 10 degress.
+This issue can either be addressed by mounting the camera at an angle or by adding a gimbals to the the quadrotor such that the gimbal will be sent commands by the onboard computer that will maintain a constant view of the target regardless of the commanded roll and pitch.
+
+Both of the above solutions have significant implementation questions that will have to be answered.
+If using the fixed camera angle, then the yaw of the qaudrotor will need to be controlled by a PID controller, similar to the the PID controllers to the roll and pitch.
+In the case of significant wind, the quadrotor will need to rotate itself such that the front of the quad is pointed into the wind during the final decent.
+
+If a gimbal is used there are two issues that arise.
+First a new set of controllers that send roll, pitch and yaw commands to the gimbal such that the camera it is attached to maintains a centred view of the target platform must be developed.
+These controllers will likely be similar to the PID controllers developed above and so they are not considered to be terrible difficult to define are implement.
+The more difficult part of using a gimbal is related to resuming the gimbal state, which in cheaper gimbals do provide.
+All of the gimbals that have been researched as part of this project do not provide state feedback and so they are considered to be open loop.
+Therefore in order to use such a gimbal the user will need to assume the commanded gimbal position is equal to the true gimbal position, from which a transform between the quad rotor and the gimbal can be made.
 

### 2016-04-20 docs/report/report.tex
report update, introduction changes

@@
 In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variaty of angles.
-Overall none of these approachs have solved the issue and most only work on very slow moving platforms with little or no wind disturbances.
-One of the most challenging with autonomous precision landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
+Overall none of these approach have completely solved the problem and most approaches only work on very slow moving platforms with little or no wind disturbances.
 
+One of the most challenging parts with autonomous landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
+In many cases GPS is not a viable option both the landing target and the quadrotor due to the lack of accuracy unless an RTK GPS system is used.
+In many cases the use of an RTK system is not a readily available option due to cost or quadrotor needs.
+
+\subsection{Related Work}
 The autonomous landing problem can be thought of as a set of three separate control problems or stages.
@@
 Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.
-
-In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.
-
-\section{Related Work} \textbf{(Needs love but might also just be cut.) }
 
@@
 Additionally the experiments did not seem to account for pitch or roll of the platform.
+
+In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.
 

### 2016-04-21 docs/report/report.tex
makig plots

@@
 
-In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the current distance between the quadrotors position relative to the landing pad.
+In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the landing pad.
 
@@
 If one assumes that the quadrotor does not move to fast, there is relativity low rotation between image captures, and that the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
-Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to black out the protions of the image where the AprilTag is unlikely to be.
-An example of this implementation is highlighted in Figure (Adptive windowing).
+Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to black out the portions of the image where the AprilTag is unlikely to be.
+An example of this implementation is highlighted in Figure (Adaptive windowing).
 
@@
 The large size of the AprilTag becomes a major issue during the final portion of the landing procedure as the AprilTag image will both appear quite large in the captured image which causes to the Adaptive Windowing Procedure outlined above to become ineffective.
-Furthermore close proximity to the AprilTag also grealy increases the chance that a portion of the AprilTag will be located outside of the captured image, causing no state estimation to be provided at the critical stages of landing.
+Furthermore close proximity to the AprilTag also greatly increases the chance that a portion of the AprilTag will be located outside of the captured image, causing no state estimation to be provided at the critical stages of landing.
 
@@
 	\end{subfigure}
-	\caption{Apriltag Inception - To mitigate the FOV problem assocaited with }
+	\caption{Apriltag Inception }
 	\label{fig:apriltagInception}

### 2016-04-21 docs/report/plot_data/Camera_Plot/AprTag_Plot_Generation.m

@@ -1,0 +1,68 @@
+% Plotting camera data for report. 
+close all;
+clear all;
+load linear_data.mat;
+load 'Dimond_Data.mat'
+
+FPS_Plotting_x = True_y(6:end);
+
+True_y = [True_y; DMocap_y];
+True_x = [True_x; DMocap_x];
+True_z = [True_z; DMocap_z];
+
+Apr_x = [Apr_x(6:end); DApr_x(2:end)];
+Apr_y = [Apr_y(6:end); DApr_y(2:end)];
+Apr_z = [Apr_z(6:end); DApr_z(2:end)];
+
+time = (Time - Time(1))/10^9;
+
+dist = sqrt((-True_y(1:end) + 0.09).^2 + ...
+            (True_x(1:end) + 0.03).^2 + ...
+            (True_z(1:end) - 1.33).^2 );
+
+measured_dist = sqrt((Apr_y).^2 + ...
+                (Apr_x).^2 + ...
+                (Apr_z).^2 );
+            
+figure(1) %error plot as funct distance
+plot(dist, (dist-measured_dist+0.03), 'bo');
+set(gca, 'XMinorTick', 'on', ...
+          'YMinorTick', 'on', ...
+          'FontWeight', 'bold', ...
+          'Fontsize', 12);
+xlabel('Euclidean Distance Between AprilTag and Camera [meters]',...
+                                    'Fontsize', 15, ...
+                                    'FontWeight', 'normal');
+                                
+ylabel('Measured Euclidean Distance [meters]',...
+               'Fontsize', 15, ...
+               'FontWeight', 'normal');
+axis([0 3.5 -0.2 0.2]);
+
+% figure(2) %ground truth
+% error_x = (Apr_x(6:end) - True_y(1:end) + 0.09);
+% error_y = (Apr_y(6:end) + True_x(1:end) + 0.02);
+% error_z = (Apr_z(6:end) + True_z(1:end) - 1.33);
+% plot3(Apr_x(6:end), Apr_y(6:end), Apr_z(6:end), '-bx', ...
+%       True_y(1:end) + 0.09, True_x(1:end) + 0.02, -(True_z(1:end) - 1.33) , '--rd')
+%  xlabel('x')
+%  ylabel('y')
+%  zlabel('z')
+
+
+figure(3)
+plot(FPS_Plotting_x, FrameRate(7:26), '-bo')
+set(gca, 'XMinorTick', 'on', ...
+          'YMinorTick', 'on', ...
+          'FontWeight', 'bold', ...
[…]

### 2016-04-21 docs/report/plot_data/PID_Plot/PidPlotting.m
made all the figs

@@ -1,0 +1,149 @@
+% plots for the PIDs
+clc;
+close all;
+clear all;
+
+load('Pid Plotting Data.mat')
+
+figure(1)
+% plot z with the setpoint.
+% [ax,h1,h2] = plotyy(Time, True_z, Time, Pid_z_Kp, 'plot') ;
+% hold(ax(1))
+% plot(ax(1), Time, setpointz, 'm')
+% hold(ax(2))
+% plot(ax(2), Time, Pid_z_Kd,'r')
+
+% fixing the Kd data file
+x = Pid_z_Kd;
+x(Pid_z_Kd == 0 ) = [];
+xt = Time;
+xt(Pid_z_Kd == 0 ) = [];
+Kd_z_interpolated = interp1(xt,x,Time);
+
+% plot z with the setpoint.
+[ax,h1,h2] = plotyy(Time, True_z, Time, Pid_z_Kp, 'plot') ;
+hold(ax(1))
+plot(ax(1), Time, setpointz, 'm')
+hold(ax(2), 'on')
+plot(ax(2), Time, Kd_z_interpolated,'r')
+hold(ax(2), 'off')
+set(ax(1),  'YLimMode', 'manual', 'YTickMode', 'auto',...
+            'YMinorTick', 'on', 'Fontsize', 12, ...
+            'FontWeight', 'bold', ...
+            'YColor', 'k')
+     
+set(ax(2), 'YLimMode', 'auto', 'YTickMode', 'auto',...
+            'YMinorTick', 'on', 'Fontsize', 12, ...
+            'FontWeight', 'bold', ...
+            'YColor', 'k')
+set(ax(2),'Box','Off')
+set(ax(1),'Box','Off')
+
+ylabel(ax(1), 'Commanded Position [meters]',...
+               'Fontsize', 15, ...
+               'FontWeight', 'normal');
+ylabel(ax(2), 'PID Gains [Change in Thrust]',...
+               'Fontsize', 15, ...
+               'FontWeight', 'normal', ...
+               'color', 'k');
+xlabel('Time [seconds]',...
+             'Fontsize', 15, ...
+             'FontWeight', 'normal');
+legend('True Elevation [m]', ...
+       'Set Elevation [m]', ...
+       'Proporitional Gain [Thrust]', ...
+       'Derivative Gain [Thrust]')
+                                
+
+%axis([0 3.5 -0.2 0.2]);
+
+figure(2)
+
+setpointx = setpointz*0;
+% fixing the Kd data file
[…]

### 2016-04-21 docs/report/report.tex
Update report

@@
 
-In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.
+In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTags \cite{apriltags} to provide the estimated state of the quadrotor relative to the landing pad.
 
 \section{Methodology}
-The majority of effort in this project so far can be separated into two individual but complementary pieces.
-First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$.
-Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizontal plane.
+The majority of effort in this project thus far can be separated into two individual but complementary pieces.
+First, a significant effort effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags.
+Secondly, using information from the estimated quadrotor state, a state machine and a set of PID controllers were developed that tracks and lands on a desired target.
 
 \subsection{Measurement and State Estimation using AprilTags}
-One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state.
-This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here).
-This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the AprilTag.
-An example of this implementation is shown in figure (Kevins image).
-This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also removed a lot of the robustification that is provided in the standard AprilTag library.
+One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz.
+This problem is exacerbated when the image size increases, as do the computational time needed to extract the pose estimate of the AprilTag, from our initial experimentation the computational time grows exponentially as image size increases as shown in (add a figure here).
+This problem was also noted in the work of \cite{Ling2014} where he addressed the issue by reducing the brightness of the image so that the majority of the image is black except for the AprilTag, thus reducing image processing requirements.
+An example of this implementation is shown in Figure~\ref{fig:ling_apriltags} This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also the lost of robustness in estimating the AprilTags.
 
-In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the landing pad.
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/ling_apriltags_1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/ling_apriltags_2.png}
+	\end{subfigure}
+	\caption{Ling's approach to optimizing AprilTags detection \cite{Ling2014}}
+	\label{fig:ling_apriltags}
+\end{figure}
+
+In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the AprilTag, additionally we introduce the use of .
 

### 2016-04-21 docs/report/plot_data/PID_Plot/PidPlotting.m
fixed PIDthrust

@@ -21,11 +21,11 @@ xt(Pid_z_Kd == 0 ) = [];
 Kd_z_interpolated = interp1(xt,x,Time);
 
 % plot z with the setpoint.
-[ax,h1,h2] = plotyy(Time, True_z, Time, Pid_z_Kp, 'plot') ;
+[ax,h1,h2] = plotyy(Time, True_z, Time, Pid_z_Kp*10, 'plot') ;
 hold(ax(1))
 plot(ax(1), Time, setpointz, 'm')
 hold(ax(2), 'on')
-plot(ax(2), Time, Kd_z_interpolated,'r')
+plot(ax(2), Time, Kd_z_interpolated*10,'r')
 hold(ax(2), 'off')
 set(ax(1),  'YLimMode', 'manual', 'YTickMode', 'auto',...
             'YMinorTick', 'on', 'Fontsize', 12, ...
@@ -42,7 +42,7 @@ set(ax(1),'Box','Off')
 ylabel(ax(1), 'Commanded Position [meters]',...
                'Fontsize', 15, ...
                'FontWeight', 'normal');
-ylabel(ax(2), 'PID Gains [Change in Thrust]',...
+ylabel(ax(2), 'PID Gains [Percentage Change in Thrust]',...
                'Fontsize', 15, ...
                'FontWeight', 'normal', ...
                'color', 'k');
@@ -51,8 +51,8 @@ xlabel('Time [seconds]',...
              'FontWeight', 'normal');
 legend('True Elevation [m]', ...
        'Set Elevation [m]', ...
-       'Proporitional Gain [Thrust]', ...
-       'Derivative Gain [Thrust]')
+       'Proporitional Gain [Precentage of Thrust]', ...
+       'Derivative Gain [Percentage of Thrust]')
                                 
 
 %axis([0 3.5 -0.2 0.2]);

### 2016-04-21 docs/report/report.tex
Edit apriltag sections

@@
 \usepackage[margin=0.8in]{geometry}
-%\setlength{\parskip}{\baselineskip}%
+\setlength{\parskip}{\baselineskip}
 %\setlength{\parindent}{0pt}
@@
 	\label{fig:ling_apriltags}
+	\vspace{-0.4cm}
 \end{figure}
 
-In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the AprilTag, additionally we introduce the use of .
+In this work, the slow rate of state estimation was addressed using two novel ideas.
+First, the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the AprilTag.
+Secondly, we introduce the use of a Region of Interest (ROI) window to focus only on the AprilTag to reduce computational time required to estimate the pose.
+These novel ideas will be discussed in the following subsections.
 
@@
 
-As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is to low to be used effectively in a PID control loop.
-Building on the work of Ling, who noted that higher update rates were possible using AprilTags when the majority of the image is filled with black pixels, a set of image preprocessing methods were developed to maximize the update rate of the AprilTag library.
+As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is too low to be used effectively in a PID control loop.
+Building upon the work of \cite{Ling2014}, who improved the AprilTag estimation rate by reducing the brightness on the image such that the majority of the pixels are black, additionally a set of image preprocessing methods such as Canny-Edge thresholding were also used.
 
@@
 If one assumes that the quadrotor does not move to fast, there is relativity low rotation between image captures, and that the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
-Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to black out the portions of the image where the AprilTag is unlikely to be.
-An example of this implementation is highlighted in Figure (Adaptive windowing).
-
-While the adaptive windowing procedure works well for when the AprilTag observed at a distance, where they do not take up a significant portion of the image, it begins to fail when the quadrotor approach the landing pad as the observed size of AprilTag begins to become larger and larger in the  image.
-This leads to the processing time of the AprilTags to increase as the quadrotor gets closer, which is a major issue as in these cases a higher update rate is actually required.
+Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to segment out portions of the image where the AprilTag is unlikely to be.
+An example of this implementation is highlighted in Figure \ref{fig:apriltags_windowing}.
 In cases where the AprilTag is not observed in the expected location (bounding box), the size of the bounding box is set to the size of the image and the entire image is processed.
 
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_roi_1.png}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\linewidth}
+		\includegraphics[width=\textwidth]{images/apriltags_roi_2.png}
+	\end{subfigure}
+	\caption{Adaptive Image Windowing}
+	\label{fig:apriltags_windowing}
+\end{figure}
+
+While the adaptive windowing procedure decreases the computational resources needed for extracting pose estimates, there are two other problems that windowing cannot solve.
+First, as the size of the observed Apriltag increases, windowing is no longer adequate in decreasing computational time, this is an issue in cases where a high update rate is required (e.g.
+quadrotor landing).
+Second, in our use case as the observed AprilTag gets larger it becomes easy for the camera to lose track of the AprilTag itself, increasing the risk of no estimation for that time.
+
 \subsubsection{AprilTag Inception}
- In order to be used for landing, the AprilTag attached to the landing pad must be relatively larger so that it can be detected from a distance of at least 15 meters which from our experience means the AprilTag must be at least 50 cm by 50 cm in size.
-The large size of the AprilTag becomes a major issue during the final portion of the landing procedure as the AprilTag image will both appear quite large in the captured image which causes to the Adaptive Windowing Procedure outlined above to become ineffective.
-Furthermore close proximity to the AprilTag also greatly increases the chance that a portion of the AprilTag will be located outside of the captured image, causing no state estimation to be provided at the critical stages of landing.
 
-To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing site of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag.
-This secondary AprilTag is assigned different family id, and is placed in the center of a primary AprilTag.
+To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
+This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag.
 Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture.
@@
 \subsubsection{Adaptive Image Down-sampling}
-It was also noted that the image could be greatly down sampled as well if the quadrotor approaches the landing pad as not as many pixels are required to calculated the location and state of the AprilTag in the image.
-Therefore 3 image sampling sizes were also introduced into the code which sub-sample the image to 160 by 140 pixels and 320 by 280 (half and quarter resolution) when the distance between the camera and the AprilTag is less than 1.5 and 3 meters respectively.
-If the camera is further than 3 meters from the AprilTag the native resolution of 640 by 480 is used.
-This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of increasing the rate of AprilTag process.
+A final technique used to optimize the AprilTag detection was the introduction of down sampling the image size as the estimated distance between camera and AprilTag decreases.
+We devised 2 image down sampling sizes $320 \times 280$ (half resolution) and $160 \times 140$ (quarter resolution), when the distance between the camera and the AprilTag is less than 1.5 and 3 meters, the images are down sampled to the two resolutions respectively.
+If the camera is further than 3 meters from the AprilTag, the native resolution of $640 \times 480$ is used.
+This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of maintaining a high AprilTag estimation rate.
 
-In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions.
-The calibration file passed to the AprilTag library during the state estimation procedure is selected based on what the current camera resolution is set at.
+In order to use down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the full, half and quarter camera resolutions, corresponding calibration files were then used with the AprilTag library during the state estimation procedure based on the current image resolution to obtain the correct pose estimates.
 

### 2016-04-21 docs/report/report.tex
Update report

@@
 \usepackage[margin=0.8in]{geometry}
-\setlength{\parskip}{\baselineskip}
+%\setlength{\parskip}{\baselineskip}
 %\setlength{\parindent}{0pt}
@@
 \subsection{Controller and State Monitoring}
-In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and at all points in time has a clear view through the camera image of the landing target located on the target vehicle.
-The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle.
+In this project we assumethat the quadrotor has successfully rendezvoused with the target vehicle and at all time has a clear view through the camera image of the landing target located on the target vehicle.
+The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
 Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
@@
 
-In order to achieve the described behaviour, a set of 3 of PID controllers are developed, one for the x, y and z directions respectively.
-During all stages of landing the x and y PID controllers work to minimize the displacement between the target and the qaudrotor which also has the side effect of maintaining the velocity relative to the target.
+In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands to reduce the horizontal and vertical distance between the quadrotor and the landing platform.
 During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one.
@@
 	\label{PIDx}
-	\psi_t = cos(\theta) \left( K_p e_x + K_i \sum_{t=0}^{t} \dot{e_x}_{,t} dt + K_d \dot{e_x}_{,t}) \right)
-\end{equation}
+	\hat{\psi_t} = cos(\theta) \left(K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t} \right)
+\end{equation}q
 
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_x.eps}
+	\caption{Position Controller - Roll Command}
+	\label{fig:apriltagInception}
+		\vspace{-0.4cm}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_y.eps}
+	\caption{Position Controller - Pitch Command}
+	\label{fig:apriltagInception}
+		\vspace{-0.4cm}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Elevation.eps}
+	\caption{Position Controller - Throttle Command}
+	\label{fig:apriltagInception}
+\end{figure*}
+
 So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.

### 2016-04-21 docs/report/report.tex
Update PID section of report

@@
 \subsection{Controller and State Monitoring}
-In this project we assumethat the quadrotor has successfully rendezvoused with the target vehicle and at all time has a clear view through the camera image of the landing target located on the target vehicle.
+In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
 The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
-Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
-Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.
+Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
+Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.
 
-In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands to reduce the horizontal and vertical distance between the quadrotor and the landing platform.
-During the approach the PIDz controller attempts to maintain a safe approach altitude such that the target does not go out of view during stage one.
-Once a these hold displacement value in x and y is achieve the $PID_z$ controller is set a set of commands that smoothly move the quadrotor to a landing position.
+In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as a altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
+We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.
 
-The PIDx and PIDy are designed such that thier output is mapped to attitude commands in the pitch and roll relative to the quadrotor frame as outlined in Equations \ref{PIDx}, \ref{PIDy}, \ref{PIDz} .
-The commanded throttle is also adjusted to account for the commanded roll and pitch using Equation \ref{Adjusted Throttle} to better maintain altitude when $\phi_t$ and $\psi_t$ are non-zero.
+The position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, these inputs are mapped to attitude and altitude commands in the roll, pitch and thrust relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}.
+The outputs of Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch} are then adjusted to account for the yaw $\theta$ changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}, the altitude commanded is adjusted when roll $\phi$ and pitch $\theta$ are non-zero to maintain altitude.
 
 \begin{equation}
-	\label{PIDx}
-	\hat{\psi_t} = cos(\theta) \left(K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t} \right)
-\end{equation}q
-
-\begin{equation}
-	\label{PIDy}
-	\phi_t = sin(\theta) \left( K_p e_y + K_i \sum_{t=0}^{t} \dot{e_y}_{,t} dt + K_d \dot{e_y}_{,t} \right)
+	\label{eq:pid_roll}
+	\hat{\phi_t} = K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t}
 \end{equation}
@@
 \begin{equation}
-	\label{PIDz}
-	Thrust_z = K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
+	\label{eq:pid_pitch}
+	\hat{\theta_t} = K_p e_y + K_i \sum_{t = 0}^{t} \dot{e}_{y,t} dt + K_d \dot{e}_{y ,t}
+\end{equation}
+
+\begin{equation}
+	\label{eq:pid_thrust}
+	\hat{T_z} =
+		K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
+\end{equation}
+
+\begin{equation}
+	\label{eq:pid_roll_adjusted}
+	\phi_t = \cos(\psi_t) \hat{\phi_t} - \sin(\psi_t) \hat{\theta_t}
+\end{equation}
+
+\begin{equation}
+	\label{eq:pid_pitch_adjusted}
+	\theta_t = \sin(\psi_t) \hat{\phi_t} + \cos(\psi_t) \hat{\theta_t}
 \end{equation}
@@
 	\label{Adjusted Throttle}
-	AdjustedThrust = \frac{Thrust_z}{cos(\phi_t) cos(\psi_t)}
+	T = 
+		T_{\text{hover}} +
+		\frac{\hat{T_{z}}}{cos(\phi_t) cos(\theta_t)}
 \end{equation}

### 2016-04-21 docs/report/report.tex
Update report

@@
 
-In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as a altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
+In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
 We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.
 
-The position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, these inputs are mapped to attitude and altitude commands in the roll, pitch and thrust relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}.
-The outputs of Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch} are then adjusted to account for the yaw $\theta$ changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}, the altitude commanded is adjusted when roll $\phi$ and pitch $\theta$ are non-zero to maintain altitude.
+The position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, these inputs are mapped to attitude and altitude commands in the roll $\hat{\phi_t}$, pitch $\hat{\theta_t}$ and thrust $\hat{T_z}$ relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}, these equations however assume that yaw $\psi$ is 0, if yaw is non-zero then roll and pitch need to be adjusted to account for the yaw changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}.
+The altitude command is adjusted when roll $\hat{\phi}$ and pitch $\hat{\theta}$ are non-zero to maintain altitude as in Equation \ref{eq:pid_thrust_adjusted}.
+
+\begin{equation}
+	\label{eq:pid_error}
+	e = e_{\text{setpoint}} - e_{\text{actual}}
+\end{equation}
 
@@
 \begin{equation}
-	\label{Adjusted Throttle}
-	T = 
+	\label{eq:pid_thrust_adjusted}
+	T_{z} = 
 		T_{\text{hover}} +

### 2016-04-21 docs/Untitled Folder/report.tex

--- 2016-04-21 docs/report/report.tex
@@
 \usepackage[margin=0.8in]{geometry}
-%\setlength{\parskip}{\baselineskip}
+%\setlength{\parskip}{\baselineskip}%
 %\setlength{\parindent}{0pt}
@@
 
-In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTags \cite{apriltags} to provide the estimated state of the quadrotor relative to the landing pad.
+In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTag \textbf{\textit{CITE APRILTAGS}} to provide the estimated state of the quadrotor relative to the landing pad.
 
 \section{Methodology}
-The majority of effort in this project thus far can be separated into two individual but complementary pieces.
-First, a significant effort effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags.
-Secondly, using information from the estimated quadrotor state, a state machine and a set of PID controllers were developed that tracks and lands on a desired target.
+The majority of effort in this project so far can be separated into two individual but complementary pieces.
+First, a significant effort effort was spent on ensuring the quadrotor's state was updated a a rate of at least 20 $Hz$.
+Next, using the information in the state  a set of PID controllers were developed that along with a state machine monitors the current relative position of the quadrotor and either initiates a landing procedure or attempts to minimize the relative displacement and velocity between the quadrotor and the landing pad in the horizontal plane.
 
 \subsection{Measurement and State Estimation using AprilTags}
-One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz.
-This problem is exacerbated when the image size increases, as do the computational time needed to extract the pose estimate of the AprilTag, from our initial experimentation the computational time grows exponentially as image size increases as shown in (add a figure here).
-This problem was also noted in the work of \cite{Ling2014} where he addressed the issue by reducing the brightness of the image so that the majority of the image is black except for the AprilTag, thus reducing image processing requirements.
-An example of this implementation is shown in Figure~\ref{fig:ling_apriltags} This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also the lost of robustness in estimating the AprilTags.
+One of the major challenges when using AprilTags on a robot that has limited computational power, such as a quadrotor, is the rate at which the AprilTag library can compute the state.
+This problem is exacerbated when using larger image sizes as the computational time of the AprilTag software appears to grow at least exponentially as shown in (add a figure here).
+This problem was also noted in the work of \cite{Ling2014} and he addressed the issue by reducing the brightness of the image so that majority of the image is black except for the AprilTag.
+An example of this implementation is shown in figure (Kevins image).
+This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also removed a lot of the robustification that is provided in the standard AprilTag library.
 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.45\linewidth}
-		\includegraphics[width=\textwidth]{images/ling_apriltags_1.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.45\linewidth}
-		\includegraphics[width=\textwidth]{images/ling_apriltags_2.png}
-	\end{subfigure}
-	\caption{Ling's approach to optimizing AprilTags detection \cite{Ling2014}}
-	\label{fig:ling_apriltags}
-	\vspace{-0.4cm}
-\end{figure}
-
-In this work, the slow rate of state estimation was addressed using two novel ideas.
-First, the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the AprilTag.
-Secondly, we introduce the use of a Region of Interest (ROI) window to focus only on the AprilTag to reduce computational time required to estimate the pose.
-These novel ideas will be discussed in the following subsections.
+In this work, the slow rate of state estimation was addressed using a novel method where the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the landing pad.
 
@@
 
-As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is too low to be used effectively in a PID control loop.
-Building upon the work of \cite{Ling2014}, who improved the AprilTag estimation rate by reducing the brightness on the image such that the majority of the pixels are black, additionally a set of image preprocessing methods such as Canny-Edge thresholding were also used.
+As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is to low to be used effectively in a PID control loop.
+Building on the work of Ling, who noted that higher update rates were possible using AprilTags when the majority of the image is filled with black pixels, a set of image preprocessing methods were developed to maximize the update rate of the AprilTag library.
 
@@
 If one assumes that the quadrotor does not move to fast, there is relativity low rotation between image captures, and that the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
-Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to segment out portions of the image where the AprilTag is unlikely to be.
-An example of this implementation is highlighted in Figure \ref{fig:apriltags_windowing}.
+Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to black out the portions of the image where the AprilTag is unlikely to be.
+An example of this implementation is highlighted in Figure (Adaptive windowing).
+
+While the adaptive windowing procedure works well for when the AprilTag observed at a distance, where they do not take up a significant portion of the image, it begins to fail when the quadrotor approach the landing pad as the observed size of AprilTag begins to become larger and larger in the  image.
+This leads to the processing time of the AprilTags to increase as the quadrotor gets closer, which is a major issue as in these cases a higher update rate is actually required.
 In cases where the AprilTag is not observed in the expected location (bounding box), the size of the bounding box is set to the size of the image and the entire image is processed.
 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}[b]{0.45\linewidth}
-		\includegraphics[width=\textwidth]{images/apriltags_roi_1.png}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.45\linewidth}
-		\includegraphics[width=\textwidth]{images/apriltags_roi_2.png}
-	\end{subfigure}
-	\caption{Adaptive Image Windowing}
-	\label{fig:apriltags_windowing}
-\end{figure}
+\subsubsection{AprilTag Inception}
+ In order to be used for landing, the AprilTag attached to the landing pad must be relatively larger so that it can be detected from a distance of at least 15 meters which from our experience means the AprilTag must be at least 50 cm by 50 cm in size.
+The large size of the AprilTag becomes a major issue during the final portion of the landing procedure as the AprilTag image will both appear quite large in the captured image which causes to the Adaptive Windowing Procedure outlined above to become ineffective.
+Furthermore close proximity to the AprilTag also greatly increases the chance that a portion of the AprilTag will be located outside of the captured image, causing no state estimation to be provided at the critical stages of landing.
 
-While the adaptive windowing procedure decreases the computational resources needed for extracting pose estimates, there are two other problems that windowing cannot solve.
-First, as the size of the observed Apriltag increases, windowing is no longer adequate in decreasing computational time, this is an issue in cases where a high update rate is required (e.g.
-quadrotor landing).
-Second, in our use case as the observed AprilTag gets larger it becomes easy for the camera to lose track of the AprilTag itself, increasing the risk of no estimation for that time.
-
-\subsubsection{AprilTag Inception}
-
-To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
-This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag.
+To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing site of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag.
+This secondary AprilTag is assigned different family id, and is placed in the center of a primary AprilTag.
 Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture.
@@
 \subsubsection{Adaptive Image Down-sampling}
-A final technique used to optimize the AprilTag detection was the introduction of down sampling the image size as the estimated distance between camera and AprilTag decreases.
-We devised 2 image down sampling sizes $320 \times 280$ (half resolution) and $160 \times 140$ (quarter resolution), when the distance between the camera and the AprilTag is less than 1.5 and 3 meters, the images are down sampled to the two resolutions respectively.
-If the camera is further than 3 meters from the AprilTag, the native resolution of $640 \times 480$ is used.
-This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of maintaining a high AprilTag estimation rate.
+It was also noted that the image could be greatly down sampled as well if the quadrotor approaches the landing pad as not as many pixels are required to calculated the location and state of the AprilTag in the image.
+Therefore 3 image sampling sizes were also introduced into the code which sub-sample the image to 160 by 140 pixels and 320 by 280 (half and quarter resolution) when the distance between the camera and the AprilTag is less than 1.5 and 3 meters respectively.
+If the camera is further than 3 meters from the AprilTag the native resolution of 640 by 480 is used.
+This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of increasing the rate of AprilTag process.
 
-In order to use down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the full, half and quarter camera resolutions, corresponding calibration files were then used with the AprilTag library during the state estimation procedure based on the current image resolution to obtain the correct pose estimates.
+In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions.
+The calibration file passed to the AprilTag library during the state estimation procedure is selected based on what the current camera resolution is set at.
 
 \subsection{Controller and State Monitoring}
-In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
-The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
-Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
-Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.
+In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and at all points in time has a clear view through the camera image of the landing target located on the target vehicle.
+The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle.
+Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
+Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing Vancouver.
 
@@
 	e = e_{\text{setpoint}} - e_{\text{actual}}
-\end{equation}
-
-\begin{equation}
-	\label{eq:pid_roll}
-	\hat{\phi_t} = K_p e_x + K_i \sum_{t = 0}^{t} e_{x, t} dt + K_d \dot{e}_{x,t}
-\end{equation}
-
-\begin{equation}
-	\label{eq:pid_pitch}
-	\hat{\theta_t} = K_p e_y + K_i \sum_{t = 0}^{t} \dot{e}_{y,t} dt + K_d \dot{e}_{y ,t}
-\end{equation}
-
-\begin{equation}
-	\label{eq:pid_thrust}
-	\hat{T_z} =
-		K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
 \end{equation}
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_x.eps}
-	\caption{Position Controller - Roll Command}
-	\label{fig:apriltagInception}
-		\vspace{-0.4cm}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_y.eps}
-	\caption{Position Controller - Pitch Command}
-	\label{fig:apriltagInception}
-		\vspace{-0.4cm}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Elevation.eps}
-	\caption{Position Controller - Throttle Command}
-	\label{fig:apriltagInception}
-\end{figure*}
-
 So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.

### 2016-04-21 docs/report/report.tex
Fix stan's poo poo 2

@@
 \subsubsection{Adaptive Image Down-sampling}
-A final technique used to optimize the AprilTag detection was the introduction of down sampling the image size as the estimated distance between camera and AprilTag decreases.
-We devised 2 image down sampling sizes $320 \times 280$ (half resolution) and $160 \times 140$ (quarter resolution), when the distance between the camera and the AprilTag is less than 1.5 and 3 meters, the images are down sampled to the two resolutions respectively.
-If the camera is further than 3 meters from the AprilTag, the native resolution of $640 \times 480$ is used.
-This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of maintaining a high AprilTag estimation rate.
+It was also noted that the image could be greatly down sampled as well if the quadrotor approaches the landing pad as not as many pixels are required to calculated the location and state of the AprilTag in the image.
+Therefore 3 image sampling sizes were also introduced into the code which sub-sample the image to 160 by 140 pixels and 320 by 280 (half and quarter resolution) when the distance between the camera and the AprilTag is less than 1.5 and 3 meters respectively.
+If the camera is further than 3 meters from the AprilTag the native resolution of 640 by 480 is used.
+This change only affected the image processing time when the quadrotor is within 3 meters of the quad and has the desired effect of increasing the rate of AprilTag process.
 
-In order to use down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the full, half and quarter camera resolutions, corresponding calibration files were then used with the AprilTag library during the state estimation procedure based on the current image resolution to obtain the correct pose estimates.
+In order to use this down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the normal, half and quarter camera resolutions.
+The calibration file passed to the AprilTag library during the state estimation procedure is selected based on what the current camera resolution is set at.
 
 \subsection{Controller and State Monitoring}
-In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
-The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
-Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
-Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.
+In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all time.
+The first step of performing  autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed with the target vehicle.
+Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must begin to descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
+Ideally the quadrotor will descend more rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just before it hits the target in order to minimize time and energy requirements of the landing maneuver.
 
-In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
+To achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
 We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.
@@
 	\label{eq:pid_thrust_adjusted}
-	T_{z} = 
+	T = 
 		T_{\text{hover}} +
@@
 \end{itemize}
+
+\subsection{AprilTag Results}
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{\linewidth}
+		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
+		\caption{}
+		\label{fig:pid_roll}
+	\end{subfigure}
+
+	\begin{subfigure}[b]{\linewidth}
+		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
+		\caption{}
+		\label{fig:pid_roll}
+	\end{subfigure}
+\end{figure}
+
 \subsection{PID and Controller Results}
@@
 	\centering
-	\includegraphics[width=\textwidth]{images/PID_x.eps}
-	\caption{Position Controller - Roll Command}
-	\label{fig:apriltagInception}
-		\vspace{-0.4cm}
+	\includegraphics[width=\textwidth]{images/PID_Pitch_x_true_and_obs.eps}
+	\caption{Position Controller - Pitch Command}
+	\label{fig:pid_roll}
 \end{figure*}
@@
 	\centering
-	\includegraphics[width=\textwidth]{images/PID_y.eps}
-	\caption{Position Controller - Pitch Command}
-	\label{fig:apriltagInception}
-		\vspace{-0.4cm}
+	\includegraphics[width=\textwidth]{images/PID_Pitch_Controls.eps}
+	\caption{Position Controller - Pitch Control Signal Components}
+	\label{fig:pid_roll}
 \end{figure*}
@@
 	\centering
-	\includegraphics[width=\textwidth]{images/PID_Elevation.eps}
-	\caption{Position Controller - Throttle Command}
-	\label{fig:apriltagInception}
+	\includegraphics[width=\textwidth]{images/PID_Roll_y_true_and_obs.eps}
+	\caption{Position Controller - Roll Command}
+	\label{fig:pid_roll}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Roll_Controls.eps}
+	\caption{Position Controller - Roll Control Signal Components}
+	\label{fig:pid_roll}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Elevation_True_and_obs.eps}
+	\caption{Position Controller - Thrust Command}
+	\label{fig:pid_roll}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Elevation_Controls.eps}
+	\caption{Position Controller - Thrust Signal Components}
+	\label{fig:pid_roll}
 \end{figure*}

### 2016-04-21 docs/report/report.tex
Update

--- 2016-04-21 docs/report/report.tex
@@
 \section{Methodology}
-The majority of effort in this project thus far can be separated into two individual but complementary pieces.
-First, a significant effort effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags.
-Secondly, using information from the estimated quadrotor state, a state machine and a set of PID controllers were developed that tracks and lands on a desired target.
+This project can be separated into two individual but complementary components.
+First, a significant effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags.
+Secondly, using information from the estimated quadrotor state, a state machine and a PID position controller were developed to track and lands on a desired target.
 
@@
 \subsubsection{AprilTag Inception}
-
 To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
@@
 
-In order to achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
+To achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
 We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.

### 2016-04-21 docs/report/plot_data/Camera_Plot/AprTag_Plot_Generation.m
added more bullshit

@@ -25,17 +25,17 @@ measured_dist = sqrt((Apr_y).^2 + ...
                 (Apr_z).^2 );
             
 figure(1) %error plot as funct distance
-plot(dist, (dist-measured_dist+0.03), 'bo');
+plot(dist, (dist-measured_dist+0.03), 'b.', 'Markersize', 30);
 set(gca, 'XMinorTick', 'on', ...
           'YMinorTick', 'on', ...
           'FontWeight', 'bold', ...
-          'Fontsize', 12);
+          'Fontsize', 20);
 xlabel('Euclidean Distance Between AprilTag and Camera [meters]',...
-                                    'Fontsize', 15, ...
+                                    'Fontsize', 30, ...
                                     'FontWeight', 'normal');
                                 
-ylabel('Measured Euclidean Distance [meters]',...
-               'Fontsize', 15, ...
+ylabel('Error in Measured Distance [meters]',...
+               'Fontsize', 30, ...
                'FontWeight', 'normal');
 axis([0 3.5 -0.2 0.2]);
 
@@ -49,19 +49,18 @@ axis([0 3.5 -0.2 0.2]);
 %  ylabel('y')
 %  zlabel('z')
 
-
 figure(3)
-plot(FPS_Plotting_x, FrameRate(7:26), '-bo')
+plot(FPS_Plotting_x, FrameRate(7:26), '-b.', 'Markersize', 30, 'linewidth', 2)
 set(gca, 'XMinorTick', 'on', ...
           'YMinorTick', 'on', ...
           'FontWeight', 'bold', ...
-          'Fontsize', 12);
+          'Fontsize', 20);
         
 xlabel('Euclidean Distance Between AprilTag and Camera [meters]',...
-                                    'Fontsize', 15, ...
+                                    'Fontsize', 30, ...
                                     'FontWeight', 'normal');
 ylabel('Frame Rate [Hz]',...
-               'Fontsize', 15, ...
+               'Fontsize', 30, ...
                'FontWeight', 'normal');
 axis([0 3.5 0 35]);
 

### 2016-04-22 docs/report/report.tex
added more bullshit
Update docs

@@
 \subsection{Controller and State Monitoring}
+\label{subsec:position_controller}
 In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
@@
 	\includegraphics[width=0.8\linewidth]{images/quadrotor.jpg}
-	\caption{DJI F450 with Pixhawk v1.5}
+	\caption{DJI F450 with Pixhawk v2.4}
 	\label{Quadrotor}
@@
 \section{Results}
-\begin{itemize}
-	\item Results of the image stuff
-	\begin{itemize}
-		\item Plot of FPS vs distance
-		\item Plot of true state vs mocap state?
-	\end{itemize}
-
-	\item PID/Control results 
-	\begin{itemize}
-		\item Plot XY for the controller loop
-		\item Optimal PID settings
-		\item How we got there
-		\item Decent plot (V as a function of Z)
-		\item Video?
-	\end{itemize}
-
-\end{itemize}
 
@@
 	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
+		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
 		\caption{}
@@
 	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
+		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
 		\caption{}
@@
 
-\subsection{PID and Controller Results}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Pitch_x_true_and_obs.eps}
-	\caption{Position Controller - Pitch Command}
-	\label{fig:pid_roll}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Pitch_Controls.eps}
-	\caption{Position Controller - Pitch Control Signal Components}
-	\label{fig:pid_roll}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Roll_y_true_and_obs.eps}
-	\caption{Position Controller - Roll Command}
-	\label{fig:pid_roll}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Roll_Controls.eps}
-	\caption{Position Controller - Roll Control Signal Components}
-	\label{fig:pid_roll}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Elevation_True_and_obs.eps}
-	\caption{Position Controller - Thrust Command}
-	\label{fig:pid_roll}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=\textwidth]{images/PID_Elevation_Controls.eps}
-	\caption{Position Controller - Thrust Signal Components}
-	\label{fig:pid_roll}
-\end{figure*}
-
-So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.
-
-\section{Conclusion and Future Work}
-
-\section{Proposed Future Work}
-In the coming weeks, the PID controllers tested and developed using the MOCAP system will be tested using state estimates that are produced from the AprilTag library and the image preprocessing methods outlined in section \textbf{\textit{OUTLINE OF IMAGE PREPROCESSSING}}.
+For AprilTag pose estimation we have optimized and tested our solution using the Optitrack motion capture system to compare state estimates produced by our optimization, a demo of the AprilTag pose estimation can be seen in this
+\href{https://www.youtube.com/watch?v=BBMlQphrqCY&index=19&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{video}.
 
@@
 This time lag as outlined in \cite{Ling2014} and defined in \ref{Detection Delay} must be accounted for when using the camera to estimate state.
-Currently our proposed method to measure this lag is to use the MOCAP system to provide a ground truth for the state from which we can estimate the estimated state.
+We measured this lag using Optitrack motion capture system to provide a ground truth for the state from which we can estimate the estimated state.
 
@@
 
+\subsection{PID and Controller Results}
+
+Before implementing our own PID position controller, we initially assumed that we could reuse PX4 firmware's own position controller and feed in the pose estimation of the quadrotor relative to the AprilTag observed using an onboard camera, we however met countless problems with regards to the code required to issue position commands, and instability issues related to the time lag induced when extracting a pose from an AprilTag.
+We therefore implemented our own PID position controller discussed in Section~\ref{subsec:position_controller}, and through many iterations of manually tuning the PID gains we found the following parameters yielded the best control behaviour.
+
+\begin{center}
+	\vspace{-0.4cm}
+	\begin{tabular}{l r}
+		\hline
+		\textbf{Roll Controller} \\
+		\hline
+		$K_{p}$ &  0.205 \\
+		$K_{i}$ & 0.05 \\
+		$K_{d}$ &  0.02 \\
+		\\
+		\hline
+		\textbf{Pitch Controller} \\
+		\hline
+		$K_{p}$ & 0.205 \\
+		$K_{i}$ & 0.05 \\
+		$K_{d}$ & 0.02 \\
+		\\
+		\hline
+		\textbf{Thrust Controller} \\
+		\hline
+		$K_{p}$ & 0.2 \\
+		$K_{i}$ & 0.0 \\
+		$K_{d}$ & 0.02 \\
+	\end{tabular}
+\end{center}
+
+Figures \ref{fig:pid_roll_command} \ref{fig:pid_roll_error},	\ref{fig:pid_pitch_command}, \ref{fig:pid_pitch_error}, \ref{fig:pid_thrust_command}, \ref{fig:pid_thrust_error} showes the PID position control signal (roll, pitch and thrust) and corresponding proportional, integral and derivative error components while a quadrotor was set to hover at $(0, 0, 1)$ for approximately 65 seconds.
+Large disturbances were applied manually to the hovering quadrotor with a testing aparatus (a.k.a a plank of wood) to test the correction behaviour of the position controller implemented.
+
+It can be observed in Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds.
+Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time.
+A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Pitch_x_true_and_obs.eps}
+	\caption{Position Controller - Pitch Command}
+	\label{fig:pid_roll_command}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Pitch_Controls.eps}
+	\caption{Position Controller - Pitch Control Signal Components}
+	\label{fig:pid_roll_error}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Roll_y_true_and_obs.eps}
+	\caption{Position Controller - Roll Command}
+	\label{fig:pid_pitch_command}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Roll_Controls.eps}
+	\caption{Position Controller - Roll Control Signal Components}
+	\label{fig:pid_pitch_error}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Elevation_True_and_obs.eps}
+	\caption{Position Controller - Thrust Command}
+	\label{fig:pid_thrust_command}
+\end{figure*}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=\textwidth]{images/PID_Elevation_Controls.eps}
+	\caption{Position Controller - Thrust Signal Components}
+	\label{fig:pid_thrust_error}
+\end{figure*}
+
+\section{Conclusion and Future Work}
+Due to lack of time, we have not be able to complete the solution to autonomously land a quadrotor onto a moving platform.
+However, we have optimized the AprilTag pose estimation process and implemented our own position controller, what remains is the pose estimation of the quadrotor inbetween the pose estimation of the AprilTag.
+This is needed because even though we can obtain an accurate pose estimate of the quadrotor just by observing the AprilTag with a camera, the quadrotor can easily fly out of the AprilTag's view and lose track its own pose estimate, this is especially dangerous in quadrotors where a pose estimate is vital to its stability and navigation.
+It is our goal in the next coming weeks that we will implement a filter to estimate and combine the AprilTag and position controller to complete the autonomous landing solution.
+
 \bibliography{report}{}
 \bibliographystyle{ieeetr}
-
 \end{document}

### 2016-04-22 docs/report/report.tex
stans updates

--- 2016-04-21 docs/report/report.tex
@@
 
-In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variaty of angles.
+In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variety of angles.
 Overall none of these approach have completely solved the problem and most approaches only work on very slow moving platforms with little or no wind disturbances.
@@
 \subsection{Measurement and State Estimation using AprilTags}
+\label{subsec:AprilTag}
 One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz.
@@
 \subsubsection{AprilTag Inception}
-To address both the decreasing state update rate as a function of proximity and reduce the probablity of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
+To address both the decreasing state update rate as a function of proximity and reduce the probability of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
 This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag.
@@
 Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
-Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just abvove ($\approx 1m$) the landing target inorder to minimize time and energy requirements of the landing maneouver.
+Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just above ($\approx 1m$) the landing target to minimize time and energy requirements of the landing manoeuvre.
 
@@
 
-\section{Experimental Hardware}
-The quadrotor used in this experiment assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers.
-The flight controller selected for the project was a Pixhawk v2.4 running the PX4 firmware stack.
-An Odroid XU4 was selected as the onboard computer to processes captured images from a video stream and sends attitude commands via usb to the Pixhawk based of the PID controllers and current state as outlined above.
-Communication between the Odroid and the Pixhawk is handled by the mavros package which is a wrapper around the popular Mavlink communication protocal for UAVs.
-Video was captured using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels along with a FujiFilm 135 degree FOV lens.
-The quadrotor and camera are highlighted in Figure \ref{Quadrotor}
+\section{Results}
+The methods outlined in sections \ref{subsec:AprilTag} and \ref{subsec:position_controller} were implemented and tested on real quadrotor with an onboard computer and camera.
+The quadrotor is assembled from a DJI F450 quadrotor frame, 4 Emax 2213-935KV motors with complementary DJI E310 420S 20A electronic speed controllers.
+A Pixhawk v2.4 running the PX4 firmware stack was selected for the flight controller and an Odroid XU4 was used as an on-board computer to processes process video captured from a using a PointGrey Firefly 2.0 camera operating 60 frames per second (fps) with a resolution of 640 by 480 pixels through a FuijiFilm 135 degree FOV lens.
+The camera calibration was done using the ROS camera calibration package.
+
+Images captured from the video stream are then processed using the AprilTag library after passing through the preprocessing steps outlined in \ref{subsec:AprilTag} and the estimated state is used by the PID controller (outlined in \ref{subsec:position_controller} and also running on the Odroid) to produce attitude commands that cause the quadrotor to move towards a goal location.
+All attitude commands are send to the Pixhawk from the Odroid via usb and rely heavily on the Mavros package, which is a wrapper around the popular Mavlink communication protocol.
+
+Using this testbed both the accuracy of the AprilTag state estimation was evaluated in the following sections.
+At this point in time a motion capture system was used in place of the AprilTag library to provide state estimates as it was found to be more reliable for initial testing purposes.
+In the coming week the PID controllers will also be tested using only the state estimates from the AprilTag library.
 
@@
 
-\section{Results}
-\begin{itemize}
-	\item Results of the image stuff
-	\begin{itemize}
-		\item Plot of FPS vs distance
-		\item Plot of true state vs mocap state?
-	\end{itemize}
+\subsection{Evaluation of AprilTag Accuracy and Update Rate}
+To evaluate the accuracy of the AprilTag and effects that the adaptive windowing procedures have on the state estimations an Optitrack motion capture system (MOCAP) was used to provide a ground truth.
+By monitoring the pose of both the camera and the AprilTag in the MOCAP system, the series of measurements were taken using the MOCAP system to calculate the pose of the AprilTag relative to the camera from a variety of ranges and angles.
+A comparison between the estimated pose from the AprilTag and the MOCAP system as a function of distance is highlighted in Figure \ref{fig:AprilTag_eval}.
+Figure \ref{fig:AprilTag_eval} also highlights the rate at which state estimates are received from the AprilTag library after being passed through the adaptive windowing procedure.
+A demo of the AprilTag pose estimation can also be seen in this
+\href{https://www.youtube.com/watch?v=BBMlQphrqCY&index=19&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{video}.
 
-	\item PID/Control results 
-	\begin{itemize}
-		\item Plot XY for the controller loop
-		\item Optimal PID settings
-		\item How we got there
-		\item Decent plot (V as a function of Z)
-		\item Video?
-	\end{itemize}
-
-\end{itemize}
-
-\subsection{AprilTag Results}
 \begin{figure}	
@@
 	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
+		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
 		\caption{}
-		\label{fig:pid_roll}
+
 	\end{subfigure}
@@
 	\begin{subfigure}[b]{\linewidth}
-		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
+		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
 		\caption{}
-		\label{fig:pid_roll}
+
 	\end{subfigure}
+	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
+	\label{fig:AprilTag_eval}	
 \end{figure}
 
+From Figure \ref{fig:AprilTag_eval} it appears that the average error of the estimated euclidean distance compared to MOCAP ground truth is within approximately $\pm 20 cm$ for any measurements between 0 and 3 meters.
+Due to the limited range of the MOCAP system distances greater than 3 m between the camera and the AprilTag were not tested.
+The system was also able to maintain a frame rate of approximately 30 fps in cases camera is less then 2 meters away from the AprilTag while producing estimates with an error within approximately $\pm 0.05 cm$.
+In future, an analysis of the sources of error in Figure \ref{fig:AprilTag_eval} will be conducted as well as evaluation of the error as a function of angle between the AprilTag and the camera.
+
+It is suspected that the PointGrey Camera used in this test was not operating at the requested frame rate of 60 fps.
+This was not noted until after analysising the data and will be investigated this coming week.
+In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resting the frame rate from 30 fps to 60 fps with no warning or indication.
+If this is the case, then the update rate of the AprilTag library on the Odroid may actually be faster than what is shown in Figure \ref{fig:AprilTag_eval}.
+In cases where a more powerful computer can be used, the adaptive image processing method results in the AprilTag library operating at 60 fps with no delay, making it extremely useful on machines that can leverage greater computational power.
+
 \subsection{PID and Controller Results}
+The PID controllers dervied in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system.
+Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted.
+After a signifcant amount of testing the following values for the proportional, derivitave and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers.
+Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests.
+
+\begin{center}
+	\vspace{-0.4cm}
+	\begin{tabular}{l r}
+		\hline
+		\textbf{Roll Controller} \\
+		\hline
+		$K_{p}$ &  0.205 \\
+		$K_{i}$ & 0.05 \\
+		$K_{d}$ &  0.02 \\
+		\\
+		\hline
+		\textbf{Pitch Controller} \\
+		\hline
+		$K_{p}$ & 0.205 \\
+		$K_{i}$ & 0.05 \\
+		$K_{d}$ & 0.02 \\
+		\\
+		\hline
+		\textbf{Thrust Controller} \\
+		\hline
+		$K_{p}$ & 0.2 \\
+		$K_{i}$ & 0.0 \\
+		$K_{d}$ & 0.02 \\
+	\end{tabular}
+\end{center}
+
+Figures \ref{fig:pid_roll_command} \ref{fig:pid_roll_error},	\ref{fig:pid_pitch_command}, \ref{fig:pid_pitch_error}, \ref{fig:pid_thrust_command}, \ref{fig:pid_thrust_error} higlight the PID position control signal (roll, pitch and thrust) and corresponding proportional, integral and derivative error components while a quadrotor was set to hover at $(0, 0, 1)$ for approximately 65 seconds.
+Large disturbances were applied manually to the hovering quadrotor with a testing apparatus (a plank of wood) to test the correction behaviour of the position controller implemented.
+These disturbances are applied at the 15, 21, 37, and 57 second marks in all six Figures.
+In the case of the elevation controller, there was no integral term used due to the risk of a suck throttle occurring in cases where the quadrotor did not detect landing and tack off correctly.
+
+From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds.
+Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time.
+A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.
+
+In all cases there is a significant amount of noise on the derivative error term as highlighted in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}.
+It is suspected that this large error is due to the small time step of 0.01 seconds used in the calculation of the derivative term which has side effect of greatly amplifying any noise in the MOCAP state estimations.
+In cases where the MOCAP measurement did not correctly correspond to the current true state of the vehicle large spikes can be noted which appears around the 9 second mark in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}.
+The noise in the MOCAP system can be reduced by adding additional markers to the quad and by making a more rigid frame to mount the tracking markers.
+
+These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments.
+Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees.
+Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag.
+Such a test will be the focus of the majority of effort in the coming weeks.
 
@@
 	\caption{Position Controller - Pitch Command}
-	\label{fig:pid_roll}
+	\label{fig:pid_roll_command}
 \end{figure*}
@@
 	\caption{Position Controller - Pitch Control Signal Components}
-	\label{fig:pid_roll}
+	\label{fig:pid_roll_error}
 \end{figure*}
@@
 	\caption{Position Controller - Roll Command}
-	\label{fig:pid_roll}
+	\label{fig:pid_pitch_command}
 \end{figure*}
@@
 	\caption{Position Controller - Roll Control Signal Components}
-	\label{fig:pid_roll}
+	\label{fig:pid_pitch_error}
 \end{figure*}
@@
 	\caption{Position Controller - Thrust Command}
-	\label{fig:pid_roll}
+	\label{fig:pid_thrust_command}
 \end{figure*}
@@
 	\caption{Position Controller - Thrust Signal Components}
-	\label{fig:pid_roll}
+	\label{fig:pid_thrust_error}
 \end{figure*}
 
-So far the PID behaviours and gains have only been evaluated using a MOCAP system and tested only relative to a stationary target and these results are discussed herein.
+\section{Conclusions and Future Work}
+A set of algorithms were developed to provide fast, reliable and accurate estimations of state between a landing pad and a quadrotor using a series of image preprocessing methods and the MIT AprilTags library.
+These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power onboard, quadrotor mounted computer system.
+A set of PID controllers were developed, tested and evaluated using the same motion capture system to provide state estimates and a ground truth.
+A set of stable yet responsive PID gains were found and tested using this system and an evaluation of their behaviour in the presence of large disturbances was conducted.
 
-\section{Conclusion and Future Work}
-
-\section{Proposed Future Work}
-In the coming weeks, the PID controllers tested and developed using the MOCAP system will be tested using state estimates that are produced from the AprilTag library and the image preprocessing methods outlined in section \textbf{\textit{OUTLINE OF IMAGE PREPROCESSSING}}.
-
-One major issue highlighted in Ling \cite{Ling2014} is that due to the relatively long processing time of the AprilTags library, the estimated state obtained at a time $t$ does not actually represent the current state due to a time lag.
-This time lag as outlined in \cite{Ling2014} and defined in \ref{Detection Delay} must be accounted for when using the camera to estimate state.
-Currently our proposed method to measure this lag is to use the MOCAP system to provide a ground truth for the state from which we can estimate the estimated state.
-
-\begin{equation}
-\label{Detection Delay}
-    t_{\text{capture}} = t - \delta t_{\text{camera}} + \delta t_{\text{detection}}
-\end{equation}
-
-The next issue that will need to be address is the problem of the camera view.
-The dynamics of a quadrotor work in such a way that in order to move towards a goal point, the quadrotor must tilt away from the target which leads to problems with maintaining a view of the target when desired roll or pitch angles are greater than approximately 10 degress.
-This issue can either be addressed by mounting the camera at an angle or by adding a gimbals to the the quadrotor such that the gimbal will be sent commands by the onboard computer that will maintain a constant view of the target regardless of the commanded roll and pitch.
-
-Both of the above solutions have significant implementation questions that will have to be answered.
-If using the fixed camera angle, then the yaw of the qaudrotor will need to be controlled by a PID controller, similar to the the PID controllers to the roll and pitch.
-In the case of significant wind, the quadrotor will need to rotate itself such that the front of the quad is pointed into the wind during the final decent.
-
-If a gimbal is used there are two issues that arise.
-First a new set of controllers that send roll, pitch and yaw commands to the gimbal such that the camera it is attached to maintains a centred view of the target platform must be developed.
-These controllers will likely be similar to the PID controllers developed above and so they are not considered to be terrible difficult to define are implement.
-The more difficult part of using a gimbal is related to resuming the gimbal state, which in cheaper gimbals do provide.
-All of the gimbals that have been researched as part of this project do not provide state feedback and so they are considered to be open loop.
-Therefore in order to use such a gimbal the user will need to assume the commanded gimbal position is equal to the true gimbal position, from which a transform between the quad rotor and the gimbal can be made.
+In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure.
+Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
 
@@
 \bibliographystyle{ieeetr}
-
 \end{document}

### 2016-04-22 docs/report/report.tex
more edits to related work

@@
 
-For perception existing solutions use a variety of simple to complex techniques.
-In \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.
+From the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor.
+In the work of Kim, 2014 \cite{Kim2014} a basic color threshold technique was to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide the state estimations.
+In the work of Heriesse Et al.
+\cite{Herisse2012} an optical flow technique was applied to a series of images captured on board the quadrotor to estimate the require state estimation in order to control the quad rotor and conduct autonomous landing.
+While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting there general applicability.
 
-A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}.
-However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
+In the case of Ling \cite{Kim2014}, the brightness used in his thresholding techquie must be set ahead of time and is sensitve to lighting changes and a similar issue is noted in the work of Heriesse \cite{Herisse2012}.
+Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed.
+This means that as the quadrotor approach the landing pad, it tends to lose any measurements of its state and therefore must complete the final landing procedure by propagating the last measured state forward.
+
+From the controls perspective the majority of literature either uses a set of PID or a Linear Quadratic Controller (LQC) controllers to command and control the quadrotor at all stages of flight based on the state estimation provided by the perception techniques.
+An LQC was thoroughly explored in \cite{Friis2009} but the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
 In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement.

### 2016-04-22 docs/report/report.tex
Minor edits

@@
 Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory.
-Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.
+Once the quadrotor has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.
 
@@
 \cite{Herisse2012} an optical flow technique was applied to a series of images captured on board the quadrotor to estimate the require state estimation in order to control the quad rotor and conduct autonomous landing.
-While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting there general applicability.
+While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting their general applicability.
 
 In the case of Ling \cite{Kim2014}, the brightness used in his thresholding techquie must be set ahead of time and is sensitve to lighting changes and a similar issue is noted in the work of Heriesse \cite{Herisse2012}.
-Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed.
+There are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed.
 This means that as the quadrotor approach the landing pad, it tends to lose any measurements of its state and therefore must complete the final landing procedure by propagating the last measured state forward.
@@
 		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
-		\caption{}
-
 	\end{subfigure}
@@
 		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
-		\caption{}
-
 	\end{subfigure}
@@
 This was not noted until after analysising the data and will be investigated this coming week.
-In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resting the frame rate from 30 fps to 60 fps with no warning or indication.
+In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resetting frame rate from 30 fps to 60 fps with no warning or indication.
 If this is the case, then the update rate of the AprilTag library on the Odroid may actually be faster than what is shown in Figure \ref{fig:AprilTag_eval}.
@@
 
-From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds.
+From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} the roll and pitch commands were bounded to $\pm 20^o$, further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds.
 Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time.
@@
 
-These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments.
+These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered too aggressive for the quadrotor used in these experiments.
 Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees.
-Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag.
-Such a test will be the focus of the majority of effort in the coming weeks.
+Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag target.
 
@@
 A set of algorithms were developed to provide fast, reliable and accurate estimations of state between a landing pad and a quadrotor using a series of image preprocessing methods and the MIT AprilTags library.
-These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power onboard, quadrotor mounted computer system.
+These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power, onboard quadrotor mounted computer system.
 A set of PID controllers were developed, tested and evaluated using the same motion capture system to provide state estimates and a ground truth.
@@
 In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure.
-Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
+Once such a landing can be performed consistently in the face of minor disturbances, the same procedure will be applied to a quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
 

### 2016-04-22 docs/report/report.tex
updates again

--- 2016-04-22 docs/report/report.tex
@@
 \section{Introduction}
-Over the years there has been been a growing interest in autonomous landing of quadrotors as landing is often one of the most dangerous and risk prone parts of flight.
-There are now several commercial and research based implementations of autonomous landing with the DJI Phantom and Pixhawk flight controller both being capable of automatic landing using a series of sensors and control algorithms.
-However there does not yet seem to be a reliable method of landing a quadrotor on either a moving platform or in cases where there is relatively large cross wind disturbance.
+Over the years there has been a growing interest in autonomous landing of quadrotors, as landing is often one of the most dangerous and risk prone parts of flight.
+There are now several commercial and research based implementations of autonomous landing with both the DJI Phantom and Pixhawk flight controllers being capable of automatic landing using a series control algorithms.
+However, there does not appear to be a reliable method of landing a quadrotor on either a moving platform or in relatively large wind disturbances.
 
-In recent years there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variety of angles.
-Overall none of these approach have completely solved the problem and most approaches only work on very slow moving platforms with little or no wind disturbances.
+In recent years.
+there have been at least least 5 academic publications on the topic \cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that approach the problem from a variety of angles.
+Overall none of these approach have completely solved the problem and most approaches only work on slow moving platforms with little or no wind disturbances.
 
-One of the most challenging parts with autonomous landing is the difficulty of obtaining a reliable estimate of the landing target relative to the quadrotor, the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target, other vision based artifacts that include lighting, lens distortion, color, etc.
-In many cases GPS is not a viable option both the landing target and the quadrotor due to the lack of accuracy unless an RTK GPS system is used.
-In many cases the use of an RTK system is not a readily available option due to cost or quadrotor needs.
+One of the most challenging problems associated with autonomous landing is the difficulty of obtaining a reliable state estimate of the landing target relative to the quadrotor.
+This is due to the fact that the landing target can often go out of the camera's field of view causing the quadrotor to lose track of the target or measurements can become corrupted by vision based artifacts that include lighting, lens distortion, color, etc.
+In many cases GPS is not a viable option both the landing target and the quadrotor due a lack of accuracy unless an RTK GPS system is used.
+In many cases the use of an RTK system is not a readily available option due to cost and the lack of required equipment.
 
@@
 
-For perception existing solutions use a variety of simple to complex techniques.
-In \cite{Kim2014} a basic color threshold technique was to identify the landing target, while \cite{Herisse2012} used optical flow in images captured on board the quadrotor to obtain necessary relative information for control.
+For the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor.
+In the work of Kim, 2014 \cite{Kim2014} a basic color thresholding technique was used to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide state estimations.
+In the work of Heriesse Et al.
+\cite{Herisse2012} an optical flow technique was applied to a series of images captured on-board the quadrotor to estimate the required states required to control the quadrotor and conduct autonomous landing.
+While both of these techniques have been shown to work in very specific cases both, require case specific parameters to be applied ahead of time, thereby limiting there general applicability.
 
-A comparison between a PID and Linear Quadratic Control (LQC) was explored in \cite{Friis2009}.
-However the authors admit, even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
-In \cite{Herisse2012} a PID controller was developed to land on a oscillating platform in the vertical direction with no lateral movement.
+In the case of Ling \cite{Kim2014}, the brightness used in his thresholding technique must be set ahead of time and is sensitive to lighting changes.
+A similar issue is noted in the work of Heriesse \cite{Herisse2012}.
+Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and, the AprilTag falling out of view of the camera during the final stages of decent.
+This meant that as the quadrotor approach the landing pad, it tended to lose any measurements of its state and therefore had complete the final landing procedure by propagating the last measured state forward in time.
+
+From the controls perspective the majority of literature either uses a set of PID or a Linear Quadratic Controller (LQC) controllers to command and control the quadrotor at all stages of flight based on the state estimation provided by the techniques discussed above.
+An LQC was thoroughly explored in Friis Et al.
+\cite{Friis2009} but the authors admit even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
+In \cite{Herisse2012}, a PID controller was developed to land on a vertically oscillating platform no lateral movement.
 While interesting, the solution took over 1 minute to transition from hovering over the landing pad to landing.
@@
 
-In this project we focus developing a set of controllers that produce the final landing trajectory and using a fiducial marker called an AprilTags \cite{apriltags} to provide the estimated state of the quadrotor relative to the landing pad.
+In this project we focus developing a set of controllers that produce the final landing trajectory and using a  AprilTags \cite{apriltags} to provide the estimated state of the quadrotor relative to the landing pad.
+We seek to develop both a more robust and rapid method of determining the state of the quadrotor and landing pad system and to develop a set of PID controllers that can be used to control the quadrotor based on the measured state information.
 
 \section{Methodology}
-This project can be separated into two individual but complementary components.
-First, a significant effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20Hz with AprilTags.
+This project was be separated into two individual, but complementary components.
+First, a significant effort was spent on ensuring the quadrotor's state was estimated at a rate of at least 20 Hz with AprilTags.
 Secondly, using information from the estimated quadrotor state, a state machine and a PID position controller were developed to track and lands on a desired target.
@@
 \label{subsec:AprilTag}
-One of the challenges we faced when estimating the quadrotor state using AprilTags was the computational resource required to sustain a rate of atleast 20hz.
-This problem is exacerbated when the image size increases, as do the computational time needed to extract the pose estimate of the AprilTag, from our initial experimentation the computational time grows exponentially as image size increases as shown in (add a figure here).
+One of the challenges faced when estimating the quadrotor state using AprilTags was the computational resources required to sustain a rate of atleast 20 Hz.
 This problem was also noted in the work of \cite{Ling2014} where he addressed the issue by reducing the brightness of the image so that the majority of the image is black except for the AprilTag, thus reducing image processing requirements.
-An example of this implementation is shown in Figure~\ref{fig:ling_apriltags} This allowed Ling \cite{Lee2012} to calculate states at a rate of approximatly 10 - 15 fps but it came at the cost of requiring the brightness parameters to be set ahead of time and also the lost of robustness in estimating the AprilTags.
+An example of this implementation is shown in Figure~\ref{fig:ling_apriltags}.
+This allowed Ling \cite{Lee2012} to calculate states at a rate of approximately 10 - 15 Hz, but it came at the cost of requiring the brightness parameters to be set ahead of time and also the removed a large portion of robustness techniques normally included in the AprilTag library.
 
@@
 
-In this work, the slow rate of state estimation was addressed using two novel ideas.
+In this work, the slow rate of state estimation was addressed using three novel ideas.
 First, the image size and calibration parameters are set depending on the distance between the quadrotor's position relative to the AprilTag.
 Secondly, we introduce the use of a Region of Interest (ROI) window to focus only on the AprilTag to reduce computational time required to estimate the pose.
-These novel ideas will be discussed in the following subsections.
+Thirdly, we embed a smaller AprilTag into a larger one that is used to provide state estimates when the distance to the landing pad is quite small (2 meters).
 
 \subsubsection{Adaptive Image Preprocessing}
-
-As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on a Snapdragon 8 core processor, which is too low to be used effectively in a PID control loop.
-Building upon the work of \cite{Ling2014}, who improved the AprilTag estimation rate by reducing the brightness on the image such that the majority of the pixels are black, additionally a set of image preprocessing methods such as Canny-Edge thresholding were also used.
+As discussed previously, the low rate of the AprilTag library when processing images of 640 by 480 pixels results in an update rate of approximately 3 to 5 fps on the small on-board computers used on the target quadrotor, which is too low to be utilized effectively in a PID controller.
+Building upon the work of \cite{Ling2014}, who improved the AprilTag estimation rate by reducing the brightness on the image such that the majority of the pixels are black.
 
 \subsubsection{Adaptive Image Windowing}
-
-If one assumes that the quadrotor does not move to fast, there is relativity low rotation between image captures, and that the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
-Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to segment out portions of the image where the AprilTag is unlikely to be.
+If one assumes that the quadrotor does not move too fast, there is relativity low rotation between captured images, and the image update rate is quite fast (60 fps in this implementation), then the location the AprilTag in the following image can be estimated based off of the location it was last observed in the previous image.
+Therefore whenever an AprilTag is measured in an image, a bounding box around the AprilTag is calculated and then used in the following image to blackout out portions of the image where the AprilTag is unlikely to be.
 An example of this implementation is highlighted in Figure \ref{fig:apriltags_windowing}.
@@
 
-While the adaptive windowing procedure decreases the computational resources needed for extracting pose estimates, there are two other problems that windowing cannot solve.
+While the adaptive windowing procedure decreases the computational resources needed for extracting pose estimates, there are two additional problems that windowing cannot solve.
 First, as the size of the observed Apriltag increases, windowing is no longer adequate in decreasing computational time, this is an issue in cases where a high update rate is required (e.g.
 quadrotor landing).
-Second, in our use case as the observed AprilTag gets larger it becomes easy for the camera to lose track of the AprilTag itself, increasing the risk of no estimation for that time.
+Second, as the observed AprilTag gets larger it becomes easy for the camera to lose track of the AprilTag itself, increasing the risk of no estimation for that time.
+Both of these problems are addressed by embedding a smaller AprilTag into the larger one.
 
@@
 To address both the decreasing state update rate as a function of proximity and reduce the probability of losing sight of the AprilTag during landing a secondary AprilTag is embedded in the larger AprilTag, we term this technique AprilTag Inception (patent pending).
-This secondary AprilTag is assigned with a different family id to avoid confusion during detection, and is placed at the center of the larger primary AprilTag.
+This secondary AprilTag is assigned different family ID to avoid confusion during detection, and is placed at the center of the larger primary AprilTag.
 Whenever the secondary AprilTag is captured in the image, the adaptive windowing method is set to track only the secondary AprilTag rather than the larger one, which reduces the portion of the image that must be processed in with each image capture.
@@
 \subsubsection{Adaptive Image Down-sampling}
-A final technique used to optimize the AprilTag detection was the introduction of down sampling the image size as the estimated distance between camera and AprilTag decreases.
-We devised 2 image down sampling sizes $320 \times 280$ (half resolution) and $160 \times 140$ (quarter resolution), when the distance between the camera and the AprilTag is less than 1.5 and 3 meters, the images are down sampled to the two resolutions respectively.
+The final technique used to optimize the AprilTag detection was the introduction of down sampling the image size as the estimated distance between camera and AprilTag decreased.
+In this work two image down sampling sizes $320 \times 280$ (half resolution) and $160 \times 140$ (quarter resolution), were used.
+Whenever the distance between the camera and the AprilTag is less than 1.5 and 3 meters, the images are down sampled to the two resolutions respectively.
 If the camera is further than 3 meters from the AprilTag, the native resolution of $640 \times 480$ is used.
@@
 
-In order to use down sampling effectively without corrupting the AprilTag estimations, 3 camera calibration files were also computed at the full, half and quarter camera resolutions, corresponding calibration files were then used with the AprilTag library during the state estimation procedure based on the current image resolution to obtain the correct pose estimates.
-
 \subsection{Controller and State Monitoring}
 \label{subsec:position_controller}
-In this project we assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
-The first step towards autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
-Next, while maintaining the near zero displacements in the x and y directions, the quadrotor descends at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
+In this project it is assumed that the quadrotor has successfully rendezvoused with the target vehicle and has a clear view through the camera image of the landing target located on the target vehicle at all times.
+The first step in autonomous landing is to position the quadrotor above the landing target such that the displacements in the x and y directions in the horizontal plane normal to the landing surface are near zero while simultaneously matching speed and aligning the axis with the target vehicle.
+Next, while maintaining the near zero displacements in the x and y directions, the quadrotor must descend at a safe rate such that the vertical distance between the quadrotor and the landing target is reduced until landing is achieved.
 Ideally the quadrotor will descend rapidly when the vertical displacement between the qaudrotor and target is large, slowing down just above ($\approx 1m$) the landing target to minimize time and energy requirements of the landing manoeuvre.
 
-To achieve the described behaviour, we developed a PID position controller that outputs attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, as well as an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
-We omit yaw control as we assume the quadrotor will be axis aligned with the direction of travel of the moving target.
+To achieve the described behaviour, a set of PID position controllers were developed that output attitude commands such as roll and pitch to reduce the horizontal and vertical distance between the quadrotor and the landing platform, along with an altitude command to maintain a safe approach altitude such that the target does not go out of view during landing.
+Yaw control is omitted in the following work and is assumed to be axis aligned with the direction of travel of the moving target at all stages of decent and tracking.
 
-The position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, these inputs are mapped to attitude and altitude commands in the roll $\hat{\phi_t}$, pitch $\hat{\theta_t}$ and thrust $\hat{T_z}$ relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}, these equations however assume that yaw $\psi$ is 0, if yaw is non-zero then roll and pitch need to be adjusted to account for the yaw changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}.
+The derived position controller takes the quadrotor's desired position and current position in $x$, $y$ and $z$ of the world frame as inputs, which are then mapped to attitude and altitude commands in the roll $\hat{\phi_t}$, pitch $\hat{\theta_t}$ and thrust $\hat{T_z}$ relative to the quadrotor frame as outlined in Equations \ref{eq:pid_roll}, \ref{eq:pid_pitch}, \ref{eq:pid_thrust}, these equations as written assume that yaw $\psi$ is 0.
+In the case that the yaw is non-zero, then roll and pitch need to be adjusted to account for the yaw changes as in Equation \ref{eq:pid_roll_adjusted} and \ref{eq:pid_pitch_adjusted}.
 The altitude command is adjusted when roll $\hat{\phi}$ and pitch $\hat{\theta}$ are non-zero to maintain altitude as in Equation \ref{eq:pid_thrust_adjusted}.
@@
 	\label{eq:pid_pitch}
-	\hat{\theta_t} = K_p e_y + K_i \sum_{t = 0}^{t} \dot{e}_{y,t} dt + K_d \dot{e}_{y ,t}
+	\hat{\theta_t} = K_p e_y + K_i \sum_{t = 0}^{t} e_{y,t} dt + K_d \dot{e}_{y ,t}
 \end{equation}
@@
 	\hat{T_z} =
-		K_p e_z + K_i \sum_{t=0}^{t} \dot{e_z}_{,t} dt + K_d \dot{e_z}_{,t} 
+		K_p e_z + K_i \sum_{t=0}^{t} e_{z,t} dt + K_d \dot{e_z}_{,t} 
 \end{equation}
@@
 It is suspected that the PointGrey Camera used in this test was not operating at the requested frame rate of 60 fps.
-This was not noted until after analysising the data and will be investigated this coming week.
+This was not noted until after analysing the data and will be investigated this coming week.
 In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resting the frame rate from 30 fps to 60 fps with no warning or indication.
@@
 \subsection{PID and Controller Results}
-The PID controllers dervied in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system.
+The PID controllers derived in section \ref{subsec:position_controller} were tested on the quadrotor using the MOCAP system.
 Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted.
-After a signifcant amount of testing the following values for the proportional, derivitave and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers.
+After a signifcant amount of testing the following values for the proportional, derivative and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers.
 Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests.
+The commanded roll and pitch attitude commands produced by the PID controllers was also limited to $\pm 20^0$ for safety.
 
@@
 
-Figures \ref{fig:pid_roll_command} \ref{fig:pid_roll_error},	\ref{fig:pid_pitch_command}, \ref{fig:pid_pitch_error}, \ref{fig:pid_thrust_command}, \ref{fig:pid_thrust_error} higlight the PID position control signal (roll, pitch and thrust) and corresponding proportional, integral and derivative error components while a quadrotor was set to hover at $(0, 0, 1)$ for approximately 65 seconds.
+Figures \ref{fig:pid_roll_command} \ref{fig:pid_roll_error},	\ref{fig:pid_pitch_command}, \ref{fig:pid_pitch_error}, \ref{fig:pid_thrust_command}, \ref{fig:pid_thrust_error} highlight the PID position control signal (roll, pitch and thrust) and corresponding proportional, integral and derivative error components while a quadrotor was set to hover at $(0, 0, 1)$ for approximately 65 seconds.
 Large disturbances were applied manually to the hovering quadrotor with a testing apparatus (a plank of wood) to test the correction behaviour of the position controller implemented.
@@
 
-From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds.
-Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time.
-A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.
+From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command}, when the quadrotor is perturbed by a disturbance in teh horizontal plane, the position controller is able recover and return to the set point within 2-4 seconds.
+A video of flight that produced the dataset shown in \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.
 
-In all cases there is a significant amount of noise on the derivative error term as highlighted in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}.
+In all cases there was significant amount of noise on the derivative error term as highlighted in Figures \ref{fig:pid_roll_error}, \ref{fig:pid_pitch_error}, and \ref{fig:pid_thrust_error}.
 It is suspected that this large error is due to the small time step of 0.01 seconds used in the calculation of the derivative term which has side effect of greatly amplifying any noise in the MOCAP state estimations.

### 2016-04-26 docs/report/report.tex

@@
 \begin{document}
+\raggedbottom
 
@@
 In the work of Kim, 2014 \cite{Kim2014} a basic color thresholding technique was used to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide state estimations.
-In the work of Heriesse Et al.
-\cite{Herisse2012} an optical flow technique was applied to a series of images captured on-board the quadrotor to estimate the required states required to control the quadrotor and conduct autonomous landing.
+In the work of Heriesse Et al., 2012 \cite{Herisse2012} an optical flow technique was applied to a series of images captured on-board the quadrotor to estimate the required states required to control the quadrotor and conduct autonomous landing.
 While both of these techniques have been shown to work in very specific cases both, require case specific parameters to be applied ahead of time, thereby limiting there general applicability.
 
-In the case of Ling \cite{Kim2014}, the brightness used in his thresholding technique must be set ahead of time and is sensitive to lighting changes.
-A similar issue is noted in the work of Heriesse \cite{Herisse2012}.
-Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and, the AprilTag falling out of view of the camera during the final stages of decent.
-This meant that as the quadrotor approach the landing pad, it tended to lose any measurements of its state and therefore had complete the final landing procedure by propagating the last measured state forward in time.
+In the case of Ling, 2014 \cite{Kim2014}, the brightness used in his thresholding technique must be set ahead of time and is sensitive to lighting changes.
+A similar issue is noted in the work of Heriesse Et al., 2012 \cite{Herisse2012}.
+Moreover in the work of Ling, there were implementation issues due to the slow state estimation rate of the AprilTag library and the AprilTag falling out of view of the camera during the final stages of decent.
+This meant that as the quadrotor approached the landing pad it tended to lose any measurements of its state and therefore had complete the final landing procedure by propagating the last measured state forward in time.
 
-From the controls perspective the majority of literature either uses a set of PID or a Linear Quadratic Controller (LQC) controllers to command and control the quadrotor at all stages of flight based on the state estimation provided by the techniques discussed above.
-An LQC was thoroughly explored in Friis Et al.
-\cite{Friis2009} but the authors admit even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
+Examining the related literature on the controllers used in solving the the autonomous landing problem, the majority of literature either uses a set of PID or a Linear Quadratic Controllers (LQC) to command and control the quadrotor at all stages of flight.
+A LQC was thoroughly explored in Friis Et al., 2009 \cite{Friis2009} but the authors admit even though LQC performed slightly better than the PID controller the difference was minor and may be attributed to the additional time spent tuning the LQC.
 In \cite{Herisse2012}, a PID controller was developed to land on a vertically oscillating platform no lateral movement.
@@
 		\caption{}		
-
 	\end{subfigure}
@@
 Due to time constraints evaluation of the PID controller was only conducted using the MOCAP system to provide state estimates, but in the coming week further tests using the AprilTag system will be conducted.
-After a signifcant amount of testing the following values for the proportional, derivative and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers.
+After a significant amount of testing the following values for the proportional, derivative and integral gains ($K_p, K_d, K_i$) were determined for the roll, pitch and height controllers.
 Using state information from the MOCAP system, the yaw of the quadrotor was fixed at zero degrees for all of the following tests.
@@
 
-From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command}, when the quadrotor is perturbed by a disturbance in teh horizontal plane, the position controller is able recover and return to the set point within 2-4 seconds.
+From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command}, when the quadrotor is perturbed by a disturbance in the horizontal plane, the position controller is able recover and return to the set point within 2-4 seconds.
 A video of flight that produced the dataset shown in \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.
@@
 Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag.
-Such a test will be the focus of the majority of effort in the coming weeks.
 
@@
 In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure.
-Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
+Once such a landing can be performed consistently in the face of minor disturbances, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
 

### 2017-01-24 awesomo_core/src/vision/camera/pointgrey.cpp
Update image settings for ROSbagging a SVO data set

@@ -148,13 +148,13 @@ int PointGreyCamera::setFormat7(void) {
   FlyCapture2::Format7PacketInfo fmt7PacketInfo;
   bool valid;
 
-  k_fmt7PixFmt = FlyCapture2::PIXEL_FORMAT_BGR;
+  k_fmt7PixFmt = FlyCapture2::PIXEL_FORMAT_RAW8;
 
-  fmt7_image_settings.mode = FlyCapture2::MODE_1;
-  fmt7_image_settings.offsetX = 200;
-  fmt7_image_settings.offsetY = 144;
-  fmt7_image_settings.width = 624;
-  fmt7_image_settings.height = 420;
+  fmt7_image_settings.mode = FlyCapture2::MODE_0;
+  fmt7_image_settings.offsetX = 380;
+  fmt7_image_settings.offsetY = 298;
+  fmt7_image_settings.width = 1264;
+  fmt7_image_settings.height = 930;
   fmt7_image_settings.pixelFormat = k_fmt7PixFmt;
 
 

### 2017-01-24 docs/paper/paper.tex

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts                                                              
\overrideIEEEmargins  % required to meet printer requirements.

% DOCUMENT STRUCTURE
\usepackage{subfiles}

% TABLES
\usepackage{caption}
\usepackage{multirow}

% ALGORITHMS
\usepackage{algorithmic}
\usepackage{algorithm}

% GRAPHICS
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{tikzscale}
%\usepackage{tkzgraph}
\usetikzlibrary{matrix}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{calc}
\usepackage{graphicx}
\usepackage{hyperref}

% MATH SYMBOLS
\usepackage{amsfonts} % mathbb{R}
\usepackage{amsmath}
\DeclareMathOperator*{\argmin}{arg\,min}

% COMMENT BLOCKS
\usepackage{verbatim}

% SUBSCRIPT COMMANDS 
\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
\newcommand{\subscript}[1]{\ensuremath{_\textrm{#1}}}

% TITLE
\title{\large{\textbf{Autonomous Landing of a Quadrotor on a Moving Platform in Outdoor Environments}}}

% AUTHORS
\author{
Chris Choi\authorrefmark{1} Stanley Brown\authorrefmark{2} and  Steven L. Waslander\authorrefmark{3}
\thanks{\superscript{*} M.A.Sc. Candidate, Mechanical and Mechatronics Engineering, University of Waterloo; c33choi@uwaterloo.ca}
\thanks{\superscript{2} M.A.Sc. Candidate, Mechanical and Mechatronics Engineering, University of Waterloo; s52brown@uwaterloo.ca}
\thanks{\superscript{\dag} Assistant Professor, Mechanical and Mechatronics Engineering, University of Waterloo; stevenw@uwaterloo.ca}
\vspace{0.5in}
}

\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

% ABSTRACT
\begin{abstract}
The task of landing an aircraft on moving objects has been a topic of interest ever since humans took to the skies in the early twentieth century. Typically when attempting landing small, Micro UAVs such as quadrotors, the landing procedure is either done manually, or using GPS guidance to land on a stationary target. If landing on a moving target or in high wind conditions, a human operator is generally required. However this requires the human operator to have a clear line of site to both the target and the aircraft during all stages of the landing procedure. In recent years there have been several papers that propose a set of methods for landing on a slow moving platform in ideal conditions such as low wind and ideal GPS signals with little or no noise. Our contribution in this work is the demonstration of a set of algorithms that allow a quadrotor to perform a autonomous landing on a car traveling at over 20 meters per second while relying only on visual inertial data collected from and on-board gimbaled camera system. From this image data, along with on-board IMU readings, it is shown that both speed of the target and the quadrotor in the inertial frame can be directly estimated, and using this information a set of controllers and planners can be developed that allows for the quadrotor to perform a high speed landing maneuver in a variety of conditions. The robustness of our system is demonstrated by landing in without using GPS, poorly lit conditions, and with high winds. 
\end{abstract}

% INTRODUCTION
\section{Introduction}

% RELATED WORK
\section{Related Work}

% PROBELM FORMULATION
\section{Problem Formulation}

% SYSTEM ARCHITECTURE
\section{System Architecture}

% EXPERIMENT RESULTS
\section{Experiment Results}

% CONCLUSIONS
\section{Conclusions and Future Work}

\bibliography{paper}

\end{document}

### 2017-01-25 docs/paper/paper.tex
Add NLOpt example

@@
+% DOCUMENT CLASS
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}
@@
 % TITLE
-\title{\large{\textbf{Autonomous Landing of a Quadrotor on a Moving Platform in Outdoor Environments}}}
+\title{\large \textbf Autonomous Landing of a Quadrotor on a Moving Platform in
+Outdoor Environments}
 
 % AUTHORS
-\author{
+\author{\
 Chris Choi\authorrefmark{1} Stanley Brown\authorrefmark{2} and  Steven L. Waslander\authorrefmark{3}
@@
 \begin{abstract}
-The task of landing an aircraft on moving objects has been a topic of interest ever since humans took to the skies in the early twentieth century.
-Typically when attempting landing small, Micro UAVs such as quadrotors, the landing procedure is either done manually, or using GPS guidance to land on a stationary target.
-If landing on a moving target or in high wind conditions, a human operator is generally required.
-However this requires the human operator to have a clear line of site to both the target and the aircraft during all stages of the landing procedure.
-In recent years there have been several papers that propose a set of methods for landing on a slow moving platform in ideal conditions such as low wind and ideal GPS signals with little or no noise.
-Our contribution in this work is the demonstration of a set of algorithms that allow a quadrotor to perform a autonomous landing on a car traveling at over 20 meters per second while relying only on visual inertial data collected from and on-board gimbaled camera system.
-From this image data, along with on-board IMU readings, it is shown that both speed of the target and the quadrotor in the inertial frame can be directly estimated, and using this information a set of controllers and planners can be developed that allows for the quadrotor to perform a high speed landing maneuver in a variety of conditions.
-The robustness of our system is demonstrated by landing in without using GPS, poorly lit conditions, and with high winds.
+The task of landing an aircraft on moving objects has been a topic of interest
+ever since humans took to the skies in the early twentieth century. Typically
+when attempting landing small, Micro UAVs such as quadrotors, the landing
+procedure is either done manually, or using GPS guidance to land on a
+stationary target. If landing on a moving target or in high wind conditions, a
+human operator is generally required. However this requires the human operator
+to have a clear line of site to both the target and the aircraft during all
+stages of the landing procedure. In recent years there have been several papers
+that propose a set of methods for landing on a slow moving platform in ideal
+conditions such as low wind and ideal GPS signals with little or no noise. Our
+contribution in this work is the demonstration of a set of algorithms that
+allow a quadrotor to perform a autonomous landing on a car travelling at over 20
+meters per second while relying only on visual inertial data collected from and
+on-board gimbaled camera system. From this image data, along with on-board IMU
+readings, it is shown that both speed of the target and the quadrotor in the
+inertial frame can be directly estimated, and using this information a set of
+controllers and planners can be developed that allows for the quadrotor to
+perform a high speed landing manoeuvre in a variety of conditions. The
+robustness of our system is demonstrated by landing in without using GPS,
+poorly lit conditions, and with high winds.
 \end{abstract}
@@
 
-% PROBELM FORMULATION
+% CONTRIBUTION
+\section{Contribution}
+
+\begin{itemize}
+  \item{Robust Landing}
+  \item{AprilTag estimation with Kalman Filter}
+  \item{Light Invariant AprilTag detection}
+  \item{AprilTag windowing to speed up detection}
+\end{itemize}
+
+% PROBLEM FORMULATION
 \section{Problem Formulation}
+
+% CAMERA TRANSFORMS
+\section{Camera Transforms}
+
+% GIMBAL TRANSFORMS
+\section{Gimbal Transforms}
+
+% LIGHT INVARIANT
+\section{Light Invariant}
+
+% APRILTAG ESTIMATION
+\section{AprilTag Estimation}
 

### 2017-01-25 awesomo_core/tests/planning/optimizer_test.cpp

@@ -1,0 +1,13 @@
+#include "awesomo_core/awesomo_test.hpp"
+#include "awesomo_core/planning/optimizer.hpp"
+
+namespace awesomo {
+
+TEST(POpt, test) {
+  POpt popt;
+
+  popt.run();
+  ASSERT_TRUE(true);
+}
+
+}  // end of awesomo namespace

### 2017-01-25 docs/paper/paper.tex
Update docs

@@
 \author{\
-Chris Choi\authorrefmark{1} Stanley Brown\authorrefmark{2} and  Steven L. Waslander\authorrefmark{3}
+Chris Choi\authorrefmark{1}, Stanley Brown\authorrefmark{2} and  Steven L. Waslander\authorrefmark{3}
 \thanks{\superscript{*} M.A.Sc. Candidate, Mechanical and Mechatronics Engineering, University of Waterloo; c33choi@uwaterloo.ca}
@@
 \section{Introduction}
+Over the years there has been a growing interest in autonomous landing of
+quadrotors, as landing is often one of the most dangerous and risk prone parts
+of flight. There are now several commercial and research based implementations
+of autonomous landing with both the DJI Phantom and Pixhawk flight controllers
+being capable of automatic landing using a series control algorithms. However,
+there does not appear to be a reliable method of landing a quadrotor on either
+a moving platform or in relatively large wind disturbances.
+
+In recent years there have been at least least 5 academic publications on the
+topic~\cite{Lee2012, Kim2014, Voos2010, Friis2009, Ling2014, Herisse2012} that
+approach the problem from a variety of angles. Overall none of these approach
+have completely solved the problem and most approaches only work on slow moving
+platforms with little or no wind disturbances.
+
+One of the most challenging problems associated with autonomous landing is the
+difficulty of obtaining a reliable state estimate of the landing target
+relative to the quadrotor. This is due to the fact that the landing target can
+often go out of the camera's field of view causing the quadrotor to lose track
+of the target or measurements can become corrupted by vision based artifacts
+that include lighting, lens distortion, color, etc. In many cases GPS is not a
+viable option both the landing target and the quadrotor due a lack of accuracy
+unless an RTK GPS system is used. In many cases the use of an RTK system is not
+a readily available option due to cost and the lack of required equipment.
 
@@
 \section{Related Work}
+The autonomous landing problem can be thought of as a set of three separate
+control problems or stages. First the quadrotor must detect the relative
+position and velocity of the landing target using either GPS of visual methods.
+Next the quadrotor must determine a rendezvous location with the landing target
+and plan the required flight trajectory. Once the quadrotor has rendezvoused a
+final landing trajectory must be calculated between quadrotor and the landing
+pad.
+
+For the perception portion of the problem there have been two main techniques
+use to identify the landing pad and estimate its state relative to the
+quadrotor. In the work of Kim, 2014~\cite{Kim2014} a basic colour thresholding
+technique was used to identify the landing target and the MIT AprilTags library
+\cite{apriltags} was used to provide state estimations. In the work of Heriesse
+Et al., 2012~\cite{Herisse2012} an optical flow technique was applied to a
+series of images captured on-board the quadrotor to estimate the required
+states required to control the quadrotor and conduct autonomous landing. While
+both of these techniques have been shown to work in very specific cases both,
+require case specific parameters to be applied ahead of time, thereby limiting
+there general applicability.
+
+In the case of Ling, 2014~\cite{Kim2014}, the brightness used in his
+thresholding technique must be set ahead of time and is sensitive to lighting
+changes. A similar issue is noted in the work of Heriesse Et al., 2012
+\cite{Herisse2012}. Moreover in the work of Ling, there were implementation
+issues due to the slow state estimation rate of the AprilTag library and the
+AprilTag falling out of view of the camera during the final stages of decent.
+This meant that as the quadrotor approached the landing pad it tended to lose
+any measurements of its state and therefore had complete the final landing
+procedure by propagating the last measured state forward in time.
+
+Examining the related literature on the controllers used in solving the the
+autonomous landing problem, the majority of literature either uses a set of PID
+or a Linear Quadratic Controllers (LQC) to command and control the quadrotor at
+all stages of flight. A LQC was thoroughly explored in Friis Et al., 2009
+\cite{Friis2009} but the authors admit even though LQC performed slightly
+better than the PID controller the difference was minor and may be attributed
+to the additional time spent tuning the LQC\@. In~\cite{Herisse2012}, a PID
+controller was developed to land on a vertically oscillating platform no
+lateral movement. While interesting, the solution took over 1 minute to
+transition from hovering over the landing pad to landing. Additionally the
+experiments did not seem to account for pitch or roll of the platform.
+
+In this project we focus developing a set of controllers that produce the final
+landing trajectory and using a  AprilTags~\cite{apriltags} to provide the
+estimated state of the quadrotor relative to the landing pad. We seek to
+develop both a more robust and rapid method of determining the state of the
+quadrotor and landing pad system and to develop a set of PID controllers that
+can be used to control the quadrotor based on the measured state information.
 
@@
   \item{AprilTag estimation with Kalman Filter}
+  \item{AprilTag windowing to speed up detection}
   \item{Light Invariant AprilTag detection}
-  \item{AprilTag windowing to speed up detection}
+  \item{Tracking Controller}
+  \item{Trajectory Planning}
 \end{itemize}
@@
 
-% LIGHT INVARIANT
-\section{Light Invariant}
+% LANDING TARGET ESTIMATION
+\section{Landing Target Estimation}
 
-% APRILTAG ESTIMATION
-\section{AprilTag Estimation}
+Kalman Filter constant acceleration
+
+\subsection{Adaptive Image Processing}
+As discussed previously, the low rate of the AprilTag library when processing
+images of 640 by 480 pixels results in an update rate of approximately 3 to 5
+fps on the on-board computers used on the target quadrotor, which is too low to
+be used for controlling the quadrotor. Building upon who improved the AprilTag
+estimation rate by reducing the brightness of the image  such that the majority
+of the image is black, we implemented an adaptive down sampling of the image size
+as the estimated distance between camera and AprilTag decreased. In this work
+two image down sampling sizes $320 \times 280$ (half resolution) and $160
+\times 140$ (quarter resolution), were used. Whenever the distance between the
+camera and the AprilTag is less than 1.5 and 3 meters, the images are down
+sampled to the two resolutions respectively. If the camera is further than 3
+meters from the AprilTag, the native resolution of $640 \times 480$ is used.
+This change only affected the image processing time when the quadrotor is
+within 3 meters of the quad and has the desired effect of maintaining a high
+AprilTag estimation rate.
+
+\subsection{Adaptive Image Windowing}
+If the AprilTag in the image space does not translate too suddenly, one can
+make the assumption that the previous detected AprilTag will approximately be
+in the same approximate image coordinates. A bounding box around the AprilTag
+can be formed and used to feed into the AprilTag detector.
+
+\subsection{AprilTag Inception}
+To address both the decreasing state update rate as a function of proximity and
+reduce the probability of losing sight of the AprilTag during landing a
+secondary AprilTag is embedded in the larger AprilTag, we term this technique
+AprilTag Inception (patent pending). This secondary AprilTag is assigned
+different family ID to avoid confusion during detection, and is placed at the
+center of the larger primary AprilTag. Whenever the secondary AprilTag is
+captured in the image, the adaptive windowing method is set to track only the
+secondary AprilTag rather than the larger one, which reduces the portion of the
+image that must be processed in with each image capture. An example of this
+procedure is highlighted in Figure.
+
+\section{Light Invariant AprilTag}
+
+% QUADROTOR CONTROL
+\section{Quadrotor Control}
 

### 2017-01-25 awesomo_core/include/awesomo_core/planning/trajectory.hpp
Add quadrotor_2d_model()

@@ -1,0 +1,11 @@
+#ifndef __AWESOMO_PLANNING_TRAJECTORY_HPP__
+#define __AWESOMO_PLANNING_TRAJECTORY_HPP__
+
+#include "awesomo_core/utils/utils.hpp"
+
+namespace awesomo {
+
+VecX quadrotor_2d_model(VecX x, Vec2 u);
+
+}  // end of awesomo namespace
+#endif

### 2017-01-25 awesomo_core/src/planning/trajectory.cpp

@@ -1,0 +1,47 @@
+#include "awesomo_core/planning/trajectory.hpp"
+
+
+namespace awesomo {
+
+// Vec2 quadrotor_calculate_inputs(double mass, double thrust, double omega) {
+//   Vec2 u;
+//
+//   u(0) = thrust / mass;
+//   u(1) = omega;
+//
+//   return u;
+// }
+
+VecX quadrotor_2d_model(VecX x, Vec2 u) {
+  const double k_gravity = 9.81;
+
+  // x1 - x
+  // x2 - z
+  // x3 - vx
+  // x4 - vz
+  // x5 - theta (pitch)
+
+  x(0) = x(0) + x(1);
+  x(1) = x(1) + u(0) * sin(x(4));
+  x(2) = x(2) + x(3);
+  x(3) = x(3) + u(0) * cos(x(4)) - k_gravity;
+  x(4) = x(4) + u(1);
+
+  return x;
+}
+
+// double input1_constraint(const std::vector<double> &x,
+//                          std::vector<double> &grad,
+//                          void *data) {
+//
+//
+// }
+//
+// double input2_constraint(const std::vector<double> &x,
+//                          std::vector<double> &grad,
+//                          void *data) {
+//
+//
+// }
+
+}  // end of awesomo namespace

### 2017-01-25 awesomo_core/tests/planning/optimizer_test.cpp

@@ -10,4 +10,5 @@ TEST(POpt, test) {
   ASSERT_TRUE(true);
 }
 
+
 }  // end of awesomo namespace

### 2017-01-25 awesomo_core/tests/planning/trajectory_test.cpp

@@ -1,0 +1,58 @@
+#include "awesomo_core/awesomo_test.hpp"
+#include "awesomo_core/planning/trajectory.hpp"
+
+#define TEST_TRAJECTORY_OUTPUT_FILE "/tmp/trajectory.output"
+
+
+namespace awesomo {
+
+static int setup_output_file(std::ofstream &output_file,
+                             std::string output_path) {
+  output_file.open(output_path);
+
+  output_file << "time_step" << ",";
+  output_file << "x" << ",";
+  output_file << "z" << ",";
+  output_file << "theta" << "\n";
+
+  return 0;
+}
+
+static void record_time_step(std::ofstream &output_file,
+                             int i,
+                             VecX x) {
+  // record true state x, z
+  output_file << i << ",";
+  output_file << x(0) << ",";
+  output_file << x(2) << ",";
+  output_file << x(4) << "\n";
+}
+
+TEST(Trajectory, quadrotor_2d_model) {
+  double dt;
+  VecX x(5);
+  Vec2 u;
+  std::ofstream output_file;
+
+  // setup
+  dt = 0.1;
+  setup_output_file(output_file, TEST_TRAJECTORY_OUTPUT_FILE);
+
+  // initial state
+  x(0) = 0.0;
+  x(1) = 0.0;
+  x(2) = 0.0;
+  x(3) = 0.0;
+  x(4) = 0.0;
+
+  // initial inputs
+  u(0) = 9.85;
+  u(1) = 0.0;
+
+  for (int i = 1; i < 10; i++) {
+    x = quadrotor_2d_model(x, u);
+    record_time_step(output_file, i, x);
+  }
+}
+
+}  // end of awesomo namespace

### 2017-01-25 scripts/plot_trajectory.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python2
+import csv
+import matplotlib.pylab as plt
+
+# GLOBAL VARIABLES
+trajectory_output = "/tmp/trajectory.output"
+
+
+def plot_data(data_file):
+    f = open(data_file, "r")
+    reader = csv.reader(f, delimiter=",")
+    next(reader)  # skip header
+
+    data = {
+        "timestep": [],
+        "x": [],
+        "z": []
+    }
+
+    for row in reader:
+        data["timestep"].append(float(row[0]))
+        data["x"].append(float(row[1]))
+        data["z"].append(float(row[2]))
+
+    plt.plot(data["x"], data["z"])
+    plt.show()
+
+
+if __name__ == "__main__":
+    plot_data(trajectory_output)

### 2017-01-25 awesomo_core/include/awesomo_core/planning/trajectory.hpp
Start implementation on trajectory generator

@@ -5,7 +5,41 @@
 
 namespace awesomo {
 
+typedef struct {
+  // input constraints
+  double thrust_min;
+  double thrust_max;
+
+  double angular_rate_min;
+  double angular_rate_max;
+
+  // feasible region constraints
+  double feasible_thrust_min;
+  double feasible_thrust_max;
+
+  double feasible_angular_rate_min;
+  double feasible_angular_rate_max;
+
+} trajectory_constraints;
+
+typedef struct {
+  int nb_states;
+  int nb_time_steps;
+  double time_taken;
+
+  Vec3 state_initial;
+  Vec3 state_final;
+  std::vector<Vec2> desired_trajectory;
+
+} trajectory_data;
+
+Vec2 quadrotor_calculate_inputs(double mass, double thrust, double omega);
 VecX quadrotor_2d_model(VecX x, Vec2 u);
+int trajectory_problem_dimensions(int nb_states, int nb_timesteps);
+int trajectory_sampling_time(double time_taken, int nb_steps);
+std::vector<Vec2> trajectory_desired_path(Vec2 pos_init,
+                                          Vec2 pos_final,
+                                          int nb_steps);
 
 }  // end of awesomo namespace
 #endif

### 2017-01-25 awesomo_core/src/planning/trajectory.cpp

@@ -3,14 +3,14 @@
 
 namespace awesomo {
 
-// Vec2 quadrotor_calculate_inputs(double mass, double thrust, double omega) {
-//   Vec2 u;
-//
-//   u(0) = thrust / mass;
-//   u(1) = omega;
-//
-//   return u;
-// }
+Vec2 quadrotor_calculate_inputs(double mass, double thrust, double omega) {
+  Vec2 u;
+
+  u(0) = thrust / mass;
+  u(1) = omega;
+
+  return u;
+}
 
 VecX quadrotor_2d_model(VecX x, Vec2 u) {
   const double k_gravity = 9.81;
@@ -30,18 +30,69 @@ VecX quadrotor_2d_model(VecX x, Vec2 u) {
   return x;
 }
 
-// double input1_constraint(const std::vector<double> &x,
-//                          std::vector<double> &grad,
-//                          void *data) {
-//
-//
-// }
-//
-// double input2_constraint(const std::vector<double> &x,
-//                          std::vector<double> &grad,
-//                          void *data) {
-//
-//
-// }
+int trajectory_problem_dimensions(int nb_states, int nb_timesteps) {
+  return nb_states * nb_timesteps;
+}
+
+int trajectory_sampling_time(double time_taken, int nb_steps) {
+  return (time_taken) / ((double) nb_steps - 1);
+}
+
+std::vector<Vec2> trajectory_desired_path(Vec2 pos_init,
+                                          Vec2 pos_final,
+                                          int nb_steps) {
+  double dx;
+  Vec2 point;
+  double m, c;
+  std::vector<Vec2> desired_path;
+
+  // calculate line equation, gradient and intersect
+  m = (pos_init(1) - pos_final(1)) / (pos_init(0) - pos_final(0));
+  c = pos_init(1) - m * pos_init(0);
+
+  // create points along the desired line path
+  dx = (pos_final(0) - pos_init(0)) / (double) (nb_steps - 1);
+  desired_path.push_back(pos_init);
+  for (int i = 0; i < (nb_steps - 2); i++) {
+    point = desired_path.back();
+    point(0) += dx;
+    point(1) = m * point(0) + c;
+    desired_path.push_back(point);
+  }
+  desired_path.push_back(pos_final);
+
+  return desired_path;
+}
+
+double trajectory_cost_func(const std::vector<double> &x,
[…]

### 2017-01-25 awesomo_core/tests/planning/trajectory_test.cpp

@@ -2,30 +2,39 @@
 #include "awesomo_core/planning/trajectory.hpp"
 
 #define TEST_TRAJECTORY_OUTPUT_FILE "/tmp/trajectory.output"
+#define TEST_PATH_OUTPUT_FILE "/tmp/path.output"
 
 
 namespace awesomo {
 
-static int setup_output_file(std::ofstream &output_file,
-                             std::string output_path) {
+static int trajectory_file_init(std::ofstream &output_file,
+                                std::string output_path) {
   output_file.open(output_path);
-
   output_file << "time_step" << ",";
   output_file << "x" << ",";
   output_file << "z" << ",";
   output_file << "theta" << "\n";
-
   return 0;
 }
 
-static void record_time_step(std::ofstream &output_file,
-                             int i,
-                             VecX x) {
-  // record true state x, z
+static void record_time_step(std::ofstream &output_file, int i, VecX x) {
   output_file << i << ",";
   output_file << x(0) << ",";
   output_file << x(2) << ",";
   output_file << x(4) << "\n";
+}
+
+static int path_file_init(std::ofstream &output_file,
+                                std::string output_path) {
+  output_file.open(output_path);
+  output_file << "x" << ",";
+  output_file << "z" << "\n";
+  return 0;
+}
+
+static void record_path(std::ofstream &output_file, Vec2 path) {
+  output_file << path(0) << ",";
+  output_file << path(1) << "\n";
 }
 
 TEST(Trajectory, quadrotor_2d_model) {
@@ -36,7 +45,7 @@ TEST(Trajectory, quadrotor_2d_model) {
 
   // setup
   dt = 0.1;
-  setup_output_file(output_file, TEST_TRAJECTORY_OUTPUT_FILE);
+  trajectory_file_init(output_file, TEST_TRAJECTORY_OUTPUT_FILE);
 
   // initial state
   x(0) = 0.0;
@@ -53,6 +62,38 @@ TEST(Trajectory, quadrotor_2d_model) {
     x = quadrotor_2d_model(x, u);
     record_time_step(output_file, i, x);
   }
+
+  // clean up
+  output_file.close();
+}
+
+TEST(Trajectory, trajectory_desired_path) {
+  Vec2 pos_init, pos_final;
+  int nb_steps;
+  std::vector<Vec2> desired_path;
[…]

### 2017-01-25 awesomo_core/tests/utils/data_test.cpp

@@ -19,7 +19,7 @@ TEST(Pose, checkPose) {
   ASSERT_FLOAT_EQ(0.0, testPose.orientation.x());
   ASSERT_FLOAT_EQ(0.0, testPose.orientation.y());
   ASSERT_FLOAT_EQ(0.0, testPose.orientation.z());
-  ASSERT_FLOAT_EQ(1.0, testPose.orientation.w());
+  ASSERT_FLOAT_EQ(0.0, testPose.orientation.w());
 
   ASSERT_FLOAT_EQ(0.0, testPose.position(0));
   ASSERT_FLOAT_EQ(0.0, testPose.position(1));

### 2017-01-25 scripts/plot_trajectory.py

@@ -4,9 +4,10 @@ import matplotlib.pylab as plt
 
 # GLOBAL VARIABLES
 trajectory_output = "/tmp/trajectory.output"
+path_output = "/tmp/path.output"
 
 
-def plot_data(data_file):
+def plot_trajectory(data_file):
     f = open(data_file, "r")
     reader = csv.reader(f, delimiter=",")
     next(reader)  # skip header
@@ -26,5 +27,24 @@ def plot_data(data_file):
     plt.show()
 
 
+def plot_path(data_file):
+    f = open(data_file, "r")
+    reader = csv.reader(f, delimiter=",")
+    next(reader)  # skip header
+
+    data = {
+        "x": [],
+        "z": []
+    }
+
+    for row in reader:
+        data["x"].append(float(row[0]))
+        data["z"].append(float(row[1]))
+
+    plt.plot(data["x"], data["z"])
+    plt.show()
+
+
 if __name__ == "__main__":
-    plot_data(trajectory_output)
+    # plot_trajectory(trajectory_output)
+    plot_path(path_output)

### 2017-02-01 awesomo_core/src/vision/camera/pointgrey.cpp
Update PG camera and PG camera node, and rename topics to match prototype conventions

@@ -32,7 +32,6 @@ int PointGreyCamera::initialize() {
     return -1;
   }
 
-
   error = this->pointgrey->Connect(&guid);
   if (error != FlyCapture2::PGRERROR_OK) {
     log_err("ERROR! Failed to connect to camera!");
@@ -42,9 +41,9 @@ int PointGreyCamera::initialize() {
   }
 
   // this->printFormat7Capabilities();
-  this->setFormat7("raw8", 640, 480, 0);
+  // this->setFormat7("raw8", 640, 480, 0); // make these not hard coded
 
-  // set video mode format and frame rate USB 2.0 cameras
+  // set video mode format and frame RRRR USB 2.0 cameras
   // error = this->pointgrey->SetVideoModeAndFrameRate(
   //   FlyCapture2::VIDEOMODE_640x480Y8, FlyCapture2::FRAMERATE_60);
   // if (error != FlyCapture2::PGRERROR_OK) {
@@ -57,6 +56,7 @@ int PointGreyCamera::initialize() {
   this->setExposure(this->config.exposure_value);
   this->setGain(this->config.gain_value);
   this->setFrameRate(200);
+  this->setFormat7("RAW8", 640 * 2, 480 * 2, 0); // make these not hard coded
 
   // start camera
   error = this->pointgrey->StartCapture();
@@ -105,10 +105,9 @@ int PointGreyCamera::getFrame(cv::Mat &image) {
 
   // resize the image to reflect camera mode
   // clang-format off
-  // image_size = cv::Size(this->current_config->image_width,
-  //                       this->current_config->image_height);
-  // image_size = cv::Size(480, 320);
-  // cv::resize(image, image, image_size);
+  image_size = cv::Size(this->config.image_width,
+                        this->config.image_height);
+  cv::resize(image, image, image_size);
   // clang-format on
 
   return 0;
@@ -124,19 +123,20 @@ int PointGreyCamera::setFormat7(std::string pixel_format, int crop_width, int cr
   int max_image_width;
   int max_image_height;
 
-
-  if (pixel_format == "MONO8") {
-    fmt7_settings.pixelFormat = FlyCapture2::PIXEL_FORMAT_MONO8;
-  }
-  else if (pixel_format == "MONO16") {
[…]

### 2017-02-01 awesomo_ros/include/awesomo_ros/nodes/camera_node.hpp

@@ -26,13 +26,17 @@ namespace awesomo {
 #define GIMBAL_JOINT_ORIENTATION_TOPIC "/awesomo/gimbal/joint/orientation/inertial"
 #define SHUTDOWN_TOPIC "/awesomo/camera/shutdown"
 
+#define TARGET_BPF_POS_TOPIC "/awesomo/apriltag/target/position/body"
+
 class CameraNode : public ROSNode {
 public:
   Camera camera;
   cv::Mat image;
 
-  Quaternion gimbal_frame;
-  Quaternion gimbal_joint;
+  Quaternion gimbal_frame_orientation;
+  Quaternion gimbal_joint_orientation;
+  Vec3 gimbal_position;
+  Vec3 target_bpf;
 
   CameraNode(int argc, char **argv) : ROSNode(argc, argv) {}
   int configure(std::string node_name, int hz);
@@ -40,6 +44,7 @@ public:
   void imageCallback(const sensor_msgs::ImageConstPtr &msg);
   void gimbalFrameCallback(const geometry_msgs::Quaternion &msg);
   void gimbalJointCallback(const geometry_msgs::Quaternion &msg);
+  void aprilTagCallback(const geometry_msgs::Vector3 &msg);
   int loopCallback(void);
 };
 

### 2017-02-01 awesomo_ros/include/awesomo_ros/nodes/gimbal_node.hpp

@@ -17,11 +17,17 @@ namespace awesomo {
 #define NODE_RATE 100
 
 // PUBLISH TOPICS
-#define FRAME_RPY_TOPIC "/awesomo/gimbal/frame/orientiation/inertial"
 #define CAMERA_IMU_TOPIC "/awesomo/gimbal/joint/imu"
+#define FRAME_ORIENTATION_TOPIC "/awesomo/gimbal/frame/orientation/inertial"
+#define JOINT_ORIENTATION_TOPIC "/awesomo/gimbal/joint/orientation/inertial"
+#define POSITION_TOPIC "/awesomo/gimbal/position/inertial"
+
 
 // SUBSCRIBE TOPICS
-#define SET_ATTITUDE_TOPIC "/awesomo/gimbal/setpoint/attitude"
+#define SETPOINT_TOPIC "/awesomo/gimbal/setpoint/attitude"
+#define TRACK_TOPIC "/awesomo/gimbal/target/track"
+#define QUAD_POSE_TOPIC "/mavros/local_position/pose"
+
 #define SHUTDOWN_TOPIC "/awesomo/gimbal/shutdown"
 
 
@@ -32,7 +38,9 @@ public:
   GimbalNode(int argc, char **argv) : ROSNode(argc, argv) {}
   ~GimbalNode(void);
   int configure(std::string node_name, int hz);
+  void quadPoseCallback(const geometry_msgs::PoseStamped &msg);
   void setAttitudeCallback(const geometry_msgs::Vector3 &msg);
+  void trackTargetCallback(const geometry_msgs::Vector3 &msg);
   int loopCallback(void);
 };
 

### 2017-02-01 awesomo_ros/include/awesomo_ros/nodes/pg_camera_node.hpp

@@ -1,5 +1,5 @@
-#ifndef __AWESOMO_ROS_NODES_CAMERA_NODE_HPP__
-#define __AWESOMO_ROS_NODES_CAMERA_NODE_HPP__
+#ifndef __AWESOMO_ROS_NODES_PG_CAMERA_NODE_HPP__
+#define __AWESOMO_ROS_NODES_PG_CAMERA_NODE_HPP__
 
 #include <ros/ros.h>
 #include <cv_bridge/cv_bridge.h>
@@ -16,7 +16,7 @@ namespace awesomo {
 
 // NODE SETTINGS
 #define NODE_NAME "awesomo_camera"
-#define NODE_RATE 110
+#define NODE_RATE 100
 
 // PUBLISH TOPICS
 #define CAMERA_IMAGE_TOPIC "/awesomo/camera/image"
@@ -26,13 +26,17 @@ namespace awesomo {
 #define GIMBAL_JOINT_ORIENTATION_TOPIC "/awesomo/gimbal/joint/orientation/inertial"
 #define SHUTDOWN_TOPIC "/awesomo/camera/shutdown"
 
+#define TARGET_BPF_POS_TOPIC "/awesomo/apriltag/target/position/body"
+
 class PGCameraNode : public ROSNode {
 public:
   PointGreyCamera camera;
   cv::Mat image;
 
-  Quaternion gimbal_frame;
-  Quaternion gimbal_joint;
+  Quaternion gimbal_frame_orientation;
+  Quaternion gimbal_joint_orientation;
+  Vec3 gimbal_position;
+  Vec3 target_bpf;
 
   PGCameraNode(int argc, char **argv) : ROSNode(argc, argv) {}
   int configure(std::string node_name, int hz);
@@ -40,6 +44,7 @@ public:
   void imageCallback(const sensor_msgs::ImageConstPtr &msg);
   void gimbalFrameCallback(const geometry_msgs::Quaternion &msg);
   void gimbalJointCallback(const geometry_msgs::Quaternion &msg);
+  void aprilTagCallback(const geometry_msgs::Vector3 &msg);
   int loopCallback(void);
 };
 

### 2017-02-01 awesomo_ros/src/ros/nodes/camera_node.cpp

@@ -22,6 +22,7 @@ int CameraNode::configure(std::string node_name, int hz) {
   this->registerImagePublisher(CAMERA_IMAGE_TOPIC);
   this->registerSubscriber(GIMBAL_FRAME_ORIENTATION_TOPIC, &CameraNode::gimbalFrameCallback, this);
   this->registerSubscriber(GIMBAL_JOINT_ORIENTATION_TOPIC, &CameraNode::gimbalJointCallback, this);
+  this->registerSubscriber(TARGET_BPF_POS_TOPIC , &CameraNode::aprilTagCallback, this);
   // this->registerShutdown(SHUTDOWN_TOPIC);
 
   // register loop callback
@@ -33,6 +34,24 @@ int CameraNode::configure(std::string node_name, int hz) {
 
 int CameraNode::publishImage(void) {
   sensor_msgs::ImageConstPtr img_msg;
+
+
+  // encode position and orientation into image (first 11 pixels in first row)
+  // if (this->gimbal_mode) {
+  this->image.at<double>(0, 0) = this->gimbal_position(0);
+  this->image.at<double>(0, 1) = this->gimbal_position(1);
+  this->image.at<double>(0, 2) = this->gimbal_position(2);
+
+  this->image.at<double>(0, 3) = this->gimbal_frame_orientation.w();
+  this->image.at<double>(0, 4) = this->gimbal_frame_orientation.x();
+  this->image.at<double>(0, 5) = this->gimbal_frame_orientation.y();
+  this->image.at<double>(0, 6) = this->gimbal_frame_orientation.z();
+
+  this->image.at<double>(0, 7) = this->gimbal_joint_orientation.w();
+  this->image.at<double>(0, 8) = this->gimbal_joint_orientation.x();
+  this->image.at<double>(0, 9) = this->gimbal_joint_orientation.y();
+  this->image.at<double>(0, 10) = this->gimbal_joint_orientation.z();
+  // }
 
   // clang-format off
   img_msg = cv_bridge::CvImage(
@@ -47,22 +66,37 @@ int CameraNode::publishImage(void) {
 }
 
 void CameraNode::gimbalFrameCallback(const geometry_msgs::Quaternion &msg) {
-  this->gimbal_frame.w() = msg.w;
-  this->gimbal_frame.x() = msg.x;
-  this->gimbal_frame.y() = msg.y;
-  this->gimbal_frame.z() = msg.z;
[…]

### 2017-02-01 awesomo_ros/src/ros/nodes/gimbal_node.cpp

@@ -20,8 +20,12 @@ int GimbalNode::configure(std::string node_name, int hz) {
   // register publisher and subscribers
   // clang-format off
   this->registerPublisher<sensor_msgs::Imu>(CAMERA_IMU_TOPIC);
-  this->registerPublisher<geometry_msgs::Quaternion>(FRAME_RPY_TOPIC);
-  this->registerSubscriber(SET_ATTITUDE_TOPIC, &GimbalNode::setAttitudeCallback, this);
+  this->registerPublisher<geometry_msgs::Quaternion>(FRAME_ORIENTATION_TOPIC);
+  this->registerPublisher<geometry_msgs::Quaternion>(JOINT_ORIENTATION_TOPIC);
+
+  this->registerSubscriber(QUAD_POSE_TOPIC, &GimbalNode::quadPoseCallback, this);
+  this->registerSubscriber(TRACK_TOPIC, &GimbalNode::trackTargetCallback, this);
+  this->registerSubscriber(SETPOINT_TOPIC, &GimbalNode::setAttitudeCallback, this);
   this->registerShutdown(SHUTDOWN_TOPIC);
   // clang-format on
 
@@ -41,10 +45,27 @@ void GimbalNode::setAttitudeCallback(const geometry_msgs::Vector3 &msg) {
   this->gimbal.setAngle(msg.x, msg.y);
 }
 
+void GimbalNode::trackTargetCallback(const geometry_msgs::Vector3 &msg) {
+  Eigen::Vector3d target_cf;
+  target_cf << msg.x, msg.y, msg.z;
+  this->gimbal.trackTarget(target_cf);
+}
+
+void GimbalNode::quadPoseCallback(const geometry_msgs::PoseStamped &msg) {
+  geometry_msgs::Vector3 ros_msg;
+
+  ros_msg.x = msg.pose.position.x;
+  ros_msg.y = msg.pose.position.y;
+  ros_msg.z = msg.pose.position.z;
+
+  this->ros_pubs[POSITION_TOPIC].publish(ros_msg);
+}
+
 int GimbalNode::loopCallback(void) {
    int retval;
    sensor_msgs::Imu cam_imu_msg;
    geometry_msgs::Quaternion frame_angles_msg;
+   geometry_msgs::Quaternion cam_angles_msg;
 
    Vec3 camera_euler;
    Vec3 frame_euler;
[…]

### 2017-02-01 awesomo_ros/src/ros/nodes/pg_camera_node.cpp

@@ -13,7 +13,7 @@ int PGCameraNode::configure(std::string node_name, int hz) {
   // camera
   this->ros_nh->getParam("/camera_config_dir", config_path);
   if (this->camera.configure(config_path) != 0) {
-    ROS_ERROR("Failed to configure Camera!");
+    ROS_ERROR("Failed to configure PGCamera!");
     return -2;
   };
   this->camera.initialize();
@@ -22,6 +22,7 @@ int PGCameraNode::configure(std::string node_name, int hz) {
   this->registerImagePublisher(CAMERA_IMAGE_TOPIC);
   this->registerSubscriber(GIMBAL_FRAME_ORIENTATION_TOPIC, &PGCameraNode::gimbalFrameCallback, this);
   this->registerSubscriber(GIMBAL_JOINT_ORIENTATION_TOPIC, &PGCameraNode::gimbalJointCallback, this);
+  this->registerSubscriber(TARGET_BPF_POS_TOPIC , &PGCameraNode::aprilTagCallback, this);
   // this->registerShutdown(SHUTDOWN_TOPIC);
 
   // register loop callback
@@ -33,16 +34,30 @@ int PGCameraNode::configure(std::string node_name, int hz) {
 
 int PGCameraNode::publishImage(void) {
   sensor_msgs::ImageConstPtr img_msg;
-  cv::Mat grey;
-  // cv::cvtColor(image, grey, CV_BGR2GRAY);
 
-  std_msgs::Header header;
-  header.stamp = ros::Time::now();
+
+  // encode position and orientation into image (first 11 pixels in first row)
+  // if (this->gimbal_mode) {
+  this->image.at<double>(0, 0) = this->gimbal_position(0);
+  this->image.at<double>(0, 1) = this->gimbal_position(1);
+  this->image.at<double>(0, 2) = this->gimbal_position(2);
+
+  this->image.at<double>(0, 3) = this->gimbal_frame_orientation.w();
+  this->image.at<double>(0, 4) = this->gimbal_frame_orientation.x();
+  this->image.at<double>(0, 5) = this->gimbal_frame_orientation.y();
+  this->image.at<double>(0, 6) = this->gimbal_frame_orientation.z();
+
+  this->image.at<double>(0, 7) = this->gimbal_joint_orientation.w();
+  this->image.at<double>(0, 8) = this->gimbal_joint_orientation.x();
[…]

### 2017-02-01 awesomo_core/include/awesomo_core/vision/camera/pointgrey.hpp
update launch files and fix segfault in pg camera object

@@ -23,6 +23,7 @@ public:
   int setExposure(double exposure);
   int setGain(double gain);
   int printFormat7Capabilities(void);
+  int changeMode(std::string mode);
 };
 
 }  // end of awesomo namespace

### 2017-02-01 awesomo_core/src/vision/camera/pointgrey.cpp

@@ -181,6 +181,16 @@ int PointGreyCamera::setFormat7(std::string pixel_format,
   return 0;
 }
 
+int PointGreyCamera::changeMode(std::string mode) {
+  // pre-check
+  if (this->configs.find(mode) == this->configs.end()) {
+    return -1;
+  }
+  // update camera settings
+  this->config = this->configs[mode];
+  return 0;
+}
+
 int PointGreyCamera::setFrameRate(double frame_rate) {
   FlyCapture2::Error error;
   FlyCapture2::Property fps_prop;

### 2017-02-01 awesomo_ros/src/ros/nodes/pg_camera_node.cpp

@@ -87,12 +87,12 @@ int PGCameraNode::loopCallback(void) {
   double dist;
   // change mode depending on aprTag distance
   dist = this->target_bpf.norm();
-  if (dist > 8.0) {
-    this->camera.changeMode("640x640");
+  if (dist > 8.0 || dist == 0) {
+    this->camera.changeMode("640x480");
   } else if ( dist > 4.0 ) {
-    this->camera.changeMode("320x320");
+    this->camera.changeMode("320x240");
   } else  {
-    this->camera.changeMode("160x160");
+    this->camera.changeMode("160x120");
   }
 
   // this->camera.showImage(this->image);

### 2017-02-05 docs/paper/paper.tex
Start implementation on trajectory generator
Update docs

--- 2017-01-25 docs/paper/paper.tex
@@
 \documentclass[letterpaper, 10 pt, conference]{ieeeconf}
-\IEEEoverridecommandlockouts
-\overrideIEEEmargins  % required to meet printer requirements.
+\IEEEoverridecommandlockouts{}
+\overrideIEEEmargins{}  % required to meet printer requirements.
 
@@
 % TITLE
-\title{\large \textbf Autonomous Landing of a Quadrotor on a Moving Platform in
+\title{\large \textbf Autonomous Quadrotor Landing on a Moving Platform in
 Outdoor Environments}
@@
 \begin{abstract}
-The task of landing an aircraft on moving objects has been a topic of interest
-ever since humans took to the skies in the early twentieth century. Typically
-when attempting landing small, Micro UAVs such as quadrotors, the landing
-procedure is either done manually, or using GPS guidance to land on a
-stationary target. If landing on a moving target or in high wind conditions, a
-human operator is generally required. However this requires the human operator
-to have a clear line of site to both the target and the aircraft during all
-stages of the landing procedure. In recent years there have been several papers
-that propose a set of methods for landing on a slow moving platform in ideal
-conditions such as low wind and ideal GPS signals with little or no noise. Our
-contribution in this work is the demonstration of a set of algorithms that
-allow a quadrotor to perform a autonomous landing on a car travelling at over 20
-meters per second while relying only on visual inertial data collected from and
-on-board gimbaled camera system. From this image data, along with on-board IMU
-readings, it is shown that both speed of the target and the quadrotor in the
-inertial frame can be directly estimated, and using this information a set of
-controllers and planners can be developed that allows for the quadrotor to
-perform a high speed landing manoeuvre in a variety of conditions. The
-robustness of our system is demonstrated by landing in without using GPS,
-poorly lit conditions, and with high winds.
 \end{abstract}
@@
 
-% CAMERA TRANSFORMS
-\section{Camera Transforms}
+% TARGET TRACKING
+\section{Target Tracking}
+A popular visual fiducial system called AprilTag~\cite{Olson2011} was chosen,
+the system allows us to identify the landing target along with the full 6 dof
+estimation. There exists multiple implementations of
+AprilTag,~\cite{AprilTagMIT} was chosen because it is the most used
+implementation. In the following we describe steps taken to optimize the
+AprilTag detection in-order to run the processing at a higher rate.
+
+\subsection{Adaptive Image Processing}
+The standard implementation of the AprilTag library when processing images
+of 640 by 480 pixels results with an update rate of approximately 3 to
+5 fps on the on-board computer too low for quadrotor controls. To improve
+performance we adapted the image size depending on the estimated
+distance between camera and AprilTag.
+
+\subsection{AprilTag Windowing}
+In~\cite{Ling2014} an attempt was made to optimize the AprilTag library
+by reducing the brightness of the image such that the majority of the
+image is black, we went one step further and masked the lastest image
+using the last detected AprilTag camera coordinates, rendering everything
+other than the AprilTag black, with this modification we assumed the image
+coordinates between frames did not vary too wildly, else the mask is
+removed and the full image is inputed to the AprilTag detector for
+processing.
+
+Once the center of the AprilTag in camera frame is found the top left and
+bottom right corners of the AprilTag can be calculated with:
+
+\begin{align}
+  X_{\text{top left}} &= X - (l / 2) - X_{\text{padding}} \\
+  Y_{\text{top left}} &= Y - (l / 2) - Y_{\text{padding}} \\
+  X_{\text{bottom right}} &= X + (l / 2) + X_{\text{padding}} \\
+  Y_{\text{bottom right}} &= Y + (l / 2) + Y_{\text{padding}}
+\end{align}
+
+Where $X, Y$ are positions of the AprilTag in the camera frame,
+$X_{\text{padding}}, Y_{\text{padding}}$ are the mask padding in the camera
+frame, $l$ is the AprilTag side length in meters, and finally $X_{\text{top
+left}}, Y_{\text{top left}}, X_{\text{bottom right}}, Y_{\text{bottom right}}$
+represent the top left and bottom right corners in the camera frame. Adding the
+mask padding at this point allows the padding to be defined in the camera
+frame which increases and decreases proportionally in the image frame
+depending on the depth-distance between camera and AprilTag.
+
+Using the pin-hole camera model, we can convert the AprilTag's corners
+from camera frame into image frame with the following:
+
+\begin{equation}
+  x = \dfrac{f_{x} * X}{Z}
+\end{equation}
+
+\begin{equation}
+  y = \dfrac{f_{y} * Y}{Z}
+\end{equation}
+
+Where $f_{x}$ and $f_{y}$ are the focal length in pixels in the $x$ and
+$y$ axis, and finally $x, y$ are image pixel coordinates. Using the
+image coordinates of the top left and bottom right corners of the AprilTag
+a mask can be created.
+
+\subsection{Nested AprilTag}
+To address visibility issues of the AprilTag as the field of view of is reduced
+during landing, we found a unique combination of AprilTag ids that allows us to
+place a smaller AprilTag in the center of a larger AprilTag (see
+Fig~\ref{fig:apriltag_illumination_invariant}). By shear coincidence the
+AprilTag implementation~\cite{AprilTagMIT} always prefers the smaller secondary
+tag when both are detected.
+
+\subsection{Illumination Invariant AprilTag}
+A common issue in computer vision is illumination changes in the
+environment which in turn interferes with the performance of detection
+algorithms. From our experience the standard black and white AprilTag
+fails to be detected if a shadow is casted partially or fully upon the tag
+features, this is because the AprilTag detection relies heavily on the
+edges and lines of the tag to be able to estimate the 6dof pose.
+
+Reliable image processing regardless of the time of day is vital to the
+success of target detection. Using methods described in~\cite{Maddern14}
+we have idenitified the best colours for an illumination invariant
+AprilTag to be blue and green (see
+Fig~\ref{apriltag_illumination_invariant}), additionally
+
+\begin{equation}
+  I = \log(R_{2}) - \alpha \log(R_{1}) - (1 - \alpha) \log(R_{3})
+\end{equation}
+
+Where $R_{1}, R_{2}, R_{3}$ are sensor responses (or image channels)
+corresponding to peak sensitivies at ordered wavelengths $\lambda_{1}
+< \lambda_{2} < \lambda_{3}$.
+
+\begin{figure}
+\label{fig:apriltag_illumination_invariant}
+  \includegraphics[width=\linewidth]{images/apriltag_illumination_invariant}
+  \caption{Illumination Invariant AprilTag}
+\end{figure}
+
+% TARGET ESTIMATION
+\section{Target Estimation}
+The inertial target position, linear velocity, angular velocity and
+heading are estimated with an Extended Kalman Filter running at 200Hz, the
+estimation is in turn used for tracking and landing controllers on board
+the quadrotor.
+
+\subsection{Process Model}
+We chose to use a two-wheel robot motion model to approximate the forward
+kinematics of the target, which is given as:
+
+\begin{equation}
+    \begin{split}
+        \textbf{x}
+        &= \begin{bmatrix}
+            x_{1} & x_{2} & x_{3} & x_{4} & x_{5} & x_{6} & x_{7}
+        \end{bmatrix} \\
+        &=
+        \begin{bmatrix}
+            x & y & z & \theta & v & \omega & v_{z}
+        \end{bmatrix}
+    \end{split}
+\end{equation}
+
+\begin{equation}
+    \textbf{u}(t)
+        = \begin{bmatrix}
+            u_{1} \\
+            u_{2} \\
+            u_{3}
+        \end{bmatrix}
+        = \begin{bmatrix}
+            v \\
+            \omega \\
+            v_{z}
+        \end{bmatrix}
+        = \begin{bmatrix}
+            \mathcal{N}_{v} \\
+            \mathcal{N}_{\omega} \\
+            \mathcal{N}_{v_{z}}
+        \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+    \dot{\textbf{x}} = \begin{bmatrix}
+        \dot{x_{1}} \\ 
+        \dot{x_{2}} \\ 
+        \dot{x_{3}} \\ 
+        \dot{x_{4}} \\
+        \dot{x_{5}} \\
+        \dot{x_{6}} \\
+        \dot{x_{7}}
+    \end{bmatrix} =
+    \begin{bmatrix}
+        x_{5} \cos(x_{4}) \\
+        x_{5} \sin(x_{4}) \\
+        x_{7} \\
+        x_{6} \\
+        u_{1} \\
+        u_{2} \\
+        u_{3} \\
+    \end{bmatrix}
+\end{equation}
+
+Where the estimator estimates the inertial position in $x$, $y$ and $z$
+direction, heading $\theta$, wheel velocity $v$, steering angular velocity
+$\omega$ and linear velocity $v_{z}$ in the $z$ direction. It is worth
+noting the linear velocity in the $x$ and $y$ direction can be calculated
+from $v \cos(\theta)$ and $v \sin(\theta)$ respectively. The inputs to the
+process model are driven by Gaussian White Noise, since we do not possess
+input information to the two wheel robot motion model.
+
+\subsection{Measurement Model}
+
+\begin{equation}
+  h(t) = \begin{bmatrix} p_{1 \times 3} & {0}_{1 \times 4} \end{bmatrix}
+\end{equation}
 
@@
 
-% LIGHT INVARIANT
-\section{Light Invariant}
+Transform detected target from image frame to gimbal joint frame
 
-% APRILTAG ESTIMATION
-\section{AprilTag Estimation}
+\begin{equation}
+  x_{\text{gjf}} = R^{\text{gjf}}_{\text{i}}
+    R^{\text{nwu}}_{\text{cf}}
+    x_{\text{i}} + t_{c}
+\end{equation}
 
-% SYSTEM ARCHITECTURE
-\section{System Architecture}
+Gimbal joint frame to body planar frame
+
+\begin{equation}
+  x_{\text{bpf}} = R^{\text{bpf}}_{\text{gjf}} x_{\text{gjf}}
+\end{equation}
+
+Body planar frame to inertial frame
+
+\begin{equation}
+  x_{\text{if}} = R^{\text{enu}}_{\text{nwu}}
+    R^{\text{if}}_{\text{bpf}}
+    x_{\text{bpf}}
+\end{equation}
+
+% TRAJECTORY PLANNING
+\section{Trajectory Planning}
+
+\begin{equation}
+  \begin{split}
+    \textbf{x} 
+      &= \begin{bmatrix}
+        x_{1} & x_{2} & x_{3} & x_{4}
+      \end{bmatrix}^{T} \\ 
+      &= \begin{bmatrix}
+        x & \dot{x} & z & \dot{z}
+      \end{bmatrix}^{T} \in {\rm I\!R}^{4}
+  \end{split}
+\end{equation}
+
+\begin{equation}
+  \begin{split}
+    \textbf{x}_{0} = \begin{bmatrix}
+        x_{0} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
+    \end{bmatrix}^{T} \\
+    \textbf{x}_{d} = \begin{bmatrix}
+        x_{d} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
+    \end{bmatrix}^{T}
+  \end{split}
+\end{equation}
+
+\begin{equation}
+  \textbf{u}(t)
+    = \begin{bmatrix} u_{1} \\ u_{2} \end{bmatrix}
+    = \begin{bmatrix} a_{z} \\ \theta \end{bmatrix}
+    \in {\rm I\!R}^{2}
+\end{equation}
+
+\begin{equation}
+  \dot{\textbf{x}} =
+    \begin{bmatrix}
+      \dot{x_{1}} \\ \dot{x_{2}} \\ \dot{x_{3}} \\ \dot{x_{4}}
+    \end{bmatrix} =
+    f(\textbf{x}, \textbf{u}) =
+    \begin{bmatrix}
+      x_{2} \\
+      u_{1} \sin(u_{2}) \\
+      x_{4} \\
+      u_{1} \cos(u_{2}) - g \\
+      u_{2}
+    \end{bmatrix}
+\end{equation}
+
+\begin{align} 
+  \text{minimize} \quad &J(\textbf{x}, \textbf{u}) \\
+  \text{s.t.} \quad & \dot{\textbf{x}} = f(\textbf{x}, \textbf{u}) \\
+    & \textbf{x}(t = 0) = \textbf{x}_{0} \\
+    & \textbf{x}(t = t_{f}) = \textbf{x}_{d} \\
+    & \textbf{u} \in \textbf{U} \quad \forall t \in [0, t_{f}]
+\end{align}
+
+% QUADROTOR CONTROL
+\section{Quadrotor Control}
+For target tracking a Proportional-Integral-Derivative (PID) controller
+was implemented. The estimated target position in inertial frame is
+converted to body frame and used as control errors to the tracker control
 
@@
 
+% BIBLIOGRAPHY
 \bibliography{paper}
+\bibliographystyle{ieeetr}
 

### 2017-02-05 scripts/awesomo_planner.py

@@ -119,7 +119,7 @@ def cost_func(x, args):
 
     # control input cost
     cost += 0.5 * np.linalg.norm(states[4])  # az
-    cost += 1.0 * np.linalg.norm(states[5])  # theta
+    cost += 2.0 * np.linalg.norm(states[5])  # theta
 
     # control input difference cost
     cost += 1.0 * pow(np.sum(np.diff(states[4])), 2)  # az
@@ -205,18 +205,18 @@ if __name__ == "__main__":
     plot_results(traj, result.x, T, n, m)
 
     # plot real trajectory using only inputs
-    x = [x0[0][0], x0[0][1], x0[0][2], x0[0][3]]
-    pos_x = [x[0]]
-    pos_y = [x[2]]
-    states = result.x.reshape(T, n + m).T
-    for i in range(T):
-        u = [states[4][i], states[5][i]]
-        x = quadrotor(x, u, dt)
-        pos_x.append(x[0])
-        pos_y.append(x[2])
-
-    plt.title("Optimal Control Trajectory")
-    plt.plot(pos_x, pos_y)
-    plt.xlabel("x")
-    plt.ylabel("z")
-    plt.show()
+    # x = [x0[0][0], x0[0][1], x0[0][2], x0[0][3]]
+    # pos_x = [x[0]]
+    # pos_y = [x[2]]
+    # states = result.x.reshape(T, n + m).T
+    # for i in range(T):
+    #     u = [states[4][i], states[5][i]]
+    #     x = quadrotor(x, u, dt)
+    #     pos_x.append(x[0])
+    #     pos_y.append(x[2])
+    #
+    # plt.title("Optimal Control Trajectory")
+    # plt.plot(pos_x, pos_y)
+    # plt.xlabel("x")
+    # plt.ylabel("z")
+    # plt.show()

### 2017-02-05 scripts/awesomo_remote.py

@@ -1,4 +1,5 @@
 #!/usr/bin/env python
+from time import sleep
 from math import pi
 
 import rospy
@@ -183,6 +184,7 @@ def lz_circle_path(radius, velocity):
 
     return (velocity, angular_velocity)
 
+
 if __name__ == "__main__":
     rospy.init_node("awesomo_remote")
     lz = LandingZone()
@@ -194,38 +196,41 @@ if __name__ == "__main__":
 
     # mavros.set_local_pose(0, 0, 0)
     # camera.set_mode("320x240")
-    # # camera.set_mode("160x160")
-    #
+    # camera.set_mode("160x160")
+
     # gimbal.set_attitude([-0.5, -1.57])
 
     # lz.set_velocity(0.5)
     # lz.set_position([1000, 0, 0])
 
-    # velocity, angular_velocity = lz_circle_path(5, 1.0)
+    # velocity, angular_velocity = lz_circle_path(10, 2.0)
     # lz.set_velocity(velocity)
     # lz.set_angular_velocity(angular_velocity)
 
     quad.set_mode("HOVER_MODE")
-    quad.set_hover_point([0.0, 0.0, 5.0])
-    quad.set_pctrl_settings({
-        "roll": {
-            "min": -30,
-            "max": 30,
-            "k_p": 0.3,
-            "k_i": 0.0,
-            "k_d": 0.2
-        },
-        "pitch": {
-            "min": -30,
-            "max": 30,
-            "k_p": 0.3,
-            "k_i": 0.0,
-            "k_d": 0.2
-        },
-        "throttle": {
-            "hover": 0.5,
-            "k_p": 0.4,
-            "k_i": 0.0,
-            "k_d": 0.2
-        }
-    })
+    quad.set_hover_height(3.0)
+    # quad.set_hover_point([0.0, 0.0, 5.0])
+    # quad.set_pctrl_settings({
+    #     "roll": {
+    #         "min": -30,
+    #         "max": 30,
+    #         "k_p": 0.3,
+    #         "k_i": 0.0,
+    #         "k_d": 0.2
+    #     },
+    #     "pitch": {
+    #         "min": -30,
+    #         "max": 30,
+    #         "k_p": 0.3,
+    #         "k_i": 0.0,
+    #         "k_d": 0.2
+    #     },
+    #     "throttle": {
+    #         "hover": 0.5,
+    #         "k_p": 0.4,
[…]

### 2017-02-07 docs/paper/paper.tex
Update paper

@@
 
-% PROBLEM FORMULATION
-\section{Problem Formulation}
+% SYSTEM OVERVIEW
+\section{System Overview}
+In this section we describe the setup of our problem, from the quadrotor,
+ground landing target to coordinate systems used to represent positions in
+body and inertial frames.
+
+For the autonomous landing problem we assume that the quadrotor has direct line
+of sight to the landing target and that the AprilTag is detectable. The target
+position and velocity estimation is performed on-board the quadrotor, and
+using the estimations of the target the quadrotor tracks and lands onto the
+target.
+
+\begin{itemize}
+  \item{$I$\@: Inertial Frame}
+  \item{$C$\@: Camera Frame}
+  \item{$G$\@: Gimbal Frame}
+  \item{$B$\@: Quadrotor Body Frame}
+  \item{$BP$\@: Quadrotor Body Planar Frame}
+\end{itemize}
+
+We describe five different main coordinate frames used throughout this
+paper, in general we have followed the ROS coordinate frame conventions
+where the inertial frame $I$ is in ENU coordinate frame, the camera frame
+$C$ is in EDN coordinate frame, gimbal frame $G$, quadrotor body frame $B$ and
+quadrotor body planar frame $BP$ uses NWU coordinate frame. The quadrotor body
+planar frame $BP$ is defined as the body centered and inertial horizon $x$-$y$
+aligned frame, to reiterate the body planar frame $BP$ ignores the roll and
+pitch (but not yaw) normally considered in a body frame $B$.
 
@@
 features, this is because the AprilTag detection relies heavily on the
-edges and lines of the tag to be able to estimate the 6dof pose.
+edges and lines of the tag to be able to estimate the 6 dof pose.
+Depending on the time of day or weather conditions, this can have
+a significant impact as the quadrotor approaches the target, as its own
+shadow over the AprilTag can render the tag undetectable.
 
-Reliable image processing regardless of the time of day is vital to the
-success of target detection. Using methods described in~\cite{Maddern14}
-we have idenitified the best colours for an illumination invariant
-AprilTag to be blue and green (see
-Fig~\ref{apriltag_illumination_invariant}), additionally
+Reliable image processing is therefore paramount to the success of target
+detection, using methods described in~\cite{Maddern14} we have idenitified
+the best colours for an illumination invariant AprilTag to be blue and
+green (see Fig~\ref{apriltag_illumination_invariant}), additionally
 
@@
 \subsection{Measurement Model}
+The measurement inputted into the estimator is the target position ($x, y,
+z$) in the inertial frame, the target position has been transformed from
+the camera frame through to the gimbal frame to the inertial frame. Care
+was taken to ensure that the IMU measurements were synchronized with image
+of the AprilTag at the time it was captured.
 
-\begin{equation}
-  h(t) = \begin{bmatrix} p_{1 \times 3} & {0}_{1 \times 4} \end{bmatrix}
-\end{equation}
-
-% GIMBAL TRANSFORMS
-\section{Gimbal Transforms}
-
-Transform detected target from image frame to gimbal joint frame
+To obtain the target position in the inertial frame, the detected target
+position is first transformed from image frame to gimbal joint frame as
+follows:
 
@@
 
-Gimbal joint frame to body planar frame
+Then from gimbal joint frame to body planar frame:
 
@@
 
-Body planar frame to inertial frame
+Finally from body planar frame to inertial frame:
 
@@
 
+This final target position in the inertial frame is then passed onto the
+estimator. The measurement model $h(t)$ and the linearized measurement
+model $H(t)$ at time $t$ is then simply
+
+\begin{equation}
+    h(t) = \begin{bmatrix} x, y, z \end{bmatrix}^{T}
+\end{equation}
+
+\begin{equation}
+    H(t) = \begin{bmatrix} I_{3 \times 3} \end{bmatrix}^{T}
+\end{equation}
+
+The Extended Kalman Filter updates the process model at 200 Hz, while the
+measurement is updated upon when the AprilTag is detected and transformed.
+The output of the estimator is in turn used for tracking and landing.
+
 % TRAJECTORY PLANNING
 \section{Trajectory Planning}
+
+\subsection{2D Quadrotor Model}
+The model used for trajectory planning is a two dimensional three degrees
+of freedom (DOF) quadrotor in the $x$-$z$ plane. By using this model we
+assume there will be small changes in the $x$-$y$ plane where the
+controllers can correct without planning.
+
+The 2D quadrotor state $\textbf{x}$ includes both position and velocity in the
+$x$ and $z$ direction. Where $x_{0}$ and $x_{d}$ are the initial and final
+states of the quadrotor. The inputs to the quadrotor model are the
+acceleration $a_{z}$ in the $z$ direction in body frame, and pitch angle
+$\theta$ in inertial frame.
 
@@
     \textbf{x}_{0} = \begin{bmatrix}
-        x_{0} & \dot{x_{d}} & z_{d} & \dot{z_{d}}
+        x_{0} & \dot{x_{0}} & z_{0} & \dot{z_{0}}
     \end{bmatrix}^{T} \\
@@
 \end{equation}
+
+The dynamics are thus given as:
 
@@
 
+Where $g$ is the gravitational constant.
+
+\subsection{Trajectory Problem Formulation}
+The objective of the trajectory is to achieve landing of the quadrotor
+onto a non-stationary target at $\textbf{x}_{d}$, further the trajectory
+has to satisfy a number of desirable soft constraints, which are minimal
+deviation from desired path $p_{\text{diff}}$, minimal total input
+$u_{\text{total}}$ and minimal input control difference between time steps
+$u_{\text{diff}}$.
+
+The desired path $\textbf{p}_{\text{desired}}$ vector is a straight-line
+from initial position $x_{0}$ to final position $x_{d}$.
+
+\begin{equation}
+    p_{\text{diff}} = || \textbf{x} - \textbf{p}_{\text{desired}} ||^{2}
+\end{equation}
+
+\begin{equation}
+    u_{\text{total}} = || \textbf{u} ||^{2}
+\end{equation}
+
+\begin{equation}
+    u_{\text{diff}} = \sum_{i = 0}^{t_{f} - 1}
+        \left\Vert
+            \textbf{u}(i + 1) - \textbf{u}(i)
+        \right\Vert^{2}
+\end{equation}
+
+\begin{equation}
+    J(\textbf{x}, \textbf{u}) =
+        w_{1} \cdot p_{\text{diff}}
+        + w_{2} \cdot u_{\text{total}}
+        + w_{3} \cdot u_{\text{diff}}
+\end{equation}
+
+\begin{equation}
+  C_{\text{eq}} = \sum_{i = 0}^{t_{f} - 1}
+    \textbf{x}(i + 1) - f(\textbf{x}(i), \textbf{u}(i))
+\end{equation}
+
 \begin{align}
@@
 \section{Quadrotor Control}
-For target tracking a Proportional-Integral-Derivative (PID) controller
-was implemented. The estimated target position in inertial frame is
-converted to body frame and used as control errors to the tracker control
+
+\subsection{Tracking Controller}
+For target tracking two PID controllers were implemented, first a position
+based controller that corrects positional errors of the quadrotor relative
+to the target. Second, a velocity based controller that uses estimated
+target velocity as a feed-forward signal to match the target's velocity.
+The two controllers are combined together to form the tracking controller.
+
+\begin{equation}
+   \theta = k_{p} e + k_{i} \sum_{i = 0}^{t} e_{i} dt + k_{d} \dot{e}
+\end{equation}
+
+\begin{figure}
+\label{fig:tracking_controller}
+  \includegraphics[width=\linewidth]{images/tracking_controller}
+  \caption{Tracking Controller}
+\end{figure}
+
+\subsection{Landing Controller}
+During landing the controller will be switched from tracking to landing,
+the controller contains two PID controllers the first controller is
+a position based control to correct positional errors of the quadrotor
+relative to the target in the body frame.
 
